### 2016-10-30 Inelastic/inelastic_main.tex
First commit

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.1 distribution.
%   Version 4.1r of REVTeX, August 2010
%
%   Copyright (c) 2009, 2010 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
 reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%showpacs,preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-1}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

%\usepackage[showframe,%Uncomment any one of the following lines to test 
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}

\begin{document}

%\preprint{APS/123-QED}

\title{Search for WIMP Inelastic Scattering Off Xenon Nuclei With Xenon100 Data}% Force line breaks with \\
\thanks{}%

\author{Ann Author}
 \altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\
\author{Second Author}%
 \email{Second.Author@institution.edu}
\affiliation{%
 Authors' institution and/or address\\
 This line break forced with \textbackslash\textbackslash
}%

\collaboration{XENON Collaboration}%\noaffiliation

\author{Authors}
% \homepage{http://www.Second.institution.edu/~Charlie.Author}
\affiliation{
 Second institution and/or address\\
 This line break forced% with \\
}%
\affiliation{
 Affiliation
}%

%\collaboration{CLEO Collaboration}%\noaffiliation

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}

\end{abstract}

%\pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
                             % Classification Scheme.
%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle

%\tableofcontents

\section{\label{sec:level1} Introduction}
Astrophysical evidence indicates that the dominant mass fraction of our Universe consists of some yet unknown form
of dark matter. Well motivated models predict Dark Matter in the form of Weakly Interacting Massive Particles (WIMPs),
hypothesis which is currently being tested by several direct and indirect detection experiment.

Most of direct detection searches focuses on  elastic scattering of dark matter particles off nuclei.
In this analysis instead we explore an inelastic scattering process, we consider the $^{129}\text{Xe}$ isotope being excited to a low-lying state
with subsequent prompt de-excitation via the emission a photon. This isotope is an excellent target
since its abundance in natural xenon is of 26.4\% and a relatively low energy is necessary to excite its $3/2+$ state above the $1/2+$
spin ground state.
Inelastic WIMP-nucleus scattering in xenon is complementary to elastic scattering for spin-dependent interactions,
the former dominates the integrated rate above  $\simeq10$~keV of energy deposition.
Furthermore, in the case of dark matter detection, this channel can be employed to asses whether the nature of the fundamental interaction
is spin-dependent or not.

\section{Xenon100 Detector}
The Xenon100 experiment is a  dual phase liquid xenon TPC. For a given interaction in the liquid target this type of detector produces two separated signals,
one proportional to the prompt scintillation (S1) the other to ionization (S2).

To add: sentences about detector stability, science run data used, Ly and Y measurements used.

\section{Data Analysis}

brief explaination of the signature, selection cuts, few words about acceptances, image of signal region and control region.

\subsection{Signal Simulation}

description of the simulated signal, few words about cross checks MC matching.

\subsection {Background Model}
Description of the data driven bkg model evaluation, few numbers on estimated background, words about cross checks with Th232.

%A citation in text uses the command \verb+\cite{#1}+ or
%\verb+\onlinecite{#1}+ and refers to an entry in the bibliography. 
%An entry in the bibliography is a reference to another document.
\subsection{Systematic Uncertainties}

few words, mainly a table summarizing uncertainties.

\section{Results}

\subsubsection{Citations}
%Because REV\TeX\ uses the \verb+natbib+ package of Patrick Daly, 
%the entire repertoire of commands in that package are available for your document;
%see the \verb+natbib+ documentation for further details. Please note that
%REV\TeX\ requires version 8.31a or later of \verb+natbib+.

\end{document}
%
% ****** End of file apssamp.tex ******

### 2016-11-28 Inelastic/inelastic_main.tex
add
separated files

@@
 
-\section{\label{sec:level1} Introduction}
-Astrophysical evidence indicates that the dominant mass fraction of our Universe consists of some yet unknown form
-of dark matter. Well motivated models predict Dark Matter in the form of Weakly Interacting Massive Particles (WIMPs),
-hypothesis which is currently being tested by several direct and indirect detection experiment.
+\input{intro}
 
-Most of direct detection searches focuses on  elastic scattering of dark matter particles off nuclei.
-In this analysis instead we explore an inelastic scattering process, we consider the $^{129}\text{Xe}$ isotope being excited to a low-lying state
-with subsequent prompt de-excitation via the emission a photon. This isotope is an excellent target
-since its abundance in natural xenon is of 26.4\% and a relatively low energy is necessary to excite its $3/2+$ state above the $1/2+$
-spin ground state.
-Inelastic WIMP-nucleus scattering in xenon is complementary to elastic scattering for spin-dependent interactions,
-the former dominates the integrated rate above  $\simeq10$~keV of energy deposition.
-Furthermore, in the case of dark matter detection, this channel can be employed to asses whether the nature of the fundamental interaction
-is spin-dependent or not.
+\input{analysis}
 
-\section{Xenon100 Detector}
-The Xenon100 experiment is a  dual phase liquid xenon TPC. For a given interaction in the liquid target this type of detector produces two separated signals,
-one proportional to the prompt scintillation (S1) the other to ionization (S2).
-
-To add: sentences about detector stability, science run data used, Ly and Y measurements used.
-
-\section{Data Analysis}
-
-brief explaination of the signature, selection cuts, few words about acceptances, image of signal region and control region.
-
-\subsection{Signal Simulation}
-
-description of the simulated signal, few words about cross checks MC matching.
-
-\subsection {Background Model}
-Description of the data driven bkg model evaluation, few numbers on estimated background, words about cross checks with Th232.
-
-%A citation in text uses the command \verb+\cite{#1}+ or
-%\verb+\onlinecite{#1}+ and refers to an entry in the bibliography. 
-%An entry in the bibliography is a reference to another document.
-\subsection{Systematic Uncertainties}
-
-few words, mainly a table summarizing uncertainties.
-
-\section{Results}
+\input{results}
 

### 2016-11-28 Inelastic/analysis.tex
separated files

\section{Data Analysis}

brief explaination of the signature, selection cuts, few words about acceptances, image of signal region and control region.

\begin{figure}[h]
  \includegraphics[width=\linewidth]{images/bkg_in_sr.png}
  \caption{Signal region and control region.}
  \label{fig:SR}
\end{figure}

\begin{figure}[h]
  \includegraphics[width=\linewidth]{images/wimp_in_sr.png}
  \caption{Signal region and control region, for WIMP of mass 100~GeV.}
  \label{fig:SR2}
\end{figure}

\subsection{Signal Simulation}

description of the simulated signal, few words about cross checks MC matching.

\subsection {Background Model}
Description of the data driven bkg model evaluation, few numbers on estimated background, words about cross checks with Th232.

%A citation in text uses the command \verb+\cite{#1}+ or
%\verb+\onlinecite{#1}+ and refers to an entry in the bibliography. 
%An entry in the bibliography is a reference to another document.
\subsection{Systematic Uncertainties}

few words, mainly a table summarizing uncertainties.

### 2016-11-28 Inelastic/intro.tex
separated files

\section{\label{sec:level1} Introduction}
Astrophysical evidence indicates that the dominant mass fraction of our Universe consists of some yet unknown form
of dark matter. Well motivated models predict Dark Matter in the form of Weakly Interacting Massive Particles (WIMPs),
hypothesis which is currently being tested by several direct and indirect detection experiment.

Most of direct detection searches focuses on  elastic scattering of dark matter particles off nuclei.
In this analysis instead we explore an inelastic scattering process, we consider the $^{129}\text{Xe}$ isotope being excited to a low-lying state
with subsequent prompt de-excitation via the emission a photon. This isotope is an excellent target
since its abundance in natural xenon is of 26.4\% and a relatively low energy is necessary to excite its $3/2+$ state above the $1/2+$
spin ground state.
Inelastic WIMP-nucleus scattering in xenon is complementary to elastic scattering for spin-dependent interactions,
the former dominates the integrated rate above  $\simeq10$~keV of energy deposition.
Furthermore, in the case of dark matter detection, this channel can be employed to asses whether the nature of the fundamental interaction
is spin-dependent or not.

\section{Xenon100 Detector}
The Xenon100 experiment is a  dual phase liquid xenon TPC. For a given interaction in the liquid target this type of detector produces two separated signals,
one proportional to the prompt scintillation (S1) the other to ionization (S2).

To add: sentences about detector stability, science run data used, Ly and Y measurements used.

### 2016-11-28 Inelastic/results.tex
separated files

\section{Results}
No evidence of dark matter.

\begin{figure}[h]
  \includegraphics[width=\linewidth]{images/data_vs_bkg.png}
  \caption{Results, comparison between data and expected background.}
  \label{fig:dataVSbkg}
\end{figure}

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{images/limit_reb.png}
  \caption{Observed and expected limits.}
  \label{fig:limits}
\end{figure}

### 2016-12-19 Inelastic/analysis.tex
some small edit

@@
 \section{Data Analysis}
+
+The inelastic scattering of a WIMP with the nucleus of $^{129}$Xe produces an energy deposit via nuclear recoil with subsequent emission of  
+a 39.6~KeV de-exitation photon. 
+The largest fraction of the energy released in the event is via electronic recoil (ER) due to the emitted photon, this represents an
+unusual signature for this kind of detector and brings the signal to overlay a phase space region with large backgrounds.
+The choosen region of interest for this analysis surrounds the 39.6~KeV line in the cS1-cS2 plane which is further divided into
+sub regions, as shown in figure~\ref{fig:SR}.
+
+Events are asked, other than falling in the defined region of interest, to fullfill several selection criteria:
+quality selection aimed to reduce noise impact toghether with energy and threshold selection on S2,
+selection of single scatter events and fiducial volume definitions are reported in detail in \cite{dataAnalysis}, this analysis follows
+the selection reported there for Run-II, only few modification have been designed specifically for this analysis and discussed below. 
+In particular, selection on S2 width as a function of drift time has been optimized on a sample of events from 40~KeV of AmBe 
+and set to a 95\% acceptance on those type of events.
+
+Xinelastic\_analysis\_S2width0
+Inelastic\_Xs2single0
+
+say something on data used: DM, calibration ecc..
 

### 2017-01-04 Inelastic/analysis.tex
first version of signal model

@@
 \section{Data Analysis}
+
+This analysis is performed using XENON100 Run-II science data, which corresponds to 224.9~live days. The detector response to
+electronic recoil (ER) has been characterized using $^{60}$Co and $^{232}$Th radioactive sources, while response to inelastic nuclear recoil (NR)
+scattering was calibrated using an $^{241}$AmBe source.
 
@@
 In particular, selection on S2 width as a function of drift time has been optimized on a sample of events from 40~KeV of AmBe 
-and set to a 95\% acceptance on those type of events.
+and set to a 95\% acceptance on those type of events. Events are required to be single scatter by applying a threshold on the 
+second largest S2 peak size, in this analysis the threshold has been set to 160~PE and constant in S2 signal size. The fiducial
+volume chosen for this analysis corresponds to 34~Kg of liquid xenon.
 
-Xinelastic\_analysis\_S2width0
-Inelastic\_Xs2single0
-
-say something on data used: DM, calibration ecc..
-
-brief explaination of the signature, selection cuts, few words about acceptances, image of signal region and control region.
+%brief explaination of the signature, selection cuts, few words about acceptances, image of signal region and control region.
 
@@
 \subsection{Signal Simulation} 
+%description of the simulated signal, few words about cross checks MC matching.
+The detector response to inelastic scattering of WIMPs of different masses off $^{129}$Xe nucleus was simulated using an empirical model.
+The total deposited energy is divided into two independent contributions: the one related to the 39.6~KeV de-exitation photon and the one  relative to
+the simultaneous nuclear recoil (NR) of the Xe atom, the number of photons and charge yield detected is simulated separatedly for each contribution
+and then added togheter.
 
-description of the simulated signal, few words about cross checks MC matching.
+The electronic recoil (ER) induced by the de-exitation photon is produced 
+The detector related light yield $L_y$ measured at 39.6~KeV with AmBe calibration has been found to have a large systematic uncertainty
+due to the contribution of the nuclear recoil, so the light yield used to describe the number of photon detected is the result of a fit 
+to data, corresponding to several lines, of the NEST model \cite{NEST,Geant1,Geant2}. The same model is used predict the charge yield at
+39.6~KeV whichis then scaled according to the detector's secondary scintillation factor $Y$, determined from detector response to single electrons \cite{SingleE},
+note that the corrected S2 observed by the bottom PMT array is used in this analysis. This is how the average $\mu_{cS1}$ and $\mu_{cS2}$ are obtained. 
+The detector resolution at 39.6~KeV is embedded in three parameter the standard deviation in cS1 and cS2, respectively $\sigma_{cs1}$ and $\sigma_{cs2}$ and 
+the correlation, $\rho$,  between cS1 and cS2. The correlation parameter is assumed to be independent of energy (at least in the considered range) and measured
+using the 164~KeV Xenon activated line by AmBe calibration source, this line is choosen since allows to disentangle efficiently contribution from nuclear recoil,
+the measured correlation is $\rho \, = \, -0.45 \pm 0.10$. Finally a two dimensional normal distribution, which is depicted in formula~\ref{f:2dgaus} except a normalization factor, 
+is employed as a probability density function $f(cS1,cS2)$ distribution of energy deposited from the 39.6~KeV photon.
+\begin{multline}
+	f(cS1,cS2)  = exp \Big( -\frac{1}{2(1-\rho^2)} \Big[ \frac{(cS1 - \mu_{cS1})^2}{\sigma_{cs1}^2} + \\ 
+	 \frac{(cS2 - \mu_{cS2})^2}{\sigma_{cs2}^2} - \frac{2\rho(cS1 - \mu_{cs1}) (cS2 - \mu_{cs2})} {\sigma_{cs1}\sigma_{cs2}} \Big] \Big) 
+	%f(cS1,cS2) ~ = ~  \frac{1}{2 \pi \sigma_{cs1} \sigma_cs2 \sqrt{1-\rho^{2}} } exp \Big( -\frac{1}{2(1-\rho^2)} \Big[ \frac{(cS1 - \hat{cS1})^2}{\sigma_{cs1}^2} \Big] \Big)
+\label{f:2dgaus}
+\end{multline}
+
+The cS1 and cS2 distributions from NR contribution to the total signal are predicted starting from the nuclear recoil energy spectrum
+for inelastic interaction of a given WIMP mass \cite{inelastic_th}, the average cS1 and cS2 are given by formula~\ref{f:cs1} and~\ref{f:cs2} respectively,
+where $\mathcal{L}_{eff}$ is the LXe relative scintillation efficiency while $S_{ee} \, = \, 0.58$  and $S_{nr} \, = \, 0.95$ describe the scintillation 
+quenching due to the electric field \cite{ScintQuenching}. The parameterization and uncertainties of $\mathcal{L}_{eff}$ as a function of $E_{nr}$ are based on existing 
+direct measurements \cite{run8Result}. The light yield at 122~keVee originate from the same NEST model fit as described above. For the cS2 the parameterization 
+of $Q_{Y}(E_{nr})$ is taken from \cite{QY}.
+all detector related resolution effects are introduced following the prescriptions described in \cite{dataAnalysis}.
+
+\begin{equation}
+cS1_{nr} ~=~ E_{nr} \, \mathcal{L}_{eff}(E_{nr}) \, L_{Y} \, \frac{S_{nr}}{S_{ee}}
+\label{f:cs1}
+\end{equation}
+
+\begin{equation}
+cS2_{nr}  ~ = ~ E_{nr} \, Q_{Y}(E_{nr}) \, Y
+\label{f:cs2}
+\end{equation}
+
+The pdf of the ER and NR contributions are then convoluted toghether to obtain the overall pdf of the signal.
+%The two contribution are summed toghether in an event-by-event basis using random extraction from the two pdfs. 
+A 2D (cS1 versus cS2) acceptance map is applied to the signal pdf to reproduce data selection effects, single selection acceptances
+are computed using calibration samples of AmBe for all the selection criteria except the outer volume veto and the single interaction selections, 
+for which a detailed computation has been performed. The average acceptance value in the region of interest is of about $0.80 \pm 0.05$. 
+An example of signal model is in Figure~\ref{fig:SR} for a WIMP of 100~GeV. 
+The simulation of the 39.6~KeV line has been compared to AmBe data, for the comparison the proper AmBe nuclear recoil and acceptances
+were simulated, the model was found in very well in agreement with calibration source data showing the largest discrepancies within 
+statistical uncertainties.
 

### 2017-01-05 Inelastic/analysis.tex
bkg model written

@@
 \subsection {Background Model}
-Description of the data driven bkg model evaluation, few numbers on estimated background, words about cross checks with Th232.
 
-%A citation in text uses the command \verb+\cite{#1}+ or
-%\verb+\onlinecite{#1}+ and refers to an entry in the bibliography. 
-%An entry in the bibliography is a reference to another document.
+The expected background in the region of interest is mainly caused by material radioactivity, mainly photons that 
+interact via compton scattering, background due to activation of Xe 39.6 line from radiogenic neutrons is found to be negligible.
+To model this background we use data from $^{60}$Co calibration campaign, the assumption is
+that the $^{60}$Co data are representative of the density in cS1-cS2 plane of the background. The calibration sample events
+in the ROI amount to  22225 events, this yield is then scaled to data according to a measured background scale factor $\tau_{bkg}$.
+
+The scale factor is measured in the two control regions shown in Figure~\ref{fig:SR} and labelled CR1 and CR2, the two control 
+regions give compatible results and the computed average is $\tau_{bkg} \, =  \, 0.034 \pm 0.002 $, where the reported uncertainty 
+is of statistical nature only.
+
+The distribution of the calibration sample has been compared to the data of the sience run in the two control regions,
+agreement is found within statistical uncertainties. $^{60}$Co calibration data have been compared in the region of interest to  
+data from $^{232}$Th calibration campaign, the largest deviation between the two shapes is within 4\%. An additional systematic
+uncertainty of 4\% has been applied to the expected background yield of each subregion of the ROI.
+
 \subsection{Systematic Uncertainties}
 
-few words, mainly a table summarizing uncertainties.
+few words, mainly a table summarizing uncertainties. Figure~\ref{fig:unc}.
+
+\begin{figure}[h]
+  \includegraphics[width=\linewidth]{images/wimp_sys_unc.png}
+  \caption{Signal region, uncertainties for WIMP of mass 100~GeV.}
+  \label{fig:unc}
+\end{figure}

### 2017-01-05 Inelastic/analysis.tex
first sloppy version

@@
 
-few words, mainly a table summarizing uncertainties. Figure~\ref{fig:unc}.
+Uncertainties on the total prediction of background events arise from the relative uncertainties on the measure of the normalization 
+factor $\tau_{bkg}$ and amount to 6\%, while uncertainties arising from radiogenic neutrons contributions are neglected. 
+Uncretainty on the shape of the predicted bakground distribution are assesed by reporting the maximal discrepancy in the ROI between
+the $^{60}$Co and $^{232}$Th calibration samples, according to this it is assigned to the expected yield of each subregion a 4\% uncertainty,
+uncertainty belonging to different regions are considered independent from each other.
+%It is important not only to describe correctly the expected total background but also its distribution
+
+Signal model, Energy scale uncertainties.... Uncertainties related to energy scale and more generally to detector response 
+are taken into account by relative uncertainties on the measure of $L_Y$,$\mathcal{L}_{eff}$,$Y$, $Q_Y$ and $\rho$. Has been shown 
+by the simulation that these type of uncertainty affect the total signal yield in the ROI by less than a percent for a wide range of masses,
+however they greatly affects the pdf of the signal model in the ROI. For each WIMP mass several signal simulation sample are produced 
+warying these parameter respectively $\pm 1 \sigma$, for each region is computed an uncertainty by adding in quadrature the variations
+%FIXME: explain this better, the up variation are separated from down variations and added togheter
+with respect to nominal of each case, Figure~\ref{fig:unc} is an example of such a systematic uncertainty computation for WIMP mass of 100~GeV.
+
+Uncertainty on the total yield of the signal arising from uncertainties on the selection acceptance are found to be very weakly dependent on 
+the WIMP mass, an overall 6\% acceptance uncertainty is then applied to all WIMP hypotesis.
+
+%FIXME: express this in an understandable way
+All the uncertainties discussed here are threated as nuissance parameter in the likelihood, which are contrained by a gaussian distribution.
 

### 2017-01-05 Inelastic/results.tex
bkg model written
first sloppy version

@@
 \section{Results}
-No evidence of dark matter.
+In an exposure of 34~Kg per 224~days of liquid xenon a yield of 764 events are found in the region of interest,
+which is compatible with the expectation of $756 \, \pm \, 5^{(stat.)} \, \pm 55^{(syst.)}$. The distribution 
+of events from data are compared to the background expectation in Figure~\ref{fig:dataVSbkg} and with the relative
+uncertainties.  
+This result is interpreted via a binned profiled likelihood approach by means of the test statistic $\tilde{q}$
+and its asymptotic distributions described in \cite{asympt}. 90\% CL$_s$ \cite{cls} confidence level limits are 
+computed on the spin dependent cross section as a function of the WIMP mass and shown in Figure~\ref{fig:limits}.
 

### 2017-01-09 Inelastic/analysis.tex
Some changes

@@
 
-This analysis is performed using XENON100 Run-II science data, which corresponds to 224.9~live days. The detector response to
+This analysis is performed using XENON100 Run-II science data, which corresponds to an exposure of 224.6~live days. The detector response to
 electronic recoil (ER) has been characterized using $^{60}$Co and $^{232}$Th radioactive sources, while response to inelastic nuclear recoil (NR)
@@
 a 39.6~KeV de-exitation photon. 
-The largest fraction of the energy released in the event is via electronic recoil (ER) due to the emitted photon, this represents an
-unusual signature for this kind of detector and brings the signal to overlay a phase space region with large backgrounds.
-The choosen region of interest for this analysis surrounds the 39.6~KeV line in the cS1-cS2 plane which is further divided into
-sub regions, as shown in figure~\ref{fig:SR}.
+The largest fraction of the energy released in the event is via electronic recoil due to the emitted photon, this represents an
+unusual signature for this kind of detector and brings the possible signal to overlay a phase space region with large backgrounds.
+The choosen region of interest for this analysis surrounds the 39.6~KeV xenon line in the cS1-cS2 plane which is further divided into
+sub-regions, as shown in Figure~\ref{fig:SR}.
 
-Events are asked, other than falling in the defined region of interest, to fullfill several selection criteria:
-quality selection aimed to reduce noise impact toghether with energy and threshold selection on S2,
-selection of single scatter events and fiducial volume definitions are reported in detail in \cite{dataAnalysis}, this analysis follows
-the selection reported there for Run-II, only few modification have been designed specifically for this analysis and discussed below. 
-In particular, selection on S2 width as a function of drift time has been optimized on a sample of events from 40~KeV of AmBe 
-and set to a 95\% acceptance on those type of events. Events are required to be single scatter by applying a threshold on the 
-second largest S2 peak size, in this analysis the threshold has been set to 160~PE and constant in S2 signal size. The fiducial
-volume chosen for this analysis corresponds to 34~Kg of liquid xenon.
+Events are asked, other than falling in the defined region of interest, to fullfill several selection criteria which can be sumarized as:
+selection aimed to reduce noise impact including energy (S1) and S2 thresholds, events must be of single scatter nature and fall 
+into a predefined fiducial volume. This analysis follows the selection criteria described in detail in \cite{dataAnalysis} for Run-II, 
+with only few exceptions. 
+%only few modification have been designed specifically for this analysis and discussed below. 
+In particular, the selection on S2 width as a function of drift time has been optimized on a sample of events selected from the 39.6~KeV line
+and set to a 95\% acceptance on these. Events are required to be single scatter by applying a threshold on the 
+second largest S2 peak size,  for this analysis this threshold has been optimized to 160~PE and set constant as function of S2 signal size. 
+Finally the chosen fiducial volume corresponds to 34~Kg of liquid xenon.
 
-%brief explaination of the signature, selection cuts, few words about acceptances, image of signal region and control region.
-
-\begin{figure}[h]
+\begin{figure}[t!]
   \includegraphics[width=\linewidth]{images/bkg_in_sr.png}
@@
 
-\begin{figure}[h]
-  \includegraphics[width=\linewidth]{images/wimp_in_sr.png}
-  \caption{Signal region and control region, for WIMP of mass 100~GeV.}
-  \label{fig:SR2}
-\end{figure}
-
 \subsection{Signal Simulation} 
 %description of the simulated signal, few words about cross checks MC matching.
-The detector response to inelastic scattering of WIMPs of different masses off $^{129}$Xe nucleus was simulated using an empirical model.
+The detector response to inelastic scattering of WIMPs  off $^{129}$Xe nucleus was simulated using an empirical model.
 The total deposited energy is divided into two independent contributions: the one related to the 39.6~KeV de-exitation photon and the one  relative to
-the simultaneous nuclear recoil (NR) of the Xe atom, the number of photons and charge yield detected is simulated separatedly for each contribution
+the simultaneous nuclear recoil of the xenon atom, the number of photons and charge yield detected is simulated separatedly for each contribution
 and then added togheter.
 
-The electronic recoil (ER) induced by the de-exitation photon is produced 
-The detector related light yield $L_y$ measured at 39.6~KeV with AmBe calibration has been found to have a large systematic uncertainty
-due to the contribution of the nuclear recoil, so the light yield used to describe the number of photon detected is the result of a fit 
-to data, corresponding to several lines, of the NEST model \cite{NEST,Geant1,Geant2}. The same model is used predict the charge yield at
-39.6~KeV whichis then scaled according to the detector's secondary scintillation factor $Y$, determined from detector response to single electrons \cite{SingleE},
-note that the corrected S2 observed by the bottom PMT array is used in this analysis. This is how the average $\mu_{cS1}$ and $\mu_{cS2}$ are obtained. 
-The detector resolution at 39.6~KeV is embedded in three parameter the standard deviation in cS1 and cS2, respectively $\sigma_{cs1}$ and $\sigma_{cs2}$ and 
-the correlation, $\rho$,  between cS1 and cS2. The correlation parameter is assumed to be independent of energy (at least in the considered range) and measured
-using the 164~KeV Xenon activated line by AmBe calibration source, this line is choosen since allows to disentangle efficiently contribution from nuclear recoil,
-the measured correlation is $\rho \, = \, -0.45 \pm 0.10$. Finally a two dimensional normal distribution, which is depicted in formula~\ref{f:2dgaus} except a normalization factor, 
-is employed as a probability density function $f(cS1,cS2)$ distribution of energy deposited from the 39.6~KeV photon.
+The ER induced by the de-exitation photon is simulated assuming a two dimensional normal distribution as its pdf in the cS1-cS2 plane, $f(cS1,cS2)$, 
+described (except a normalization factor) in equation~\ref{f:2dgaus}:
 \begin{multline}
@@
 \end{multline}
+where $\mu_{cS1}$ and $\mu_{cS2}$ 
+represents the average observed cS1 and cS2 given a 39.6~KeV ER, $\sigma_{cs1}$ and $\sigma_{cs2}$ are the standard deviation in cS1 and cS2 respectively,
+while $\rho$ stands for the correlation between cS1 and cS2.
+The detector related light yield $L_y$ measured at 39.6~KeV, necessary to evaluate the average number of photon detected ($\mu_{cS1}$),
+%with AmBe calibration has been found to have a large systematic uncertainty
+%due to the contribution of the nuclear recoil, so the light yield used to describe the number of photon detected 
+is obtained as the result of a NEST model~\cite{NEST,Geant1,Geant2} fit to data collected with several lines.  The same model is used to predict the charge yield at
+39.6~KeV which is then scaled according to the detector's secondary scintillation gain $Y$, determined from detector response to single electrons~\cite{SingleE}.
+Note that the corrected S2 observed by the bottom PMT array is used in this analysis.  
+The detector resolution at 39.6~KeV in cS1 and cS2 has been measured to be respectively 15.8\% and 14.7\% and used to extract the standard 
+deviations $\sigma_{cs1}$, $\sigma_{cs2}$.  The correlation parameter is assumed to be independent of energy (at least in the considered range) and measured
+using the 164~KeV xenon activated line by $^{124}$AmBe calibration data, this line is choosen since allows to disentangle efficiently contribution from nuclear recoil.
+The measured correlation is $\rho \, = \, -0.45 \pm 0.10$.
 
-The cS1 and cS2 distributions from NR contribution to the total signal are predicted starting from the nuclear recoil energy spectrum
-for inelastic interaction of a given WIMP mass \cite{inelastic_th}, the average cS1 and cS2 are given by formula~\ref{f:cs1} and~\ref{f:cs2} respectively,
-where $\mathcal{L}_{eff}$ is the LXe relative scintillation efficiency while $S_{ee} \, = \, 0.58$  and $S_{nr} \, = \, 0.95$ describe the scintillation 
+The cS1 and cS2 distributions from NR contribution are predicted starting from the nuclear recoil energy spectrum
+for WIMPs inelastic interaction~\cite{inelastic_th}. The average cS1 and cS2 are given by equations~\ref{f:cs1} and~\ref{f:cs2} respectively,
+where $\mathcal{L}_{eff}$ is the liquid xenon NR relative scintillation efficiency while $S_{ee} \, = \, 0.58$  and $S_{nr} \, = \, 0.95$ describe the scintillation 
 quenching due to the electric field \cite{ScintQuenching}. The parameterization and uncertainties of $\mathcal{L}_{eff}$ as a function of $E_{nr}$ are based on existing 
@@
 of $Q_{Y}(E_{nr})$ is taken from \cite{QY}.
-all detector related resolution effects are introduced following the prescriptions described in \cite{dataAnalysis}.
+Finally all detector related resolution effects are introduced following the prescriptions described in \cite{dataAnalysis}.
 
 \begin{equation}
-cS1_{nr} ~=~ E_{nr} \, \mathcal{L}_{eff}(E_{nr}) \, L_{Y} \, \frac{S_{nr}}{S_{ee}}
+cS1_{nr} ~=~ E_{nr} \, \mathcal{L}_{eff}(E_{nr}) \, L_{y} \, \frac{S_{nr}}{S_{ee}}
 \label{f:cs1}
@@
 %The two contribution are summed toghether in an event-by-event basis using random extraction from the two pdfs. 
-A 2D (cS1 versus cS2) acceptance map is applied to the signal pdf to reproduce data selection effects, single selection acceptances
-are computed using calibration samples of AmBe for all the selection criteria except the outer volume veto and the single interaction selections, 
-for which a detailed computation has been performed. The average acceptance value in the region of interest is of about $0.80 \pm 0.05$. 
-An example of signal model is in Figure~\ref{fig:SR} for a WIMP of 100~GeV. 
-The simulation of the 39.6~KeV line has been compared to AmBe data, for the comparison the proper AmBe nuclear recoil and acceptances
-were simulated, the model was found in very well in agreement with calibration source data showing the largest discrepancies within 
-statistical uncertainties.
+A 2D (cS1 versus cS2) acceptance map is applied to the signal pdf to reproduce data selection effects. Acceptances are computed separately for each selection 
+criteria using $^{124}$AmBe calibration sample, selections as the outer volume veto and the single scatter interaction represent an exception  and 
+a detailed computation has been performed in these cases. The acceptance average in the region of interest to about $0.80 \pm 0.05$. 
+Figure~\ref{fig:SR} shows an example of full simulated signal model for a WIMP of 100~GeV mass.
+
+The signal simulation procedure has been validated reproducing the 39.6~KeV xenon line from interaction due to
+$^{124}$AmBe source and has been compared to data. For the comparison the proper  $^{124}$AmBe nuclear recoil and acceptances
+were simulated. The simulated events were found in agreement  with calibration data within statistical uncertainties.
+
+\begin{figure}[t!]
+  \includegraphics[width=\linewidth]{images/wimp_in_sr.png}
+  \caption{Signal region and control region, for WIMP of mass 100~GeV.}
+  \label{fig:SR2}
+\end{figure}
 
@@
 
-The expected background in the region of interest is mainly caused by material radioactivity, mainly photons that 
-interact via compton scattering, background due to activation of Xe 39.6 line from radiogenic neutrons is found to be negligible.
-To model this background we use data from $^{60}$Co calibration campaign, the assumption is
-that the $^{60}$Co data are representative of the density in cS1-cS2 plane of the background. The calibration sample events
-in the ROI amount to  22225 events, this yield is then scaled to data according to a measured background scale factor $\tau_{bkg}$.
+The main expected background contribution in the region of interest is due material radioactivity, composed mainly by photons  
+interacting via compton scattering. Background contribution due to the activation of the xenon 39.6~KeV line from radiogenic neutrons is expected to be negligible.
+The background is modeled using data from $^{60}$Co calibration campaign, which are assumed to well represent the background density distribution 
+in the cS1-cS2 plane.
 
-The scale factor is measured in the two control regions shown in Figure~\ref{fig:SR} and labelled CR1 and CR2, the two control 
+The calibration sample yields  about 22'000 events in the ROI, these are then scaled to data according to a measured background scale factor $\tau_{bkg}$.
+The scale factor is measured in the two control regions shown in Figure~\ref{fig:SR} and labelled CR1 and CR2. The two control 
 regions give compatible results and the computed average is $\tau_{bkg} \, =  \, 0.034 \pm 0.002 $, where the reported uncertainty 
@@
 data from $^{232}$Th calibration campaign, the largest deviation between the two shapes is within 4\%. An additional systematic
-uncertainty of 4\% has been applied to the expected background yield of each subregion of the ROI.
+uncertainty of 4\% has been applied to the expected background yield of each sub-region of the ROI.
 
@@
 
-Uncertainties on the total prediction of background events arise from the relative uncertainties on the measure of the normalization 
-factor $\tau_{bkg}$ and amount to 6\%, while uncertainties arising from radiogenic neutrons contributions are neglected. 
-Uncretainty on the shape of the predicted bakground distribution are assesed by reporting the maximal discrepancy in the ROI between
-the $^{60}$Co and $^{232}$Th calibration samples, according to this it is assigned to the expected yield of each subregion a 4\% uncertainty,
-uncertainty belonging to different regions are considered independent from each other.
+%FIXME: maybe change region definitions in order to have the sub-region 9 labelled as 7, so the signal would "nicely" look like a bump.
+\begin{figure}[t!]
+  \includegraphics[width=\linewidth]{images/wimp_sys_unc.png}
+  \caption{Signal region, uncertainties for WIMP of mass 100~GeV.}
+  \label{fig:unc}
+\end{figure}
+
+Uncertainties on the total prediction of background events arise from the uncertainty on the measure of the normalization 
+factor, $\tau_{bkg}$, and amount to 6\%, contribution of radiogenic neutrons are neglected. 
+Systematic uncretainty on the shape of the predicted bakground distribution are assesed by the maximal discrepancy in the ROI between
+the $^{60}$Co and $^{232}$Th calibration samples, a 4\% systematic additional to statistical uncertainty is assigned to the expected yield of each sub-region,
+note that uncertainties belonging to different sub-regions are considered independent from each other.
 %It is important not only to describe correctly the expected total background but also its distribution
@@
 Signal model, Energy scale uncertainties.... Uncertainties related to energy scale and more generally to detector response 
-are taken into account by relative uncertainties on the measure of $L_Y$,$\mathcal{L}_{eff}$,$Y$, $Q_Y$ and $\rho$. Has been shown 
+are taken into account by relative uncertainties on the measure of $L_y$,$\mathcal{L}_{eff}$,$Y$, $Q_Y$ and $\rho$. Has been shown 
 by the simulation that these type of uncertainty affect the total signal yield in the ROI by less than a percent for a wide range of masses,
@@
 All the uncertainties discussed here are threated as nuissance parameter in the likelihood, which are contrained by a gaussian distribution.
-
-\begin{figure}[h]
-  \includegraphics[width=\linewidth]{images/wimp_sys_unc.png}
-  \caption{Signal region, uncertainties for WIMP of mass 100~GeV.}
-  \label{fig:unc}
-\end{figure}

### 2017-01-09 Inelastic/inelastic_main.tex
some small edit
first version of signal model
Some changes

@@
  reprint,
-%superscriptaddress,
+superscriptaddress,
 %groupedaddress,
@@
 ]{revtex4-1}
+%]{article}
 
+\usepackage{color}
 \usepackage{graphicx}% Include figure files
@@
 \usepackage{bm}% bold math
+%\usepackage{multicol}
 %\usepackage{hyperref}% add hypertext capabilities
@@
 
+%\usepackage[sorting=none]{biblatex}
+\usepackage{lineno}
+
+\newcommand{\assergi}{\affiliation{INFN, Laboratori Nazionali del Gran Sasso, Assergi, 67100, Italy}}
+\newcommand{\bologna}{\affiliation{University of Bologna and INFN-Bologna, Bologna, Italy}}
+\newcommand{\columbia}{\affiliation{Physics Department, Columbia University, New York, NY 10027, USA}}
+\newcommand{\coimbra}{\affiliation{Department of Physics, University of Coimbra, R. Larga, 3004-516, Coimbra, Portugal}}
+\newcommand{\heidelberg}{\affiliation{Max-Planck-Institut f\"ur Kernphysik, Saupfercheckweg 1, 69117 Heidelberg, Germany}}
+\newcommand{\houston}{\affiliation{Department of Physics and Astronomy, Rice University, Houston, TX 77005 - 1892, USA}}
+\newcommand{\laquila}{\affiliation{Department of Physics, University of L'Aquila, 67010, Italy}}
+\newcommand{\losangeles}{\affiliation{Physics \& Astronomy Department, University of California, Los Angeles, USA}}
+\newcommand{\mainz}{\affiliation{Institut f\"ur Physik, Johannes Gutenberg Universit\"at Mainz, 55099 Mainz, Germany}}
+\newcommand{\munster}{\affiliation{Institut f\"ur Kernphysik, Wilhelms-Universit\"at M\"unster, 48149 M\"unster, Germany}}
+\newcommand{\nikhef}{\affiliation{Nikhef  and the University of Amsterdam, Science park, Amsterdam, Netherlands}}
+\newcommand{\purdue}{\affiliation{Department of Physics, Purdue University, West Lafayette, IN 47907, USA}}
+\newcommand{\shanghai}{\affiliation{Department of Physics, Shanghai Jiao Tong University, Shanghai, 200240, China}}
+\newcommand{\subatech}{\affiliation{SUBATECH, Ecole des Mines de Nantes, CNRS/In2p3, Universit\'e de Nantes, 44307 Nantes, France}}
+\newcommand{\torino}{\affiliation{University of Torino and INFN-Torino, Torino, Italy}}
+\newcommand{\weizmann}{\affiliation{Department of Particle Physics and Astrophysics, Weizmann Institute of Science, 76100 Rehovot, Israel}}
+\newcommand{\zurich}{\affiliation{Physics Institute, University of Z\"{u}rich, Winterthurerstr. 190, CH-8057, Switzerland}}
+%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{document}
 
-%\preprint{APS/123-QED}
+\title{Search for WIMP Inelastic Scattering Off Xenon Nuclei With Xenon100 Data}% Force line breaks with \\
 
-\title{Search for WIMP Inelastic Scattering Off Xenon Nuclei With Xenon100 Data}% Force line breaks with \\
-\thanks{}%
+\author{M.~Alfonsi}\nikhef
+\author{E.~Aprile}\columbia 
+\author{K.~Arisaka}\losangeles
+\author{F.~Arneodo}\assergi
+\author{C.~Balan}\coimbra
+\author{L.~Baudis}\zurich
+\author{A.~Behrens}\zurich
+\author{P.~Beltrame}\losangeles
+\author{K.~Bokeloh}\munster
+\author{E.~Brown}\munster
+\author{G.~Bruno}\assergi
+\author{R.~Budnik}\columbia 
+\author{J.~M.~R.~Cardoso}\coimbra
+\author{W.-T.~Chen}\subatech
+\author{B.~Choi}\columbia
+\author{H.~Contreras}\columbia
+\author{J.~P.~Cussonneau}\subatech
+\author{M.~P.~Decowski}\nikhef
+\author{E.~Duchovni}\weizmann
+\author{S.~Fattori}\mainz
+\author{A.~D.~Ferella}\zurich
+\author{W.~Fulgione}\torino
+\author{F.~Gao}\shanghai
+\author{M.~Garbini}\bologna
+\author{K.-L.~Giboni}\columbia
+\author{L.~W.~Goetzke}\columbia
+\author{C.~Grignon}\mainz
+\author{E.~Gross}\weizmann
+\author{W.~Hampel}\heidelberg
+\author{H.~Kettling}\munster
+\author{A.~Kish}\zurich
+\author{J.~Lamblin}\subatech
+\author{H.~Landsman}\weizmann
+\author{R.~F.~Lang}\purdue\columbia
+\author{M.~Le~Calloch}\subatech
+\author{C.~Levy}\munster
+\author{K.~E.~Lim}\columbia
+\author{Q.~Lin}\shanghai
+\author{S.~Lindemann}\heidelberg
+\author{M.~Lindner}\heidelberg
+\author{J.~A.~M.~Lopes}\coimbra
+\author{K.~Lung}\losangeles
+\author{T.~Marrod\'an~Undagoitia} \email{marrodan@physik.uzh.ch} \zurich%[Email:]
+\author{F.~V.~Massoli}\bologna
+\author{Y.~Mei}\houston\mainz
+\author{A.~J.~Melgarejo~Fernandez}\columbia
+\author{Y.~Meng}\losangeles
+\author{A.~Molinario}\torino
+\author{E.~Nativ}\weizmann
+\author{K.~Ni}\shanghai
+\author{U.~Oberlack}\houston\mainz
+\author{S.~E.~A.~Orrigo}\coimbra
+\author{E.~Pantic} \email{pantic@physics.ucla.edu} \losangeles
+\author{D.~P\"atzold}\mainz
+\author{R.~Persiani}\bologna
+\author{G.~Plante}\columbia
+\author{N.~Priel}\weizmann
+\author{A.~C.~C.~Ribeiro}\coimbra
+\author{A.~Rizzo}\columbia
+\author{S.~Rosendahl}\munster
+\author{J.~M.~F.~dos Santos}\coimbra
+\author{G.~Sartorelli}\bologna
+\author{J.~Schreiner}\heidelberg
+\author{M.~Schumann}\zurich
+\author{L.~Scotto~Lavina}\subatech
+\author{P.~R.~Scovell}\losangeles
+\author{M.~Selvi}\bologna
+\author{P.~Shagin}\houston
+\author{H.~Simgen}\heidelberg
+\author{A.~Teymourian}\losangeles
+\author{D.~Thers}\subatech
+\author{O.~Vitells}\weizmann
+\author{H.~Wang}\losangeles
+\author{M.~Weber}\heidelberg
+\author{C.~Weinheimer}\munster
 
-\author{Ann Author}
- \altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\
-\author{Second Author}%
- \email{Second.Author@institution.edu}
-\affiliation{%
- Authors' institution and/or address\\
- This line break forced with \textbackslash\textbackslash
-}%
+\collaboration{The XENON100 Collaboration}\noaffiliation
 
-\collaboration{XENON Collaboration}%\noaffiliation
-
-\author{Authors}
-% \homepage{http://www.Second.institution.edu/~Charlie.Author}
-\affiliation{
- Second institution and/or address\\
- This line break forced% with \\
-}%
-\affiliation{
- Affiliation
-}%
-
-%\collaboration{CLEO Collaboration}%\noaffiliation
-
-\date{\today}% It is always \today, today,
-             %  but any date may be explicitly specified
+\date{\today}
 
 \begin{abstract}
-
+	Some nice abstract here.....
 \end{abstract}
 
-%\pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
-                             % Classification Scheme.
 %\keywords{Suggested keywords}%Use showkeys class option if keyword
@@
 %\tableofcontents
+
+\linenumbers
 
@@
 
-\subsubsection{Citations}
-%Because REV\TeX\ uses the \verb+natbib+ package of Patrick Daly, 
-%the entire repertoire of commands in that package are available for your document;
-%see the \verb+natbib+ documentation for further details. Please note that
-%REV\TeX\ requires version 8.31a or later of \verb+natbib+.
+%\input{biblio.tex}
 
+\bibliography{inelastic_main} 
+\bibliographystyle{unsrt}
+%\printbibliography
 \end{document}
-%
-% ****** End of file apssamp.tex ******

### 2017-01-09 Inelastic/intro.tex
Some changes

@@
 hypothesis which is currently being tested by several direct and indirect detection experiment. 
+\textcolor{blue}{some citation missing.}
 
 Most of direct detection searches focuses on  elastic scattering of dark matter particles off nuclei.
-In this analysis instead we explore an inelastic scattering process, we consider the $^{129}\text{Xe}$ isotope being excited to a low-lying state
+In this analysis instead an inelastic scattering process is explored, we consider the $^{129}\text{Xe}$ isotope being excited to a low-lying state
 with subsequent prompt de-excitation via the emission a photon. This isotope is an excellent target
 since its abundance in natural xenon is of 26.4\% and a relatively low energy is necessary to excite its $3/2+$ state above the $1/2+$
-spin ground state.
+spin ground state. These type of processes were previously studied in detail for liquid xenon detector in~\cite{inelastic_th}.
 Inelastic WIMP-nucleus scattering in xenon is complementary to elastic scattering for spin-dependent interactions,
@@
 
-To add: sentences about detector stability, science run data used, Ly and Y measurements used.
+\textcolor{blue}{To add: describe and explain cS1 and cS2 definitions, some sentences about detector stability, maybe science run data used and calibration campaign goes here, 
+maybe Ly and Y measurements used goes here.}

### 2017-01-09 Inelastic/analysis.tex
first version to ranny

@@
 The inelastic scattering of a WIMP with the nucleus of $^{129}$Xe produces an energy deposit via nuclear recoil with subsequent emission of  
-a 39.6~KeV de-exitation photon. 
+a 39.6~keV de-exitation photon. 
 The largest fraction of the energy released in the event is via electronic recoil due to the emitted photon, this represents an
 unusual signature for this kind of detector and brings the possible signal to overlay a phase space region with large backgrounds.
-The choosen region of interest for this analysis surrounds the 39.6~KeV xenon line in the cS1-cS2 plane which is further divided into
+The choosen region of interest for this analysis surrounds the 39.6~keV xenon line in the cS1-cS2 plane which is further divided into
 sub-regions, as shown in Figure~\ref{fig:SR}.
@@
 %only few modification have been designed specifically for this analysis and discussed below. 
-In particular, the selection on S2 width as a function of drift time has been optimized on a sample of events selected from the 39.6~KeV line
+In particular, the selection on S2 width as a function of drift time has been optimized on a sample of events selected from the 39.6~keV line
 and set to a 95\% acceptance on these. Events are required to be single scatter by applying a threshold on the 
@@
 The detector response to inelastic scattering of WIMPs  off $^{129}$Xe nucleus was simulated using an empirical model.
-The total deposited energy is divided into two independent contributions: the one related to the 39.6~KeV de-exitation photon and the one  relative to
+The total deposited energy is divided into two independent contributions: the one related to the 39.6~keV de-exitation photon and the one  relative to
 the simultaneous nuclear recoil of the xenon atom, the number of photons and charge yield detected is simulated separatedly for each contribution
@@
 where $\mu_{cS1}$ and $\mu_{cS2}$ 
-represents the average observed cS1 and cS2 given a 39.6~KeV ER, $\sigma_{cs1}$ and $\sigma_{cs2}$ are the standard deviation in cS1 and cS2 respectively,
+represents the average observed cS1 and cS2 given a 39.6~keVee , $\sigma_{cs1}$ and $\sigma_{cs2}$ are the standard deviation in cS1 and cS2 respectively,
 while $\rho$ stands for the correlation between cS1 and cS2.
-The detector related light yield $L_y$ measured at 39.6~KeV, necessary to evaluate the average number of photon detected ($\mu_{cS1}$),
+The detector related light yield $L_y$ measured at 39.6~keV, necessary to evaluate the average number of photon detected ($\mu_{cS1}$),
 %with AmBe calibration has been found to have a large systematic uncertainty
@@
 is obtained as the result of a NEST model~\cite{NEST,Geant1,Geant2} fit to data collected with several lines.  The same model is used to predict the charge yield at
-39.6~KeV which is then scaled according to the detector's secondary scintillation gain $Y$, determined from detector response to single electrons~\cite{SingleE}.
+39.6~keV which is then scaled according to the detector's secondary scintillation gain $Y$, determined from detector response to single electrons~\cite{SingleE}.
 Note that the corrected S2 observed by the bottom PMT array is used in this analysis.  
-The detector resolution at 39.6~KeV in cS1 and cS2 has been measured to be respectively 15.8\% and 14.7\% and used to extract the standard 
+The detector resolution at 39.6~keV in cS1 and cS2 has been measured to be respectively 15.8\% and 14.7\% and used to extract the standard 
 deviations $\sigma_{cs1}$, $\sigma_{cs2}$.  The correlation parameter is assumed to be independent of energy (at least in the considered range) and measured
-using the 164~KeV xenon activated line by $^{124}$AmBe calibration data, this line is choosen since allows to disentangle efficiently contribution from nuclear recoil.
+using the 164~keV xenon activated line by $^{124}$AmBe calibration data, this line is choosen since allows to disentangle efficiently contribution from nuclear recoil.
 The measured correlation is $\rho \, = \, -0.45 \pm 0.10$.
@@
 
-The signal simulation procedure has been validated reproducing the 39.6~KeV xenon line from interaction due to
+The signal simulation procedure has been validated reproducing the 39.6~keV xenon line from interaction due to
 $^{124}$AmBe source and has been compared to data. For the comparison the proper  $^{124}$AmBe nuclear recoil and acceptances
@@
 The main expected background contribution in the region of interest is due material radioactivity, composed mainly by photons  
-interacting via compton scattering. Background contribution due to the activation of the xenon 39.6~KeV line from radiogenic neutrons is expected to be negligible.
+interacting via compton scattering. Background contribution due to the activation of the xenon 39.6~keV line from radiogenic neutrons is expected to be negligible.
 The background is modeled using data from $^{60}$Co calibration campaign, which are assumed to well represent the background density distribution 
@@
 
-Signal model, Energy scale uncertainties.... Uncertainties related to energy scale and more generally to detector response 
-are taken into account by relative uncertainties on the measure of $L_y$,$\mathcal{L}_{eff}$,$Y$, $Q_Y$ and $\rho$. Has been shown 
-by the simulation that these type of uncertainty affect the total signal yield in the ROI by less than a percent for a wide range of masses,
-however they greatly affects the pdf of the signal model in the ROI. For each WIMP mass several signal simulation sample are produced 
-warying these parameter respectively $\pm 1 \sigma$, for each region is computed an uncertainty by adding in quadrature the variations
-%FIXME: explain this better, the up variation are separated from down variations and added togheter
-with respect to nominal of each case, Figure~\ref{fig:unc} is an example of such a systematic uncertainty computation for WIMP mass of 100~GeV.
-
 Uncertainty on the total yield of the signal arising from uncertainties on the selection acceptance are found to be very weakly dependent on 
@@
 
+Uncertainties on the energy scale and, more generally, related to detector response 
+are parametrized using the respective uncertainties on the measure of $L_y$, $\mathcal{L}_{eff}$, $Y$, $Q_Y$ and $\rho$. The simulation shows 
+that these type of uncertainties mainly affect the pdf of the signal model in the ROI, and very weakly the total signal yield. 
+%For each WIMP mass we simulate several signal pseudo-sample, which are produced varying the model parameters  respectively of $\pm 1$ standard deviation. 
+They are taken into account by simulating several signal pseudo-sample for each WIMP mass, the pseudo-sampleis are produced varying the model parameters respectively of $\pm 1$ standard deviation. 
+For each sub-region is then computed an overall uncertainty by adding in quadrature the variations of each pseudo-sample 
+%FIXME: explain this better, the up variation are separated from down variations and added togheter
+with respect to nominal. Figure~\ref{fig:unc} is an example of such a systematic uncertainty computation for WIMP mass of 100~GeV.
+
 %FIXME: express this in an understandable way
-All the uncertainties discussed here are threated as nuissance parameter in the likelihood, which are contrained by a gaussian distribution.
+All the uncertainties discussed here are parametrized within a binned profiled likelihood function using the framework~\cite{roostat,roofit}.
+All parameters related to systematic uncertainties are assumed to be normally distributed.

### 2017-01-09 Inelastic/results.tex
Some changes
first version to ranny

--- 2016-11-28 Inelastic/results.tex
@@
 \section{Results}
-No evidence of dark matter.
+In an exposure of 34~kg of liquid xenon and 224.6~live days of data a yield of 764 events are found in the region of interest,
+this is compatible with the expectation of $756 \, \pm \, 5^{(stat.)} \, \pm 55^{(syst.)}$ events from the background only hypothesis. 
+Figure~\ref{fig:dataVSbkg} shows how these events are distributed in the region of interest, the bottom panel shows the ratio
+between data and expected background, where the gray and orange shaded areas represent respectively statistical and systematic uncertainty 
+on the background expectation.
+%The distribution of events from data are compared to the background expectation in Figure~\ref{fig:dataVSbkg} and with the relative
+%uncertainties.  
+This result is interpreted via a binned profiled likelihood approach by means of the test statistic $\tilde{q}$
+and its asymptotic distributions described in \cite{asympt}.
 
-\begin{figure}[h]
+Assuming  an isothermal WIMP halo with a local density of $\rho_{\chi} \, = \, 0.3$~$GeV/cm^3$ , a local circular veloc-
+ity of $v_0 \,= \, 220$~km/s, and a galactic escape velocity of $v_{esc} \, = \, 544$ km/s, 
+\textcolor{blue}{other assumptions...,} a 90\% CL$_s$~\cite{cls} confidence level limit is  
+computed on the spin dependent inelastic WIMP-nucleon cross section, $\sigma_{ine}$, as a function of the WIMP mass, $m_{\chi}$, and shown in Figure~\ref{fig:limits}.
+The expecetd median sensitivity is reported with its relative one (green area) and two (yellow area) standard deviation uncertainty.
+A limit is set on $\sigma_{ine}$ to $3.3 \times 10^{-38} ~cm^{2}$ for a WIMP of mass 100~GeV. This limit is compared with
+\textcolor{blue}{decide which other experiment to plot.}
+
+\newpage
+\begin{figure}[t!]
   \includegraphics[width=\linewidth]{images/data_vs_bkg.png}
@@
 
-\begin{figure}[h!]
+\begin{figure}[h]
   \includegraphics[width=\linewidth]{images/limit_reb.png}
@@
 \end{figure}
+
+\newpage

### 2017-01-16 Inelastic/analysis.tex
Version 0.1 to EB

@@
 The inelastic scattering of a WIMP with the nucleus of $^{129}$Xe produces an energy deposit via nuclear recoil with subsequent emission of  
-a 39.6~keV de-exitation photon. 
+a 39.6~keV de-excitation photon. 
 The largest fraction of the energy released in the event is via electronic recoil due to the emitted photon, this represents an
 unusual signature for this kind of detector and brings the possible signal to overlay a phase space region with large backgrounds.
-The choosen region of interest for this analysis surrounds the 39.6~keV xenon line in the cS1-cS2 plane which is further divided into
-sub-regions, as shown in Figure~\ref{fig:SR}.
+The chosen region of interest (ROI) for this analysis surrounds the 39.6~keV xenon line in the cS1-cS2 plane and is further divided into
+sub-regions, as shown in Figure~\ref{fig:SR} and~\ref{fig:SR2}.
 
-Events are asked, other than falling in the defined region of interest, to fullfill several selection criteria which can be sumarized as:
-selection aimed to reduce noise impact including energy (S1) and S2 thresholds, events must be of single scatter nature and fall 
-into a predefined fiducial volume. This analysis follows the selection criteria described in detail in \cite{dataAnalysis} for Run-II, 
-with only few exceptions. 
+Events are asked, other than falling in the defined region of interest, to fulfill several selection criteria which can be summarized as:
+selection aimed to reduce noise impact and including energy (S1) and S2 thresholds, veto of events with energy release in the detector's outer volume, 
+and additionally, events must be of single scatter nature and fall into a predefined fiducial volume. This analysis follows the 
+selection criteria described in detail in \cite{dataAnalysis} for Run-II, with only few exceptions reported in what follows. 
 %only few modification have been designed specifically for this analysis and discussed below. 
-In particular, the selection on S2 width as a function of drift time has been optimized on a sample of events selected from the 39.6~keV line
+The selection on S2 width as a function of drift time has been optimized on a sample of events selected from the 39.6~keV line
 and set to a 95\% acceptance on these. Events are required to be single scatter by applying a threshold on the 
@@
 The detector response to inelastic scattering of WIMPs  off $^{129}$Xe nucleus was simulated using an empirical model.
-The total deposited energy is divided into two independent contributions: the one related to the 39.6~keV de-exitation photon and the one  relative to
-the simultaneous nuclear recoil of the xenon atom, the number of photons and charge yield detected is simulated separatedly for each contribution
-and then added togheter.
+The total deposited energy is divided into two independent contributions: one related to the 39.6~keV de-excitation photon and the other  relative to
+the simultaneous nuclear recoil of the xenon atom. The number of photons and charge yield detected is simulated separately for each contribution
+and then added together.
 
-The ER induced by the de-exitation photon is simulated assuming a two dimensional normal distribution as its pdf in the cS1-cS2 plane, $f(cS1,cS2)$, 
-described (except a normalization factor) in equation~\ref{f:2dgaus}:
+The distribution in the cS1-cS2 plane of an ER induced by the de-excitation photon is simulated assuming a two dimensional normal pdf, $f(cS1,cS2)$, 
+described except a normalization factor in equation~\ref{f:2dgaus}:
 \begin{multline}
@@
 while $\rho$ stands for the correlation between cS1 and cS2.
-The detector related light yield $L_y$ measured at 39.6~keV, necessary to evaluate the average number of photon detected ($\mu_{cS1}$),
+The detector related light yield $L_y$  at 39.6~keV, necessary to evaluate the average number of photon detected ($\mu_{cS1}$),
 %with AmBe calibration has been found to have a large systematic uncertainty
@@
 39.6~keV which is then scaled according to the detector's secondary scintillation gain $Y$, determined from detector response to single electrons~\cite{SingleE}.
-Note that the corrected S2 observed by the bottom PMT array is used in this analysis.  
 The detector resolution at 39.6~keV in cS1 and cS2 has been measured to be respectively 15.8\% and 14.7\% and used to extract the standard 
 deviations $\sigma_{cs1}$, $\sigma_{cs2}$.  The correlation parameter is assumed to be independent of energy (at least in the considered range) and measured
-using the 164~keV xenon activated line by $^{124}$AmBe calibration data, this line is choosen since allows to disentangle efficiently contribution from nuclear recoil.
+using the 164~keV xenon activated line by $^{124}$AmBe calibration data, this line is chosen since allows to disentangle efficiently contribution from nuclear recoil.
 The measured correlation is $\rho \, = \, -0.45 \pm 0.10$.
@@
 The cS1 and cS2 distributions from NR contribution are predicted starting from the nuclear recoil energy spectrum
-for WIMPs inelastic interaction~\cite{inelastic_th}. The average cS1 and cS2 are given by equations~\ref{f:cs1} and~\ref{f:cs2} respectively,
-where $\mathcal{L}_{eff}$ is the liquid xenon NR relative scintillation efficiency while $S_{ee} \, = \, 0.58$  and $S_{nr} \, = \, 0.95$ describe the scintillation 
+of WIMPs inelastic interaction~\cite{inelastic_th}. The average cS1 and cS2 are given by equations~\ref{f:cs1} and~\ref{f:cs2} respectively,
+where $\mathcal{L}_{eff}$ is the liquid xenon NR relative scintillation efficiency, while $S_{ee} \, = \, 0.58$  and $S_{nr} \, = \, 0.95$ describe the scintillation 
 quenching due to the electric field \cite{ScintQuenching}. The parameterization and uncertainties of $\mathcal{L}_{eff}$ as a function of $E_{nr}$ are based on existing 
@@
 
-The pdf of the ER and NR contributions are then convoluted toghether to obtain the overall pdf of the signal.
-%The two contribution are summed toghether in an event-by-event basis using random extraction from the two pdfs. 
+The pdf of the ER and NR contributions are then convoluted together to obtain the overall pdf of the signal.
+%The two contribution are summed together in an event-by-event basis using random extraction from the two pdfs. 
 A 2D (cS1 versus cS2) acceptance map is applied to the signal pdf to reproduce data selection effects. Acceptances are computed separately for each selection 
 criteria using $^{124}$AmBe calibration sample, selections as the outer volume veto and the single scatter interaction represent an exception  and 
-a detailed computation has been performed in these cases. The acceptance average in the region of interest to about $0.80 \pm 0.05$. 
+a dedicated computation has been performed in these cases. The selections acceptance average in the region of interest to about $0.80 \pm 0.05$. 
 Figure~\ref{fig:SR} shows an example of full simulated signal model for a WIMP of 100~GeV mass.
@@
 The signal simulation procedure has been validated reproducing the 39.6~keV xenon line from interaction due to
-$^{124}$AmBe source and has been compared to data. For the comparison the proper  $^{124}$AmBe nuclear recoil and acceptances
+$^{124}$AmBe source and has been compared to data. For this comparison the proper  $^{124}$AmBe nuclear recoil and acceptances
 were simulated. The simulated events were found in agreement  with calibration data within statistical uncertainties.
@@
 
-The main expected background contribution in the region of interest is due material radioactivity, composed mainly by photons  
-interacting via compton scattering. Background contribution due to the activation of the xenon 39.6~keV line from radiogenic neutrons is expected to be negligible.
-The background is modeled using data from $^{60}$Co calibration campaign, which are assumed to well represent the background density distribution 
+The main expected background contribution in the region of interest is due to eviromental and material radioactivity, its composition is mainly
+represented by Compton scattering photons. Background contribution due to the activation of the xenon 39.6~keV line from radiogenic neutrons is expected to be negligible.
+
+The background is modeled using data from the $^{60}$Co calibration campaign, which are assumed to well represent the background density distribution 
 in the cS1-cS2 plane. 
-
-The calibration sample yields  about 22'000 events in the ROI, these are then scaled to data according to a measured background scale factor $\tau_{bkg}$.
-The scale factor is measured in the two control regions shown in Figure~\ref{fig:SR} and labelled CR1 and CR2. The two control 
+The calibration sample yields  about 22'000 events in the ROI, these are then scaled to data according to a measured scale factor $\tau_{bkg}$.
+This scale factor, which is merely the ratio between the data and calibration sample yields, is measured in the two control regions shown in Figure~\ref{fig:SR} and labelled CR1 and CR2.
+The two control
 regions give compatible results and the computed average is $\tau_{bkg} \, =  \, 0.034 \pm 0.002 $, where the reported uncertainty 
@@
 
-The distribution of the calibration sample has been compared to the data of the sience run in the two control regions,
-agreement is found within statistical uncertainties. $^{60}$Co calibration data have been compared in the region of interest to  
+The distribution of the calibration sample has been compared to the data of the science run in the two control regions,
+agreement is found within statistical uncertainties. Furthermore, $^{60}$Co calibration data have been compared in the region of interest to  
 data from $^{232}$Th calibration campaign, the largest deviation between the two shapes is within 4\%. An additional systematic
@@
 factor, $\tau_{bkg}$, and amount to 6\%, contribution of radiogenic neutrons are neglected. 
-Systematic uncretainty on the shape of the predicted bakground distribution are assesed by the maximal discrepancy in the ROI between
-the $^{60}$Co and $^{232}$Th calibration samples, a 4\% systematic additional to statistical uncertainty is assigned to the expected yield of each sub-region,
-note that uncertainties belonging to different sub-regions are considered independent from each other.
+Systematic uncertainty on the shape of the predicted background distribution are assessed by the maximal discrepancy in the ROI between
+the $^{60}$Co and $^{232}$Th calibration samples, a 4\% systematic additional to statistical uncertainty is assigned to the expected yield of each sub-region.
+Note that uncertainties belonging to different sub-regions are considered independent from each other.
 %It is important not only to describe correctly the expected total background but also its distribution
 
-Uncertainty on the total yield of the signal arising from uncertainties on the selection acceptance are found to be very weakly dependent on 
-the WIMP mass, an overall 6\% acceptance uncertainty is then applied to all WIMP hypotesis.
+Uncertainty on the total yield of signal arising from selections acceptance uncertainties are found to be very weakly dependent on 
+the WIMP mass, an overall 6\% acceptance uncertainty is then applied to all WIMPs hypothesis.
 
 Uncertainties on the energy scale and, more generally, related to detector response 
-are parametrized using the respective uncertainties on the measure of $L_y$, $\mathcal{L}_{eff}$, $Y$, $Q_Y$ and $\rho$. The simulation shows 
+are parameterized using the respective uncertainties on the measure of $L_y$, $\mathcal{L}_{eff}$, $Y$, $Q_Y$ and $\rho$. The simulation shows 
 that these type of uncertainties mainly affect the pdf of the signal model in the ROI, and very weakly the total signal yield. 
 %For each WIMP mass we simulate several signal pseudo-sample, which are produced varying the model parameters  respectively of $\pm 1$ standard deviation. 
-They are taken into account by simulating several signal pseudo-sample for each WIMP mass, the pseudo-sampleis are produced varying the model parameters respectively of $\pm 1$ standard deviation. 
+They are taken into account by simulating several signal pseudo-sample for each WIMP mass, the pseudo-samples are produced varying the model parameters respectively of $\pm 1$ standard deviation. 
 For each sub-region is then computed an overall uncertainty by adding in quadrature the variations of each pseudo-sample 
-%FIXME: explain this better, the up variation are separated from down variations and added togheter
-with respect to nominal. Figure~\ref{fig:unc} is an example of such a systematic uncertainty computation for WIMP mass of 100~GeV.
+%FIXME: explain this better, the up variation are separated from down variations and added together
+with respect to nominal. Figure~\ref{fig:unc} is an example of such a systematic uncertainty computation for a WIMP of 100~GeV mass.
 
 %FIXME: express this in an understandable way
-All the uncertainties discussed here are parametrized within a binned profiled likelihood function using the framework~\cite{roostat,roofit}.
+All the uncertainties discussed here are parameterized within a binned profiled likelihood function using the framework~\cite{roostat,roofit}.
 All parameters related to systematic uncertainties are assumed to be normally distributed.

### 2017-01-16 Inelastic/intro.tex
Version 0.1 to EB

--- 2016-11-28 Inelastic/intro.tex
@@
 hypothesis which is currently being tested by several direct and indirect detection experiment. 
+\textcolor{blue}{some citation missing.}
 
 Most of direct detection searches focuses on  elastic scattering of dark matter particles off nuclei.
-In this analysis instead we explore an inelastic scattering process, we consider the $^{129}\text{Xe}$ isotope being excited to a low-lying state
-with subsequent prompt de-excitation via the emission a photon. This isotope is an excellent target
+In this analysis instead an inelastic scattering process is explored: we consider the $^{129}\text{Xe}$ isotope being excited to a low-lying state
+with subsequent prompt de-excitation via the emission of a photon. This isotope is an excellent target
 since its abundance in natural xenon is of 26.4\% and a relatively low energy is necessary to excite its $3/2+$ state above the $1/2+$
-spin ground state.
+spin ground state. These type of processes were previously studied in detail for liquid xenon detectors in~\cite{inelastic_th}.
 Inelastic WIMP-nucleus scattering in xenon is complementary to elastic scattering for spin-dependent interactions,
-the former dominates the integrated rate above  $\simeq10$~keV of energy deposition.
-Furthermore, in the case of dark matter detection, this channel can be employed to asses whether the nature of the fundamental interaction
+the former dominating the integrated rate above  $\simeq10$~keV of energy deposition.
+Furthermore, in case of dark matter detection, this channel can be employed to asses whether the nature of the fundamental interaction
 is spin-dependent or not.
@@
 
-To add: sentences about detector stability, science run data used, Ly and Y measurements used.
+\textcolor{blue}{To add: describe and explain cS1 and cS2 definitions, some sentences about detector stability, maybe science run data used and calibration campaign goes here, 
+maybe Ly and Y measurements used goes here.} 
+Note that the corrected S2 observed by the bottom PMT array is used in this analysis.

### 2017-01-16 Inelastic/results.tex
Version 0.1 to EB

--- 2016-11-28 Inelastic/results.tex
@@
 \section{Results}
-No evidence of dark matter.
+Using an exposure of 34~kg of liquid xenon and 224.6~live days of data a yield of 764 events is observed  in the region of interest,
+this is compatible with the expectation of $756 \, \pm \, 5^{(stat.)} \, \pm 55^{(syst.)}$ events from the background only hypothesis. 
+Figure~\ref{fig:dataVSbkg} shows how these events are distributed in the region of interest, the bottom panel shows the ratio
+between data and expected background, where the gray and orange shaded areas represent respectively statistical and systematic uncertainty 
+on the background expectation.
+%The distribution of events from data are compared to the background expectation in Figure~\ref{fig:dataVSbkg} and with the relative
+%uncertainties.
 
-\begin{figure}[h]
+This result is interpreted via a binned profiled likelihood approach by means of the test statistic $\tilde{q}$
+and its asymptotic distributions described in \cite{asympt}. 
+Assuming  an isothermal WIMP halo with a local density of $\rho_{\chi} \, = \, 0.3$~$GeV/cm^3$ , a local circular velocity of $v_0 \,= \, 220$~km/s, and a galactic escape velocity of $v_{esc} \, = \, 544$ km/s,
+\textcolor{blue}{other assumptions...,} a 90\% CL$_s$~\cite{cls} confidence level limit is  
+computed on the spin dependent inelastic WIMP-nucleon cross section, $\sigma_{inel}$, as a function of the WIMP mass, $m_{\chi}$, and shown in Figure~\ref{fig:limits}.
+The expected median sensitivity is reported with its relative one (green area) and two (yellow area) standard deviation uncertainty.
+A  limit is set on $\sigma_{inel}$ to $3.3 \times 10^{-38} ~cm^{2}$ at 90\% CL$_s$ confidence level for a WIMP of mass 100~GeV. This limit is compared with
+\textcolor{blue}{decide which other experiment to plot.}
+
+\newpage
+\begin{figure}[t!]
   \includegraphics[width=\linewidth]{images/data_vs_bkg.png}

### 2017-01-16 Inelastic/intro.tex
Laura's modifications to intro.tex

--- 2016-11-28 Inelastic/intro.tex
@@
 \section{\label{sec:level1} Introduction}
-Astrophysical evidence indicates that the dominant mass fraction of our Universe consists of some yet unknown form
-of dark matter. Well motivated models predict Dark Matter in the form of Weakly Interacting Massive Particles (WIMPs),
-hypothesis which is currently being tested by several direct and indirect detection experiment.
+Astrophysical and cosmological evidence indicates that the dominant mass fraction of our Universe consists of some yet unknown
+form of dark, or invisible matter. The dark matter could be made of new, yet undiscovered particles, and well-motivated
+theoretical models going beyond the Standard Model of particle physics predict the existence of Weakly Interacting Massive
+Particles (WIMPs), which are natural candidates for dark matter. This hypothesis is currently being tested by several direct
+and indirect detection experiments, as well as at the LHC~\cite{Bertone:2004pz,Baudis:2016qwx}.
 
-Most of direct detection searches focuses on  elastic scattering of dark matter particles off nuclei.
-In this analysis instead we explore an inelastic scattering process, we consider the $^{129}\text{Xe}$ isotope being excited to a low-lying state
-with subsequent prompt de-excitation via the emission a photon. This isotope is an excellent target
-since its abundance in natural xenon is of 26.4\% and a relatively low energy is necessary to excite its $3/2+$ state above the $1/2+$
-spin ground state.
-Inelastic WIMP-nucleus scattering in xenon is complementary to elastic scattering for spin-dependent interactions,
-the former dominates the integrated rate above  $\simeq10$~keV of energy deposition.
-Furthermore, in the case of dark matter detection, this channel can be employed to asses whether the nature of the fundamental interaction
-is spin-dependent or not.
+Most direct detection searches focus on elastic scattering of galactic dark matter particles off nuclei, where the keV-scale 
+nuclear recoil energy is to be detected~\cite{Baudis:2012ig,Baudis:2015mpa,Undagoitia:2015gya}. In this work, the 
+alternative process of inelastic scattering is explored, where a WIMP-nucleus scattering induces a transition to a low-lying 
+excited nuclear state. The experimental signature is a nuclear recoil detected together with the prompt de-excitation 
+photon~\cite{Ellis:1988nb}.
 
-\section{Xenon100 Detector}
-The Xenon100 experiment is a  dual phase liquid xenon TPC. For a given interaction in the liquid target this type of detector produces two separated signals,
-one proportional to the prompt scintillation (S1) the other to ionization (S2).
+We consider the $^{129}\text{Xe}$ isotope, which has an abundance of 26.4\% in natural xenon, and a lowest-lying 
+3/2$^{+}$ state at 36.6\,keV above the 1/2$^+$ gound state. The electromnagnetic nuclear decay has a half-life of 0.97\,s. 
+The sigantures of inelastic scattering in xenon have been studied in detail in~\cite{Baudis:2013bba}. It was found that this 
+channel is complementary to spin-dependent, elastic scattering, dominating the integrated rates above $\simeq10$\,keV energy 
+depositions. In addition, in case of a positive signal, the observation of inelastic scattering would provide a clear 
+indication of the spin-dependent nature of the fundamental interaction.
 
-To add: sentences about detector stability, science run data used, Ly and Y measurements used.
+\section{The XENON100 Detector}
+
+The XENON100 experiment operated a dual-phase (liquid and gas) xenon time projection chamber (TPC) at the Laboratori Nazionali 
+del Gran Sasso (LNGS) in Italy. It contained 161\,kg of xenon in total,  with  62\,kg in the active region of the TPC. These 
+were monitored by 242 low-radioactivity, UV-sensitive photomultiplier tubes (PMTs) arranged in two arrays, one in the liquid 
+and one in the gas. The PMTs detected the prompt scintillation (S1) and the delayed, proportional scintillation signal (S2) 
+created by a particle interacting in the active TPC region. The S2-signal is generated due to ionisation electrons, drifted 
+and extracted into the gas phase, where the proportional scintillation, or electroluminiscence, is produced. These photons 
+carry the $x-y$ information of the interaction site, while the $z-$information came from the drift time measurement. The TPC 
+thus yielded a three-dimensional event localisation, enabling to reject the majority of background events via fiducial volume 
+cuts, as well a multiple interactions, which are unlikely due to dark matter particles~\cite{Aprile:2011dd}. The ratio of 
+S2/S1 provided the basis for distinguishing between nuclear recoils (NRs), as induced by fast neutrons and expected from 
+elastic WIMP-nucleus scatters, and electronic recoils (ERs) produced by $\beta$ and $\gamma$-rays. As we shall see, the 
+inelastic scattering signature will be a superposition of an ER and a NR, due to the low lifetime of the excited state and 
+the short mean free path ($\sim$0.15\,mm) of the 39.6\,keV photon.
+
+XENON100 has acquired science data between 2008-2015, and has set competitive constraints on spin-
+independent~\cite{Aprile:2012nq,Aprile:2016swn} and spin-dependent~\cite{Aprile:2013doa,Aprile:2016swn} elastic WIMP-nucleus 
+scatters, as well as on axions/ALPs~\cite{Aprile:2014eoa} and leptophilic dark matter 
+models~\cite{Aprile:2015ade,Aprile:2015ibr,Aprile:2017yea}.

### 2017-01-16 Inelastic/inelastic_main.tex
first version to ranny
deleted_auth

--- 2016-11-28 Inelastic/inelastic_main.tex
@@
  reprint,
-%superscriptaddress,
+superscriptaddress,
+linenumbers,
 %groupedaddress,
@@
 
+%\usepackage[sorting=none]{biblatex}
+
 \begin{document}
 
-%\preprint{APS/123-QED}
+\title{Search for WIMP Inelastic Scattering Off Xenon Nuclei With Xenon100 Data}% Force line breaks with \\
 
-\title{Search for WIMP Inelastic Scattering Off Xenon Nuclei With Xenon100 Data}% Force line breaks with \\
-\thanks{}%
+\collaboration{The XENON100 Collaboration}\noaffiliation
 
-\author{Ann Author}
- \altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\
-\author{Second Author}%
- \email{Second.Author@institution.edu}
-\affiliation{%
- Authors' institution and/or address\\
- This line break forced with \textbackslash\textbackslash
-}%
-
-\collaboration{XENON Collaboration}%\noaffiliation
-
-\author{Authors}
-% \homepage{http://www.Second.institution.edu/~Charlie.Author}
-\affiliation{
- Second institution and/or address\\
- This line break forced% with \\
-}%
-\affiliation{
- Affiliation
-}%
-
-%\collaboration{CLEO Collaboration}%\noaffiliation
-
-\date{\today}% It is always \today, today,
-             %  but any date may be explicitly specified
+\date{\today}
 
 \begin{abstract}
-
+	Some nice abstract here.....
 \end{abstract}
 
-%\pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
-                             % Classification Scheme.
 %\keywords{Suggested keywords}%Use showkeys class option if keyword

### 2017-01-16 Inelastic/intro.tex
updated_intro_and_ref

@@
 Particles (WIMPs), which are natural candidates for dark matter. This hypothesis is currently being tested by several direct
-and indirect detection experiments, as well as at the LHC~\cite{Bertone:2004pz,Baudis:2016qwx}.
+and indirect detection experiments, as well as at the LHC~\cite{Bertone:2010zza,Baudis:2016qwx}.
 
@@
 3/2$^{+}$ state at 36.6\,keV above the 1/2$^+$ gound state. The electromnagnetic nuclear decay has a half-life of 0.97\,s. 
-The sigantures of inelastic scattering in xenon have been studied in detail in~\cite{Baudis:2013bba}. It was found that this 
+The signatures of inelastic scattering in xenon have been studied in detail in~\cite{Baudis:2013bba}. It was found that this 
 channel is complementary to spin-dependent, elastic scattering, dominating the integrated rates above $\simeq10$\,keV energy 
@@
 
+Our paper is structures as follows.  In Section~\ref{sec:xenon100} we briefly describe the XENON100 detector and the employed data 
+set in this analysis. In Section~\ref{sec:analysis} we detail the data analysis method, including the simulation of the expected signal and the 
+background model. We conclude in Section~\ref{sec:results} with our results and new constraints on inelastic WIMP-nucleus scatters.
+
 \section{The XENON100 Detector}
+\label{sec:xenon100}
 
@@
 del Gran Sasso (LNGS) in Italy. It contained 161\,kg of xenon in total,  with  62\,kg in the active region of the TPC. These 
-were monitored by 242 low-radioactivity, UV-sensitive photomultiplier tubes (PMTs) arranged in two arrays, one in the liquid 
+were monitored by 242 1-inch square, low-radioactivity, UV-sensitive photomultiplier tubes (PMTs) arranged in two arrays, one in the liquid 
 and one in the gas. The PMTs detected the prompt scintillation (S1) and the delayed, proportional scintillation signal (S2) 
-created by a particle interacting in the active TPC region. The S2-signal is generated due to ionisation electrons, drifted 
-and extracted into the gas phase, where the proportional scintillation, or electroluminiscence, is produced. These photons 
-carry the $x-y$ information of the interaction site, while the $z-$information came from the drift time measurement. The TPC 
+created by a particle interacting in the active TPC region. The S2-signal was generated due to ionisation electrons, drifted 
+in a field of 530\,V/cm and extracted into the gas phase by a field of 12\,kV/cm, where the proportional scintillation, or electroluminiscence, 
+was produced. These photons carried the $x-y$ information of the interaction site, while the $z-$information came from the drift time measurement. The TPC 
 thus yielded a three-dimensional event localisation, enabling to reject the majority of background events via fiducial volume 
@@
 
-XENON100 has acquired science data between 2008-2015, and has set competitive constraints on spin-
-independent~\cite{Aprile:2012nq,Aprile:2016swn} and spin-dependent~\cite{Aprile:2013doa,Aprile:2016swn} elastic WIMP-nucleus 
-scatters, as well as on axions/ALPs~\cite{Aprile:2014eoa} and leptophilic dark matter 
-models~\cite{Aprile:2015ade,Aprile:2015ibr,Aprile:2017yea}.
+XENON100 has acquired science data between 2008-2015, and has set competitive constraints on spin-independent~\cite{Aprile:2012nq,Aprile:2016swn} 
+and spin-dependent~\cite{Aprile:2013doa,Aprile:2016swn} elastic WIMP-nucleus 
+scatters, as well as on axions/ALPs~\cite{Aprile:2014eoa} and leptophilic dark matter models~\cite{Aprile:2015ade,Aprile:2015ibr,Aprile:2017yea}.
+
+Here

### 2017-01-16 Inelastic/results.tex
updated_intro_and_ref

@@
 \section{Results}
+\label{sec:results}
+
 Using an exposure of 34~kg of liquid xenon and 224.6~live days of data a yield of 764 events is observed  in the region of interest,

### 2017-01-18 Inelastic/analysis.tex
updated_intro_and_ref
updated_xenon100_started_analysis_section

@@
 \section{Data Analysis}
+\label{sec:analysis}
 
-This analysis is performed using XENON100 Run-II science data, which corresponds to an exposure of 224.6~live days. The detector response to
-electronic recoil (ER) has been characterized using $^{60}$Co and $^{232}$Th radioactive sources, while response to inelastic nuclear recoil (NR)
-scattering was calibrated using an $^{241}$AmBe source.
+This analysis is performed using XENON100 run\,II science data, which corresponds to a data set with an exposure of 224.6~live days. The detector response to
+ERs has been characterised with $^{60}$Co and $^{232}$Th calibration sources, while the response to NRs was calibrated with an $^{241}$AmBe $(\alpha,n)$-source.
+This fast neutron source gives rise to elastic and inelastic neutron-nucleus scatters, and can thus be employed to define the expected signal region.
 
-The inelastic scattering of a WIMP with the nucleus of $^{129}$Xe produces an energy deposit via nuclear recoil with subsequent emission of  
-a 39.6~keV de-excitation photon. 
-The largest fraction of the energy released in the event is via electronic recoil due to the emitted photon, this represents an
-unusual signature for this kind of detector and brings the possible signal to overlay a phase space region with large backgrounds.
-The chosen region of interest (ROI) for this analysis surrounds the 39.6~keV xenon line in the cS1-cS2 plane and is further divided into
-sub-regions, as shown in Figure~\ref{fig:SR} and~\ref{fig:SR2}.
+\subsection{Signal Correction}
 
-Events are asked, other than falling in the defined region of interest, to fulfill several selection criteria which can be summarized as:
+A particle interaction in the liquid xenon produces an S1 and a correlated S2 signal with a certain number of photoelectrons (PE) observed by the PMTs.
+The non-uniform scintillation light collection by the PMT arrays, due to solid angle effects, Rayleigh scattering length, reflectivity, transmission of the electrodes, etc, lead to a position-dependent S1 signal.
+The warping of the top meshes (inducing a variation in the width of the gas gap between the anode and the liquid-gas interface), the absorption of electrons by residual impurities, as they drift towards the gas region, as well as solid angle effects lead to a position-dependent S2 signal.
+These signals are thus corrected in 3 dimensions, using various calibration data~\cite{Aprile:2011dd}, with the corrected quantities denoted as cS1 and cS2.
+
+\subsection{Signal Region}
+
+As explained in Section~\ref{sec:intro}, the inelastic scattering of a WIMP with a $^{129}$Xe nucleus produces an energy deposit via a NR with subsequent emission of  
+a 39.6\,keV de-excitation photon. The largest fraction of the energy released in the event is via an ER, due to the emitted photon which loses its energy in the LXe.
+This represents an unusual signature compared to the one expected from an elastic scatter, and brings the signal region to overlap with the ER background region.
+The selected region of interest (ROI) for this analysis surrounds the 39.6\,keV xenon line in the cS1-cS2 plane and is further divided into
+sub-regions, as shown in Figures~\ref{fig:SR} and~\ref{fig:SR2}.
+
+Other than falling in the defined region of interest, events are required to fulfil several selection criteria, which can be summarised as follows:
 selection aimed to reduce noise impact and including energy (S1) and S2 thresholds, veto of events with energy release in the detector's outer volume, 
@@
 %description of the simulated signal, few words about cross checks MC matching.
+
 The detector response to inelastic scattering of WIMPs  off $^{129}$Xe nucleus was simulated using an empirical model.

### 2017-01-18 Inelastic/intro.tex
updated_xenon100_started_analysis_section

@@
-\section{\label{sec:level1} Introduction}
+\section{\label{sec:intro} Introduction}
+
 Astrophysical and cosmological evidence indicates that the dominant mass fraction of our Universe consists of some yet unknown
-form of dark, or invisible matter. The dark matter could be made of new, yet undiscovered particles, and well-motivated
+form of dark, or invisible matter. The dark matter could be made of new, stable or long-lived and yet undiscovered particles. Well-motivated
 theoretical models going beyond the Standard Model of particle physics predict the existence of Weakly Interacting Massive
@@
 
-The XENON100 experiment operated a dual-phase (liquid and gas) xenon time projection chamber (TPC) at the Laboratori Nazionali 
-del Gran Sasso (LNGS) in Italy. It contained 161\,kg of xenon in total,  with  62\,kg in the active region of the TPC. These 
-were monitored by 242 1-inch square, low-radioactivity, UV-sensitive photomultiplier tubes (PMTs) arranged in two arrays, one in the liquid 
-and one in the gas. The PMTs detected the prompt scintillation (S1) and the delayed, proportional scintillation signal (S2) 
-created by a particle interacting in the active TPC region. The S2-signal was generated due to ionisation electrons, drifted 
-in a field of 530\,V/cm and extracted into the gas phase by a field of 12\,kV/cm, where the proportional scintillation, or electroluminiscence, 
-was produced. These photons carried the $x-y$ information of the interaction site, while the $z-$information came from the drift time measurement. The TPC 
-thus yielded a three-dimensional event localisation, enabling to reject the majority of background events via fiducial volume 
-cuts, as well a multiple interactions, which are unlikely due to dark matter particles~\cite{Aprile:2011dd}. The ratio of 
-S2/S1 provided the basis for distinguishing between nuclear recoils (NRs), as induced by fast neutrons and expected from 
-elastic WIMP-nucleus scatters, and electronic recoils (ERs) produced by $\beta$ and $\gamma$-rays. As we shall see, the 
-inelastic scattering signature will be a superposition of an ER and a NR, due to the low lifetime of the excited state and 
-the short mean free path ($\sim$0.15\,mm) of the 39.6\,keV photon.
+The XENON100 experiment operates a dual-phase (liquid and gas) xenon time projection chamber (TPC) at the Laboratori Nazionali 
+del Gran Sasso (LNGS) in Italy. It contains 161\,kg of xenon in total,  with  62\,kg in the active region of the TPC. These 
+are monitored by 242 1-inch square, low-radioactivity, UV-sensitive photomultiplier tubes (PMTs) arranged in two arrays, one in the liquid 
+and one in the gas. The PMTs detect the prompt scintillation (S1) and the delayed, proportional scintillation signal (S2) 
+created by a particle interacting in the active TPC region. The S2-signal is generated due to ionisation electrons, drifted 
+in an electric field of 530\,V/cm and extracted into the gas phase by a stronger field of $\sim$ 12\,kV/cm, where the proportional scintillation, or electroluminiscence, 
+is produced. These photons carry the $(x,y)$ information of the interaction site, while the $z-$information comes from the drift time measurement. The TPC 
+thus yields a three-dimensional event localisation, with an $(x,y)$ resolution of $<$3\,mm (1\,$\sigma$), and a $z$ resolution of  $<$0.3\,mm (1\,$\sigma$), enabling to reject the majority of background events via fiducial volume cuts~\cite{Aprile:2011dd}.
+The ratio S2/S1 provides the basis for distinguishing between nuclear recoils (NRs), as induced by fast neutrons and expected from elastic WIMP-nucleus scatters, and electronic recoils (ERs) produced by $\beta$ and $\gamma$-rays.
 
@@
 and spin-dependent~\cite{Aprile:2013doa,Aprile:2016swn} elastic WIMP-nucleus 
-scatters, as well as on axions/ALPs~\cite{Aprile:2014eoa} and leptophilic dark matter models~\cite{Aprile:2015ade,Aprile:2015ibr,Aprile:2017yea}.
+scatters, on solar axions and galactic ALPs~\cite{Aprile:2014eoa}, as well as on leptophilic dark matter models~\cite{Aprile:2015ade,Aprile:2015ibr,Aprile:2017yea}.
 
-Here
+Here we explore a potential new signature in the XENON100 detector, caused by spin-dependent, inelastic WIMP-$^{129}$Xe scatters. The expected  
+inelastic scattering signature is a combination of an ER and a NR, due to the short lifetime of the excited nuclear state and  the short mean free path of $\sim$0.15\,mm of the 39.6\,keV de-excitation photon.

### 2017-01-19 Inelastic/analysis.tex
continued_with_section3_A_B_C_some_comments_in_red

@@
 
-This analysis is performed using XENON100 run\,II science data, which corresponds to a data set with an exposure of 224.6~live days. The detector response to
+This analysis is performed using XENON100 Run-II science data, which corresponds to a data set with an exposure of 224.6~live days. The detector response to
 ERs has been characterised with $^{60}$Co and $^{232}$Th calibration sources, while the response to NRs was calibrated with an $^{241}$AmBe $(\alpha,n)$-source.
-This fast neutron source gives rise to elastic and inelastic neutron-nucleus scatters, and can thus be employed to define the expected signal region.
+This fast neutron source gives rise to elastic and inelastic neutron-nucleus scatters, and can thus be employed to define the expected signal region for inelastic WIMP-nucleus scatters.
 
@@
 The non-uniform scintillation light collection by the PMT arrays, due to solid angle effects, Rayleigh scattering length, reflectivity, transmission of the electrodes, etc, lead to a position-dependent S1 signal.
-The warping of the top meshes (inducing a variation in the width of the gas gap between the anode and the liquid-gas interface), the absorption of electrons by residual impurities, as they drift towards the gas region, as well as solid angle effects lead to a position-dependent S2 signal.
-These signals are thus corrected in 3 dimensions, using various calibration data~\cite{Aprile:2011dd}, with the corrected quantities denoted as cS1 and cS2.
+The warping of the top meshes (inducing a variation in the width of the gas gap between the anode and the liquid-gas interface), the absorption of electrons by residual impurities as they drift towards the gas region, as well as solid angle effects lead to a position-dependent S2 signal.
+These signals are thus corrected in 3 dimensions, using various calibration data, as detailed in~\cite{Aprile:2011dd,Aprile:2012vw}, with the corrected quantities denoted as cS1 and cS2, and defined in~\cite{Aprile:2012vw}.
+The trigger efficiency in thus run was 100\% for S2$>$300\,PE.
 
-\subsection{Signal Region}
+\subsection{Signal Region and Event Selection}
 
@@
 
-Other than falling in the defined region of interest, events are required to fulfil several selection criteria, which can be summarised as follows:
-selection aimed to reduce noise impact and including energy (S1) and S2 thresholds, veto of events with energy release in the detector's outer volume, 
-and additionally, events must be of single scatter nature and fall into a predefined fiducial volume. This analysis follows the 
-selection criteria described in detail in \cite{dataAnalysis} for Run-II, with only few exceptions reported in what follows. 
-%only few modification have been designed specifically for this analysis and discussed below. 
-The selection on S2 width as a function of drift time has been optimized on a sample of events selected from the 39.6~keV line
-and set to a 95\% acceptance on these. Events are required to be single scatter by applying a threshold on the 
-second largest S2 peak size,  for this analysis this threshold has been optimized to 160~PE and set constant as function of S2 signal size. 
-Finally the chosen fiducial volume corresponds to 34~Kg of liquid xenon.
+Apart from the condition to occur in the defined region of interest in the cS2-cS1-plane, valid events are required to fulfil several selection criteria, 
+which can be summarised as follows: data quality cuts, energy selection and S2 threshold cut, veto cut for events with energy release in the detectors active LXe shield, 
+selection of single scatter events and of a predefined fiducial volume.
+
+This analysis follows the selection criteria described in detail in \cite{Aprile:2012vw} for Run-II, with only a few exceptions reported in what follows. 
+The cut on the S2 signal width as a function of drift time (where the maximal drift time is 176\,$\mu$s and the width values range from $\sim$1-2\,$\mu$s) has been optimised on a sample of events selected from the 39.6\,keV line and set to a 95\% acceptance on these.
+Events are required to be single-scatters by applying a threshold cut on the size of the
+second largest S2 peak. For this analysis, the threshold has been optimised to 160\,PE and set constant as function of S2 signal size. 
+Finally, the chosen fiducial volume corresponds to 34\,kg of liquid xenon.
 
@@
   \includegraphics[width=\linewidth]{images/bkg_in_sr.png}
-  \caption{Signal region and control region.}
+  \caption{Signal (1-9) and control (CR1 and CR2) regions for the inelastic WIMP-$^{129}$Xe interaction in the cS2 versus cS1 plane.
+{\textcolor{red} {I think we must explains the shape of these regions.}}}
   \label{fig:SR}
@@
 \subsection{Signal Simulation}
-%description of the simulated signal, few words about cross checks MC matching.
 
-The detector response to inelastic scattering of WIMPs  off $^{129}$Xe nucleus was simulated using an empirical model.
-The total deposited energy is divided into two independent contributions: one related to the 39.6~keV de-excitation photon and the other  relative to
-the simultaneous nuclear recoil of the xenon atom. The number of photons and charge yield detected is simulated separately for each contribution
-and then added together.
+The detector response to inelastic WIMP-$^{129}$Xe interactions was simulated using an empirical signal model.
+The total deposited energy is divided into two independent contributions: one coming from the 39.6\,keV de-excitation photon and the other  from  
+the simultaneous nuclear recoil of the xenon atom. The detected light (S1) and charge (S2) signals are simulated separately for each of the two contributions 
+and then added together. This is due to the fact that the light and charge yields depend on the type of interaction (ER vs. NR), and on the deposited energy.
 
-The distribution in the cS1-cS2 plane of an ER induced by the de-excitation photon is simulated assuming a two dimensional normal pdf, $f(cS1,cS2)$, 
-described except a normalization factor in equation~\ref{f:2dgaus}:
+The distribution of an ER induced by the de-excitation photon in the cS1-cS2 plane  is simulated assuming a two dimensional normal probability distribution function (pdf), $f(cS1,cS2)$, 
+described (apart from a constant normalisation factor) by the following equation:
+
 \begin{multline}
-	f(cS1,cS2)  = exp \Big( -\frac{1}{2(1-\rho^2)} \Big[ \frac{(cS1 - \mu_{cS1})^2}{\sigma_{cs1}^2} + \\ 
-	 \frac{(cS2 - \mu_{cS2})^2}{\sigma_{cs2}^2} - \frac{2\rho(cS1 - \mu_{cs1}) (cS2 - \mu_{cs2})} {\sigma_{cs1}\sigma_{cs2}} \Big] \Big) 
+	f(cS1,cS2)  = {\rm exp} \Big\{ -\frac{1}{2(1-\rho^2)} \Big[ \frac{(cS1 - \mu_{cS1})^2}{\sigma_{cs1}^2} + \\ 
+	 \frac{(cS2 - \mu_{cS2})^2}{\sigma_{cs2}^2} - \frac{2\rho\cdot(cS1 - \mu_{cs1}) (cS2 - \mu_{cs2})} {\sigma_{cs1}\sigma_{cs2}} \Big] \Big\}
 	%f(cS1,cS2) ~ = ~  \frac{1}{2 \pi \sigma_{cs1} \sigma_cs2 \sqrt{1-\rho^{2}} } exp \Big( -\frac{1}{2(1-\rho^2)} \Big[ \frac{(cS1 - \hat{cS1})^2}{\sigma_{cs1}^2} \Big] \Big)
@@
 where $\mu_{cS1}$ and $\mu_{cS2}$ 
-represents the average observed cS1 and cS2 given a 39.6~keVee , $\sigma_{cs1}$ and $\sigma_{cs2}$ are the standard deviation in cS1 and cS2 respectively,
-while $\rho$ stands for the correlation between cS1 and cS2.
-The detector related light yield $L_y$  at 39.6~keV, necessary to evaluate the average number of photon detected ($\mu_{cS1}$),
-%with AmBe calibration has been found to have a large systematic uncertainty
-%due to the contribution of the nuclear recoil, so the light yield used to describe the number of photon detected 
-is obtained as the result of a NEST model~\cite{NEST,Geant1,Geant2} fit to data collected with several lines.  The same model is used to predict the charge yield at
-39.6~keV which is then scaled according to the detector's secondary scintillation gain $Y$, determined from detector response to single electrons~\cite{SingleE}.
-The detector resolution at 39.6~keV in cS1 and cS2 has been measured to be respectively 15.8\% and 14.7\% and used to extract the standard 
-deviations $\sigma_{cs1}$, $\sigma_{cs2}$.  The correlation parameter is assumed to be independent of energy (at least in the considered range) and measured
-using the 164~keV xenon activated line by $^{124}$AmBe calibration data, this line is chosen since allows to disentangle efficiently contribution from nuclear recoil.
-The measured correlation is $\rho \, = \, -0.45 \pm 0.10$.
+represent the average observed cS1 and cS2 signals given a 39.6\,keV ER, $\sigma_{cs1}$ and $\sigma_{cs2}$ are the standard deviation in cS1 and cS2 respectively,
+while $\rho$ stands for the correlation between the cS1 and cS2 signals. The detector-related light yield $L_y$  at 39.6\,keV, necessary to evaluate the average number of prompt photons detected 
+($\mu_{cS1}$), is obtained from the NEST model~\cite{NEST,Geant1,Geant2} fit to data collected with several $\gamma$-lines.  The average light yield at 39.6\,keV is 2.7\,PE/keV.
 
-The cS1 and cS2 distributions from NR contribution are predicted starting from the nuclear recoil energy spectrum
-of WIMPs inelastic interaction~\cite{inelastic_th}. The average cS1 and cS2 are given by equations~\ref{f:cs1} and~\ref{f:cs2} respectively,
-where $\mathcal{L}_{eff}$ is the liquid xenon NR relative scintillation efficiency, while $S_{ee} \, = \, 0.58$  and $S_{nr} \, = \, 0.95$ describe the scintillation 
-quenching due to the electric field \cite{ScintQuenching}. The parameterization and uncertainties of $\mathcal{L}_{eff}$ as a function of $E_{nr}$ are based on existing 
-direct measurements \cite{run8Result}. The light yield at 122~keVee originate from the same NEST model fit as described above. For the cS2 the parameterization 
-of $Q_{Y}(E_{nr})$ is taken from \cite{QY}.
-Finally all detector related resolution effects are introduced following the prescriptions described in \cite{dataAnalysis}.
+The same model is used to predict the charge yield at 39.6\,keV, which is afterwards scaled according to the detector's secondary scintillation gain $Y$. 
+ The latter is determined from detector's response to single electrons~\cite{SingleE}.
+The energy resolution at 39.6\,keV in cS1 and cS2 has been measured to be 15.8\% and 14.7\%, respectively, and is used to extract the standard 
+deviations $\sigma_{cs1}$, $\sigma_{cs2}$.  The correlation parameter is assumed to be independent of energy (at least in the considered narrow energy range) and measured
+using the 164\,keV line from the decay of the $^{131m}$Xe isomer ($T_{1/2}$=11.8\,d) produced during the  $^{124}$AmBe run.
+This $\gamma$-line is chosen because it allows to disentangle efficiently the contribution from the nuclear recoil.
+The measured correlation coefficient is $\rho \, = \, -0.45 \pm 0.10$.
+
+The cS1 and cS2 distributions from the NR contribution are predicted starting from the expected nuclear recoil energy spectrum
+of WIMP inelastic interactions~\cite{Baudis:2013bba}. The average cS1 and cS2 are given by equations~\ref{f:cs1} and~\ref{f:cs2} respectively,
+where $\mathcal{L}_{eff}$ is the liquid xenon relative scintillation efficiency for NRs, while $S_{ee} \, = \, 0.58$  and $S_{nr} \, = \, 0.95$ describe the scintillation 
+quenching  of ER and NRs, respectively, due to the electric field \cite{ScintQuenching}.
+The parameterisation and uncertainties of $\mathcal{L}_{eff}$ as a function of nuclear recoil energy $E_{nr}$ are based on existing
+direct measurements \cite{run8Result}. The light yield for 122\,keV ERs is taken from the same NEST model fit as described above. For cS2, the parameterisation 
+of $Q_{Y}(E_{nr})$ is taken from \cite{QY}. Finally, all detector related resolution effects are introduced following the prescriptions described in \cite{Aprile:2012vw}.
 
@@
 
-The pdf of the ER and NR contributions are then convoluted together to obtain the overall pdf of the signal.
-%The two contribution are summed together in an event-by-event basis using random extraction from the two pdfs. 
+The pdf of the ER and NR contributions are then convoluted together to obtain the overall pdf of the expected signal.
 A 2D (cS1 versus cS2) acceptance map is applied to the signal pdf to reproduce data selection effects. Acceptances are computed separately for each selection 
-criteria using $^{124}$AmBe calibration sample, selections as the outer volume veto and the single scatter interaction represent an exception  and 
-a dedicated computation has been performed in these cases. The selections acceptance average in the region of interest to about $0.80 \pm 0.05$. 
-Figure~\ref{fig:SR} shows an example of full simulated signal model for a WIMP of 100~GeV mass.
+criteria using the $^{124}$AmBe calibration sample. Other selections such as the liquid xenon veto cut, and the single-scatter interaction represent an exception  and 
+a dedicated computation has been performed in these cases. The combined acceptance  of all selection criteria in the region of interest averages to $\sim$$(0.80\pm0.05)$. 
+Figure~\ref{fig:SR} shows an example of fully simulated signal model for a WIMP mass of 100\,GeV/c$^2$.
 
-The signal simulation procedure has been validated reproducing the 39.6~keV xenon line from interaction due to
-$^{124}$AmBe source and has been compared to data. For this comparison the proper  $^{124}$AmBe nuclear recoil and acceptances
-were simulated. The simulated events were found in agreement  with calibration data within statistical uncertainties.
+The signal simulation procedure has been validated by reproducing the 39.6\,keV xenon line from interactions due to neutrons from the 
+$^{124}$AmBe source and comparison to data. For this comparison, the proper  $^{124}$AmBe nuclear recoil and acceptances
+were simulated. The simulated events were in agreement  with calibration data within statistical uncertainties. 
+{\textcolor{red} {Should we show an example, namely a figure from the signal model note?}}
 
@@
   \includegraphics[width=\linewidth]{images/wimp_in_sr.png}
-  \caption{Signal region and control region, for WIMP of mass 100~GeV.}
+  \caption{Simulated signal (1-9) and control (CR1 and CR2) regions for a WIMP mass 100\,GeV/c$^2$.}
   \label{fig:SR2}

### 2017-01-19 Inelastic/analysis.tex
continued_with_subsectionE_somecomments

@@
 These signals are thus corrected in 3 dimensions, using various calibration data, as detailed in~\cite{Aprile:2011dd,Aprile:2012vw}, with the corrected quantities denoted as cS1 and cS2, and defined in~\cite{Aprile:2012vw}.
-The trigger efficiency in thus run was 100\% for S2$>$300\,PE.
+The trigger efficiency in this run was 100\% for S2$>$300\,PE.
 
@@
 The selected region of interest (ROI) for this analysis surrounds the 39.6\,keV xenon line in the cS1-cS2 plane and is further divided into
-sub-regions, as shown in Figures~\ref{fig:SR} and~\ref{fig:SR2}.
+sub-regions, as shown in Figures~\ref{fig:SR} and~\ref{fig:SR2}. {\textcolor{red} {Here more info on these regions, and the cS1 and cS2 boundaries?}
 
 Apart from the condition to occur in the defined region of interest in the cS2-cS1-plane, valid events are required to fulfil several selection criteria, 
-which can be summarised as follows: data quality cuts, energy selection and S2 threshold cut, veto cut for events with energy release in the detectors active LXe shield, 
-selection of single scatter events and of a predefined fiducial volume.
+which can be summarised as follows: basic data quality cuts, energy selection and S2 threshold cut, veto cut for events with energy release in the detector's active LXe shield, 
+selection of single-scatter events and of a predefined fiducial volume.
 
-This analysis follows the selection criteria described in detail in \cite{Aprile:2012vw} for Run-II, with only a few exceptions reported in what follows. 
-The cut on the S2 signal width as a function of drift time (where the maximal drift time is 176\,$\mu$s and the width values range from $\sim$1-2\,$\mu$s) has been optimised on a sample of events selected from the 39.6\,keV line and set to a 95\% acceptance on these.
+This analysis closely follows the event selection criteria described in detail in \cite{Aprile:2012vw} for Run-II, with only a few exceptions reported in what follows. 
+The cut on the width of the S2 signal as a function of drift time (where the maximal drift time is 176\,$\mu$s and the width values range from $\sim$1-2\,$\mu$s) has been optimised on a sample of events selected from the 39.6\,keV line and set to a 95\% acceptance on these.
+This cut ensures that the S2-signal width is consistent with the $z$-position calculated from the observed time difference between the S1 and S1 signals.
 Events are required to be single-scatters by applying a threshold cut on the size of the
@@
 
-The main expected background contribution in the region of interest is due to eviromental and material radioactivity, its composition is mainly
-represented by Compton scattering photons. Background contribution due to the activation of the xenon 39.6~keV line from radiogenic neutrons is expected to be negligible.
+The background in the region of interest for inelastic scattering is dominated by ERs due the residual radioactivity of detector materials, due to $^{85}$Kr present in the liquid xenon ($\sim$55\%) as well as due to $^{222}$Rn decays in the liquid ($<$7\%)~\cite{Aprile:2011vb}.
+The background contribution from inelastic scatters of radiogenic or cosmogenic neutrons (producing a 39.6\,keV de-excitation line) is negligible thanks to the very low expected neutron scattering rate in the detector~\cite{Aprile:2013tov}.
 
-The background is modeled using data from the $^{60}$Co calibration campaign, which are assumed to well represent the background density distribution 
-in the cS1-cS2 plane. 
-The calibration sample yields  about 22'000 events in the ROI, these are then scaled to data according to a measured scale factor $\tau_{bkg}$.
+The expected background is modelled using data from the $^{60}$Co calibration campaign, which are assumed to well represent the background density distribution 
+in the cS1-cS2 plane. The calibration sample yields  about $2.2\times10^4$ events in the ROI; these are then scaled to the science data according to a measured scale 
+factor $\tau_{bkg}$.
 This scale factor, which is merely the ratio between the data and calibration sample yields, is measured in the two control regions shown in Figure~\ref{fig:SR} and labelled CR1 and CR2.
@@
 The distribution of the calibration sample has been compared to the data of the science run in the two control regions,
-agreement is found within statistical uncertainties. Furthermore, $^{60}$Co calibration data have been compared in the region of interest to  
-data from $^{232}$Th calibration campaign, the largest deviation between the two shapes is within 4\%. An additional systematic
-uncertainty of 4\% has been applied to the expected background yield of each sub-region of the ROI.
+and agreement was found within statistical uncertainties. Furthermore, $^{60}$Co calibration data have been compared in the region of interest to  
+data from the $^{232}$Th calibration campaign, and the largest deviation between the two shapes is within 4\%. An additional systematic
+uncertainty of 4\% has thus been applied to the expected background yield of each sub-region of the ROI.
+{\textcolor{red} {Should we show a figure, namely the agreement of data and BG model for the control regions? Like the second figure in the background model check note.}}
 
@@
   \includegraphics[width=\linewidth]{images/wimp_sys_unc.png}
-  \caption{Signal region, uncertainties for WIMP of mass 100~GeV.}
+  \caption{Predicted signal (blue curve), along with statistical and systematic uncertainties (cyan region) simulated for a WIMP mass of 100\,GeV/c$^2$.
+The signal and its uncertainties are shown as a function of the signal region number {\textcolor{red} {Maybe there is a better way to say this, or leave out?}}.
+The signal has been scaled for a total number of 50 events.
+}
   \label{fig:unc}
@@
 
-Uncertainties on the total prediction of background events arise from the uncertainty on the measure of the normalization 
-factor, $\tau_{bkg}$, and amount to 6\%, contribution of radiogenic neutrons are neglected. 
-Systematic uncertainty on the shape of the predicted background distribution are assessed by the maximal discrepancy in the ROI between
-the $^{60}$Co and $^{232}$Th calibration samples, a 4\% systematic additional to statistical uncertainty is assigned to the expected yield of each sub-region.
-Note that uncertainties belonging to different sub-regions are considered independent from each other.
+Uncertainties on the  prediction of the total number of background events arise from the uncertainty on the measurement of the normalisation 
+factor, $\tau_{bkg}$, and amount to 6\%. % contribution of radiogenic neutrons are neglected. 
+Systematic uncertainty on the shape of the predicted background distribution are assessed by the maximal observed discrepancy in the ROI between
+the $^{60}$Co and $^{232}$Th calibration samples.  As explained, a 4\% systematic uncertainty is added  to the expected yield of each sub-region.
+Uncertainties belonging to different sub-regions in the ROI are considered independent from one another.
 %It is important not only to describe correctly the expected total background but also its distribution
 
-Uncertainty on the total yield of signal arising from selections acceptance uncertainties are found to be very weakly dependent on 
-the WIMP mass, an overall 6\% acceptance uncertainty is then applied to all WIMPs hypothesis.
+Uncertainties on the total yield of signal events arising from selections acceptance uncertainties are found to be very weakly dependent on 
+the WIMP mass, and an overall 6\% acceptance uncertainty is applied to all WIMP hypotheses.
 
-Uncertainties on the energy scale and, more generally, related to detector response 
-are parameterized using the respective uncertainties on the measure of $L_y$, $\mathcal{L}_{eff}$, $Y$, $Q_Y$ and $\rho$. The simulation shows 
-that these type of uncertainties mainly affect the pdf of the signal model in the ROI, and very weakly the total signal yield. 
+Uncertainties on the energy scale and, more generally, related to detector responses  are parameterised 
+using the respective uncertainties on the measures of $L_y$, $\mathcal{L}_{eff}$, $Y$, $Q_Y$ and $\rho$. The simulation shows 
+that these uncertainties mainly affect the pdf of the signal model in the ROI, and very weakly the total signal yield. 
 %For each WIMP mass we simulate several signal pseudo-sample, which are produced varying the model parameters  respectively of $\pm 1$ standard deviation. 
-They are taken into account by simulating several signal pseudo-sample for each WIMP mass, the pseudo-samples are produced varying the model parameters respectively of $\pm 1$ standard deviation. 
-For each sub-region is then computed an overall uncertainty by adding in quadrature the variations of each pseudo-sample 
+They are taken into account by simulating several signal pseudo-samples for each WIMP mass, where the pseudo-samples are produced 
+by varying the model parameters within their $\pm 1$ standard deviations. 
+For each sub-region an overall uncertainty is then computed, by adding in quadrature the variations of each pseudo-sample 
 %FIXME: explain this better, the up variation are separated from down variations and added together
-with respect to nominal. Figure~\ref{fig:unc} is an example of such a systematic uncertainty computation for a WIMP of 100~GeV mass.
+with respect to nominal. Figure~\ref{fig:unc} shows an example of such a systematic uncertainty computation for a WIMP mass of 100\,GeV/c$^2$.
 
 %FIXME: express this in an understandable way
-All the uncertainties discussed here are parameterized within a binned profiled likelihood function using the framework~\cite{roostat,roofit}.
-All parameters related to systematic uncertainties are assumed to be normally distributed.
+All the uncertainties discussed here are parameterised with a binned profile likelihood function using the framework from~\cite{roostat,roofit}.
+All the parameters related to systematic uncertainties are assumed to be normally distributed.

### 2017-01-19 Inelastic/results.tex
continued_with_subsectionE_somecomments

@@
 
-Using an exposure of 34~kg of liquid xenon and 224.6~live days of data a yield of 764 events is observed  in the region of interest,
-this is compatible with the expectation of $756 \, \pm \, 5^{(stat.)} \, \pm 55^{(syst.)}$ events from the background only hypothesis. 
+Using a fiducial volume with 34\,kg of liquid xenon and 224.6~live days of data yields 764 events observed  in the region of interest.
+This number is compatible with the expectation of $756 \, \pm \, 5^{(stat.)} \, \pm 55^{(syst.)}$ events from the background only hypothesis. 
 Figure~\ref{fig:dataVSbkg} shows how these events are distributed in the region of interest, the bottom panel shows the ratio
@@
 on the background expectation.
+
 %The distribution of events from data are compared to the background expectation in Figure~\ref{fig:dataVSbkg} and with the relative

### 2017-01-19 Inelastic/analysis.tex
more_edits_captions_results_citations

@@
 The selected region of interest (ROI) for this analysis surrounds the 39.6\,keV xenon line in the cS1-cS2 plane and is further divided into
-sub-regions, as shown in Figures~\ref{fig:SR} and~\ref{fig:SR2}. {\textcolor{red} {Here more info on these regions, and the cS1 and cS2 boundaries?}
+sub-regions, as shown in Figures~\ref{fig:SR} and~\ref{fig:SR2}.
+These sub-regions were defined such as to contain roughly a similar number of expected background events in each region.
+The control regions CR1 and CR2 are chosen to be as close as possible to the signal regions,  and are used as cross check of the background shape distribution.
 
@@
   \includegraphics[width=\linewidth]{images/bkg_in_sr.png}
-  \caption{Signal (1-9) and control (CR1 and CR2) regions for the inelastic WIMP-$^{129}$Xe interaction in the cS2 versus cS1 plane.
-{\textcolor{red} {I think we must explains the shape of these regions.}}}
+  \caption{Signal (1-9) and control (CR1 and CR2) regions for the inelastic WIMP-$^{129}$Xe interaction in the cS2 versus cS1 plane. Their definition is given in the text.}
   \label{fig:SR}
@@
 
-The distribution of an ER induced by the de-excitation photon in the cS1-cS2 plane  is simulated assuming a two dimensional normal probability distribution function (pdf), $f(cS1,cS2)$, 
+The distribution of an ER induced by the de-excitation photon in the cS1-cS2 plane  is simulated assuming a two dimensional normal probability distribution function (pdf), $f(cS1_{er},cS2_{er})$, 
 described (apart from a constant normalisation factor) by the following equation:
@@
 \begin{multline}
-	f(cS1,cS2)  = {\rm exp} \Big\{ -\frac{1}{2(1-\rho^2)} \Big[ \frac{(cS1 - \mu_{cS1})^2}{\sigma_{cs1}^2} + \\ 
-	 \frac{(cS2 - \mu_{cS2})^2}{\sigma_{cs2}^2} - \frac{2\rho\cdot(cS1 - \mu_{cs1}) (cS2 - \mu_{cs2})} {\sigma_{cs1}\sigma_{cs2}} \Big] \Big\}
+	f(cS1_{er},cS2_{er})  = {\rm exp} \Big\{ -\frac{1}{2(1-\rho^2)} \Big[ \frac{(cS1_{er} - \mu_{cS1_{er}})^2}{\sigma_{cs1}^2} + \\ 
+	 \frac{(cS2_{er} - \mu_{cS2_{er}})^2}{\sigma_{cs2}^2} - \frac{2\rho\cdot(cS1_{er} - \mu_{cs1}) (cS2_{er} - \mu_{cs2})} {\sigma_{cs1}\sigma_{cs2}} \Big] \Big\}
 	%f(cS1,cS2) ~ = ~  \frac{1}{2 \pi \sigma_{cs1} \sigma_cs2 \sqrt{1-\rho^{2}} } exp \Big( -\frac{1}{2(1-\rho^2)} \Big[ \frac{(cS1 - \hat{cS1})^2}{\sigma_{cs1}^2} \Big] \Big)
@@
 where $\mu_{cS1}$ and $\mu_{cS2}$ 
-represent the average observed cS1 and cS2 signals given a 39.6\,keV ER, $\sigma_{cs1}$ and $\sigma_{cs2}$ are the standard deviation in cS1 and cS2 respectively,
+represent the average observed $cS1_{er}$ and $cS2_{er}$ signals given a 39.6\,keV ER, $\sigma_{cs1}$ and $\sigma_{cs2}$ are the standard deviation in $cS1_{er}$ and $cS2_{er}$ respectively,
 while $\rho$ stands for the correlation between the cS1 and cS2 signals. The detector-related light yield $L_y$  at 39.6\,keV, necessary to evaluate the average number of prompt photons detected 

### 2017-01-19 Inelastic/results.tex
more_edits_captions_results_citations

--- 2017-01-16 Inelastic/results.tex
@@
-\section{Results}
+\section{Results and Discussion}
 \label{sec:results}
 
-Using an exposure of 34~kg of liquid xenon and 224.6~live days of data a yield of 764 events is observed  in the region of interest,
-this is compatible with the expectation of $756 \, \pm \, 5^{(stat.)} \, \pm 55^{(syst.)}$ events from the background only hypothesis. 
-Figure~\ref{fig:dataVSbkg} shows how these events are distributed in the region of interest, the bottom panel shows the ratio
-between data and expected background, where the gray and orange shaded areas represent respectively statistical and systematic uncertainty 
-on the background expectation.
-%The distribution of events from data are compared to the background expectation in Figure~\ref{fig:dataVSbkg} and with the relative
-%uncertainties.
+Using a fiducial volume containing 34\,kg of liquid xenon and 224.6~live days of data yields 764 events observed  in the region of interest.
+This number is compatible with the expectation of $756 \, \pm \, 5 \,{\rm (stat)} \, \pm 55\, {\rm (syst)}$ events from the background only hypothesis. 
+Figure~\ref{fig:dataVSbkg} shows the distribution of  events  in the region of interest, where the bottom panel displays the ratio
+between data and expected background. The grey and orange shaded areas represent the statistical and systematic uncertainty 
+on the background expectation, respectively. The expected signal for a WIMP mass of 100\,GeV/c$^2$, and normalised to a total of 50 events, is also shown.
 
-This result is interpreted via a binned profiled likelihood approach by means of the test statistic $\tilde{q}$
-and its asymptotic distributions described in \cite{asympt}. 
-Assuming  an isothermal WIMP halo with a local density of $\rho_{\chi} \, = \, 0.3$~$GeV/cm^3$ , a local circular velocity of $v_0 \,= \, 220$~km/s, and a galactic escape velocity of $v_{esc} \, = \, 544$ km/s,
-\textcolor{blue}{other assumptions...,} a 90\% CL$_s$~\cite{cls} confidence level limit is  
-computed on the spin dependent inelastic WIMP-nucleon cross section, $\sigma_{inel}$, as a function of the WIMP mass, $m_{\chi}$, and shown in Figure~\ref{fig:limits}.
-The expected median sensitivity is reported with its relative one (green area) and two (yellow area) standard deviation uncertainty.
-A  limit is set on $\sigma_{inel}$ to $3.3 \times 10^{-38} ~cm^{2}$ at 90\% CL$_s$ confidence level for a WIMP of mass 100~GeV. This limit is compared with
-\textcolor{blue}{decide which other experiment to plot.}
+%\newpage
 
-\newpage
 \begin{figure}[t!]
   \includegraphics[width=\linewidth]{images/data_vs_bkg.png}
-  \caption{Results, comparison between data and expected background.}
+  \caption{Distribution of  observed events  in the region of interest (data points), along with the normalised distribution from calibration data (filled histogram).
+The bottom panel displays the ratio
+between data and expected background, where the grey and orange shaded areas represent the statistical and systematic uncertainty 
+on the background expectation, respectively. The expected signal for a WIMP mass of 100\,GeV/c$^2$ (blue dashed), and normalised to a total of 50 events, is also shown.}
   \label{fig:dataVSbkg}
@@
 
+This result is interpreted via a binned profiled likelihood approach by means of the test statistic $\tilde{q}$
+and its asymptotic distributions, as  described in \cite{asympt}. 
+Assuming  an isothermal WIMP halo with a local density of $\rho_{\chi} \, = \, 0.3$\,GeV/cm$^3$, a local circular velocity of $v_0 \,= \, 220$\,km/s, and a galactic escape velocity of $v_{\rm{esc}} \, = \, 544$\,km/s,
+\textcolor{blue}{other assumptions...,} a 90\% CL$_s$~\cite{cls} confidence level upper limit on the spin-dependent inelastic WIMP-nucleon cross section as a function of WIMP mass is computed.
+We employ the nuclear structure factors as calculated in \cite{Baudis:2013qla}, based on state-of-the-art large-scale shell-model calculations, with chiral effective field theory WIMP-nucleon currents.
+
 \begin{figure}[h]
   \includegraphics[width=\linewidth]{images/limit_reb.png}
-  \caption{Observed and expected limits.}
+  \caption{Upper limit (black curve) on the spin-dependent, inelastic WIMP-nucleon cross section as a function of WIMP mass.
+The expected median sensitivity (dashed curve) along with the relative one (green area) and two (yellow area) standard deviation uncertainty is also shown.
+This result is compared to the upper limit (at 90\% C.L.) obtained by the XMASS experiment (red curve)~\cite{Uchida:2014cnn}.}
   \label{fig:limits}
@@
 
-\newpage
+Our result is shown in Figure~\ref{fig:limits}, together with the expected median sensitivity and its relative one and two  standard deviation uncertainty.
+The most constraining upper limit is  $3.3 \times 10^{-38}$\,cm$^{2}$ (at 90\% CL$_s$ confidence level) is for a WIMP of mass 100\,GeV/c$^2$.
+
+This results is compared to the one obtained by the XMASS experiment~\cite{Uchida:2014cnn}, a single phase liquid xenon detector, which used a fiducial volume containing 41\,kg of LXe and 165.9~live days of data.
+\textcolor{blue}{Decide which other experiment to also plot - DAMA LXe?
+However only XMASS uses the same form factors as we do.}
+
+Our limit improves upon the XMASS result and constrains new parameter space for the spin-dependent, inelastic scattering cross section.
+While these upper limits are not competitive to spin-dependent, elastic scattering results, as obtained by XENON100~\cite{Aprile:2013doa} and LUX~\cite{Akerib:2016lao} (with a cross section minimum of $\sim2 \times 10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/cm$^2$ WIMP), our results set the pathway for a sensitive search of inelastic WIMP-nucleus scattering in running or upcoming liquid xenon experiments such as XENON1T~\cite{Aprile:2015uzo}, XENONnT~\cite{Aprile:2015uzo},  LZ~\cite{Akerib:2015cja}, and DARWIN~\cite{Aalbers:2016jon}.
+In these larger detectors, with lower intrinsic backgrounds from $^{85}$Kr and $^{222}$Rn decays, and improved self-shielding, the electronic recoil background will be reduced by a few orders of magnitude with respect to XENON100, and ultimately dominated by solar neutrino interactions~\cite{Baudis:2013qla}.
+
+The discovery of this interaction channel would be a clear signature for a spin-dependent nature of the interaction, and would provide a potential handle  to constrain the WIMP mass~\cite{Baudis:2013bba}.
+
+%\newpage

### 2017-01-20 Inelastic/analysis.tex
fixed_typos_and_some_text_added_more_comments_in_red

@@
 
-This analysis is performed using XENON100 Run-II science data, which corresponds to a data set with an exposure of 224.6~live days. The detector response to
-ERs has been characterised with $^{60}$Co and $^{232}$Th calibration sources, while the response to NRs was calibrated with an $^{241}$AmBe $(\alpha,n)$-source.
+This analysis is performed using XENON100 Run-II science data, with 224.6~live days of data taking.
+The detector's response to ERs has been characterised with $^{60}$Co and $^{232}$Th calibration sources, while the response to NRs was calibrated with an $^{241}$AmBe $(\alpha,n)$-source.
 This fast neutron source gives rise to elastic and inelastic neutron-nucleus scatters, and can thus be employed to define the expected signal region for inelastic WIMP-nucleus scatters.
@@
 
-As explained in Section~\ref{sec:intro}, the inelastic scattering of a WIMP with a $^{129}$Xe nucleus produces an energy deposit via a NR with subsequent emission of  
+As explained in Section~\ref{sec:intro}, the inelastic scattering of a WIMP with a $^{129}$Xe nucleus is expected to produce an energy deposit via a NR with subsequent emission of  
 a 39.6\,keV de-excitation photon. The largest fraction of the energy released in the event is via an ER, due to the emitted photon which loses its energy in the LXe.
 This represents an unusual signature compared to the one expected from an elastic scatter, and brings the signal region to overlap with the ER background region.
+{\textcolor{red} {Should we mention that AmBe data is used here, to define these regions? And should we provide somewhere the used energy ranges in cS1 and cS2?}}
 The selected region of interest (ROI) for this analysis surrounds the 39.6\,keV xenon line in the cS1-cS2 plane and is further divided into
 sub-regions, as shown in Figures~\ref{fig:SR} and~\ref{fig:SR2}.
-These sub-regions were defined such as to contain roughly a similar number of expected background events in each region.
-The control regions CR1 and CR2 are chosen to be as close as possible to the signal regions,  and are used as cross check of the background shape distribution.
+These sub-regions were defined such as to roughly contain a similar number of expected background events in each region.
+The control regions (denoted as CR1 and CR2 in the figures), are selected to be as close as possible to the signal regions,  and are used for cross checks of the background shape distribution.
 
-Apart from the condition to occur in the defined region of interest in the cS2-cS1-plane, valid events are required to fulfil several selection criteria, 
+Apart from the condition to occur in the defined region of interest in the (cS2,cS1)-plane, valid events are required to fulfil several selection criteria, 
 which can be summarised as follows: basic data quality cuts, energy selection and S2 threshold cut, veto cut for events with energy release in the detector's active LXe shield, 
 selection of single-scatter events and of a predefined fiducial volume.
-
-This analysis closely follows the event selection criteria described in detail in \cite{Aprile:2012vw} for Run-II, with only a few exceptions reported in what follows. 
+Our analysis closely follows the event selection criteria described in detail in \cite{Aprile:2012vw} for Run-II, with only a few exceptions, as explained in the following.
 The cut on the width of the S2 signal as a function of drift time (where the maximal drift time is 176\,$\mu$s and the width values range from $\sim$1-2\,$\mu$s) has been optimised on a sample of events selected from the 39.6\,keV line and set to a 95\% acceptance on these.
@@
 second largest S2 peak. For this analysis, the threshold has been optimised to 160\,PE and set constant as function of S2 signal size. 
-Finally, the chosen fiducial volume corresponds to 34\,kg of liquid xenon.
+Finally, the chosen fiducial volume corresponds to 34\,kg of liquid xenon, which is identical to the one used for the elastic scattering channel~\cite{Aprile:2012vw}.
 
@@
   \includegraphics[width=\linewidth]{images/bkg_in_sr.png}
-  \caption{Signal (1-9) and control (CR1 and CR2) regions for the inelastic WIMP-$^{129}$Xe interaction in the cS2 versus cS1 plane. Their definition is given in the text.}
+  \caption{Signal (1-9) and control (CR1 and CR2) regions for the inelastic WIMP-$^{129}$Xe interaction in the cS2 versus cS1 plane.
+Their definition is given in the text.
+{\textcolor{red} {We should also write which data is shown here; if this is the first plot in the paper, it may not be clear why the signal and control regions are where they are...}}}
   \label{fig:SR}
@@
 the simultaneous nuclear recoil of the xenon atom. The detected light (S1) and charge (S2) signals are simulated separately for each of the two contributions 
-and then added together. This is due to the fact that the light and charge yields depend on the type of interaction (ER vs. NR), and on the deposited energy.
+and then added together. This recipe has been followed  because the light and charge yields depend both on the type of interaction (ER vs. NR), and on the deposited energy.
 
-The distribution of an ER induced by the de-excitation photon in the cS1-cS2 plane  is simulated assuming a two dimensional normal probability distribution function (pdf), $f(cS1_{er},cS2_{er})$, 
+The distribution of an ER induced by the de-excitation photon in the (cS1,cS2)-plane  is simulated assuming a two dimensional normal probability distribution function (pdf), $f(cS1_{er},cS2_{er})$, 
 described (apart from a constant normalisation factor) by the following equation:
@@
 
-The same model is used to predict the charge yield at 39.6\,keV, which is afterwards scaled according to the detector's secondary scintillation gain $Y$. 
+The same model is used to predict the charge yield at 39.6\,keV, which is then scaled according to the detector's secondary scintillation gain $Y$. 
  The latter is determined from detector's response to single electrons~\cite{SingleE}.
@@
 
+{\textcolor{red} {Should we also give the numerical values of $L_Y$ and $Y$?}}
 The pdf of the ER and NR contributions are then convoluted together to obtain the overall pdf of the expected signal.
@@
 a dedicated computation has been performed in these cases. The combined acceptance  of all selection criteria in the region of interest averages to $\sim$$(0.80\pm0.05)$. 
-Figure~\ref{fig:SR} shows an example of fully simulated signal model for a WIMP mass of 100\,GeV/c$^2$.
+Figure~\ref{fig:unc} shows an example of fully simulated signal model for a WIMP mass of 100\,GeV/c$^2$.
 
 The signal simulation procedure has been validated by reproducing the 39.6\,keV xenon line from interactions due to neutrons from the 
-$^{124}$AmBe source and comparison to data. For this comparison, the proper  $^{124}$AmBe nuclear recoil and acceptances
+$^{124}$AmBe source and comparison to data. For this comparison, the  $^{124}$AmBe nuclear recoil interactions and their acceptances
 were simulated. The simulated events were in agreement  with calibration data within statistical uncertainties. 
@@
 The expected background is modelled using data from the $^{60}$Co calibration campaign, which are assumed to well represent the background density distribution 
-in the cS1-cS2 plane. The calibration sample yields  about $2.2\times10^4$ events in the ROI; these are then scaled to the science data according to a measured scale 
+in the (cS1,cS2)-plane. The calibration sample yields  about $2.2\times10^4$ events in the ROI; these are then scaled to the science data according to a measured scale 
 factor $\tau_{bkg}$.
-This scale factor, which is merely the ratio between the data and calibration sample yields, is measured in the two control regions shown in Figure~\ref{fig:SR} and labelled CR1 and CR2.
-The two control
-regions give compatible results and the computed average is $\tau_{bkg} \, =  \, 0.034 \pm 0.002 $, where the reported uncertainty 
+This scale factor, which is merely the ratio between the data and calibration sample yields, is measured in the two control regions shown in Figure~\ref{fig:SR} (labelled CR1 and CR2).
+The two control regions give compatible results and the computed average is $\tau_{bkg} \, =  \, 0.034 \pm 0.002 $, where the reported uncertainty
 is of statistical nature only.

### 2017-01-20 Inelastic/intro.tex
fixed_typos_and_some_text_added_more_comments_in_red

@@
 Most direct detection searches focus on elastic scattering of galactic dark matter particles off nuclei, where the keV-scale 
-nuclear recoil energy is to be detected~\cite{Baudis:2012ig,Baudis:2015mpa,Undagoitia:2015gya}. In this work, the 
+nuclear recoil energy is to be detected~\cite{Baudis:2012ig,Undagoitia:2015gya,Baudis:2015mpa}. In this work, the 
 alternative process of inelastic scattering is explored, where a WIMP-nucleus scattering induces a transition to a low-lying 
@@
 We consider the $^{129}\text{Xe}$ isotope, which has an abundance of 26.4\% in natural xenon, and a lowest-lying 
-3/2$^{+}$ state at 36.6\,keV above the 1/2$^+$ gound state. The electromnagnetic nuclear decay has a half-life of 0.97\,s. 
-The signatures of inelastic scattering in xenon have been studied in detail in~\cite{Baudis:2013bba}. It was found that this 
-channel is complementary to spin-dependent, elastic scattering, dominating the integrated rates above $\simeq10$\,keV energy 
-depositions. In addition, in case of a positive signal, the observation of inelastic scattering would provide a clear 
+3/2$^{+}$ state at 36.6\,keV above the 1/2$^+$ ground state. The electromagnetic nuclear decay has a half-life of 0.97\,s. 
+The signatures and structure functions for inelastic scattering in xenon have been studied in detail in~\cite{Baudis:2013bba}.
+It was found that this channel is complementary to spin-dependent, elastic scattering, and that it dominates the integrated rates above $\simeq10$\,keV energy depositions.
+In addition, in case of a positive signal, the observation of inelastic scattering would provide a clear 
 indication of the spin-dependent nature of the fundamental interaction.
 
-Our paper is structures as follows.  In Section~\ref{sec:xenon100} we briefly describe the XENON100 detector and the employed data 
-set in this analysis. In Section~\ref{sec:analysis} we detail the data analysis method, including the simulation of the expected signal and the 
-background model. We conclude in Section~\ref{sec:results} with our results and new constraints on inelastic WIMP-nucleus scatters.
+This paper is structured as follows.  In Section~\ref{sec:xenon100} we briefly describe the main features of the XENON100 detector.  In Section~\ref{sec:analysis} we introduce the employed data 
+set in this analysis and detail the data analysis method, including the simulation of the expected signal and the 
+background model. We conclude in Section~\ref{sec:results} with our results, and discuss the new constraints on inelastic WIMP-nucleus interactions.
 
@@
 del Gran Sasso (LNGS) in Italy. It contains 161\,kg of xenon in total,  with  62\,kg in the active region of the TPC. These 
-are monitored by 242 1-inch square, low-radioactivity, UV-sensitive photomultiplier tubes (PMTs) arranged in two arrays, one in the liquid 
+are monitored by 178 1-inch square, low-radioactivity, UV-sensitive photomultiplier tubes (PMTs) arranged in two arrays, one in the liquid 
 and one in the gas. The PMTs detect the prompt scintillation (S1) and the delayed, proportional scintillation signal (S2) 
@@
 The ratio S2/S1 provides the basis for distinguishing between nuclear recoils (NRs), as induced by fast neutrons and expected from elastic WIMP-nucleus scatters, and electronic recoils (ERs) produced by $\beta$ and $\gamma$-rays.
+A 4\,cm thick liquid xenon (LXe) layer surrounds the TPC and is monitored by 64 1-inch square PMTs, providing an effective active veto for further background reduction.
 
@@
 and spin-dependent~\cite{Aprile:2013doa,Aprile:2016swn} elastic WIMP-nucleus 
-scatters, on solar axions and galactic ALPs~\cite{Aprile:2014eoa}, as well as on leptophilic dark matter models~\cite{Aprile:2015ade,Aprile:2015ibr,Aprile:2017yea}.
+scatters, on solar axions and galactic ALPs~\cite{Aprile:2014eoa}, as well as on leptophilic dark matter models~\cite{Aprile:2015ade,Aprile:2015ibr,Aprile:2017yea} that were invented to explain the annual modulation signature observed in the DAMA/LIBRA experiment~\cite{Bernabei:2012in}.
 
-Here we explore a potential new signature in the XENON100 detector, caused by spin-dependent, inelastic WIMP-$^{129}$Xe scatters. The expected  
-inelastic scattering signature is a combination of an ER and a NR, due to the short lifetime of the excited nuclear state and  the short mean free path of $\sim$0.15\,mm of the 39.6\,keV de-excitation photon.
+Here we explore a new potential dark matter channel in the XENON100 detector, caused by spin-dependent, inelastic WIMP-$^{129}$Xe interactions.
+The expected inelastic scattering signature is a combination between an ER and a NR, due to the short lifetime of the excited nuclear state and  the short mean free path of $\sim$0.15\,mm of the 39.6\,keV de-excitation photon.

### 2017-01-20 Inelastic/results.tex
fixed_typos_and_some_text_added_more_comments_in_red

@@
 
+{\textcolor{red} {Should we first say that we do not observe any signal, given that the observed rate is compatible with the expected background?}}
 This result is interpreted via a binned profiled likelihood approach by means of the test statistic $\tilde{q}$
@@
 Our result is shown in Figure~\ref{fig:limits}, together with the expected median sensitivity and its relative one and two  standard deviation uncertainty.
-The most constraining upper limit is  $3.3 \times 10^{-38}$\,cm$^{2}$ (at 90\% CL$_s$ confidence level) is for a WIMP of mass 100\,GeV/c$^2$.
+The most constraining upper limit is  at a cross section of $3.3 \times 10^{-38}$\,cm$^{2}$ (at 90\% CL$_s$ confidence level), for a WIMP of mass 100\,GeV/c$^2$.
 
@@
 Our limit improves upon the XMASS result and constrains new parameter space for the spin-dependent, inelastic scattering cross section.
-While these upper limits are not competitive to spin-dependent, elastic scattering results, as obtained by XENON100~\cite{Aprile:2013doa} and LUX~\cite{Akerib:2016lao} (with a cross section minimum of $\sim2 \times 10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/cm$^2$ WIMP), our results set the pathway for a sensitive search of inelastic WIMP-nucleus scattering in running or upcoming liquid xenon experiments such as XENON1T~\cite{Aprile:2015uzo}, XENONnT~\cite{Aprile:2015uzo},  LZ~\cite{Akerib:2015cja}, and DARWIN~\cite{Aalbers:2016jon}.
+While these upper limits are not competitive to spin-dependent, elastic scattering results, as obtained by XENON100~\cite{Aprile:2013doa} and LUX~\cite{Akerib:2016lao} (with a cross section minimum of $\sim2 \times 10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/c$^2$ WIMP), our results set the pathway for a sensitive search of inelastic WIMP-nucleus scattering in running or upcoming liquid xenon experiments such as XENON1T~\cite{Aprile:2015uzo}, XENONnT~\cite{Aprile:2015uzo},  LZ~\cite{Akerib:2015cja}, and DARWIN~\cite{Aalbers:2016jon}.
 In these larger detectors, with lower intrinsic backgrounds from $^{85}$Kr and $^{222}$Rn decays, and improved self-shielding, the electronic recoil background will be reduced by a few orders of magnitude with respect to XENON100, and ultimately dominated by solar neutrino interactions~\cite{Baudis:2013qla}.
+The discovery of this interaction channel would be a clear signature for a spin-dependent nature of the interaction, and would provide a potential handle  to constrain the WIMP mass with data from one experiment only~\cite{Baudis:2013bba}.
 
-The discovery of this interaction channel would be a clear signature for a spin-dependent nature of the interaction, and would provide a potential handle  to constrain the WIMP mass~\cite{Baudis:2013bba}.
-
-%\newpage
+\newpage

### 2017-01-23 Inelastic/analysis.tex
Some editing after discussion

@@
 
+\begin{figure*}[t!]
+	\begin{subfigure}{0.49\linewidth}
+		\includegraphics[width=\linewidth]{images/wimp_in_sr.png}
+		\subcaption{}
+	\end{subfigure}
+	\begin{subfigure}{0.49\linewidth}
+		\includegraphics[width=\linewidth]{images/bkg_in_sr.png}
+		\subcaption{}
+	\end{subfigure}
+	\caption{\raggedright Signal (1-9) and control (CR1 and CR2) regions for the inelastic WIMP-$^{129}$Xe interaction in the (cS2,cS1)-plane. 
+		Figure (a) shows the signal distribution for a simulated WIMP of mass 100\,GeV/c$^2$, while Figure (b) is obtained using  $^{60}$Co calibration data 
+		and represent the background expectation distribution.}
+  \label{fig:SR}
+\end{figure*}
+
 \subsection{Signal Correction}
@@
 These signals are thus corrected in 3 dimensions, using various calibration data, as detailed in~\cite{Aprile:2011dd,Aprile:2012vw}, with the corrected quantities denoted as cS1 and cS2, and defined in~\cite{Aprile:2012vw}.
-The trigger efficiency in this run was 100\% for S2$>$300\,PE.
+%The trigger efficiency in this run was 100\% for S2$>$300\,PE.
 
@@
 This represents an unusual signature compared to the one expected from an elastic scatter, and brings the signal region to overlap with the ER background region.
-{\textcolor{red} {Should we mention that AmBe data is used here, to define these regions? And should we provide somewhere the used energy ranges in cS1 and cS2?}}
-The selected region of interest (ROI) for this analysis surrounds the 39.6\,keV xenon line in the cS1-cS2 plane and is further divided into
-sub-regions, as shown in Figures~\ref{fig:SR} and~\ref{fig:SR2}.
+%{\textcolor{red} {Should we mention that AmBe data is used here, to define these regions? And should we provide somewhere the used energy ranges in cS1 and cS2?}}
+The selected region of interest (ROI) for this analysis surrounds the 39.6\,keV xenon line in the (cS1,cS2)-plane 
+\textcolor{red} {and is based on $^{124}$AmBe calibration data, it extends from 60 to 200\,PE in cS1 and from 4$\times \, 10^3$ to 16$\times \, 10^3$\,PE in cS2, it is further divided  into sub-regions}
+\sout{and is further divided into sub-regions,} as shown 
+in Figure~\ref{fig:SR}.
 These sub-regions were defined such as to roughly contain a similar number of expected background events in each region.
@@
 
-Apart from the condition to occur in the defined region of interest in the (cS2,cS1)-plane, valid events are required to fulfil several selection criteria, 
+Apart from the condition to occur in the defined region of interest in the (cS1,cS2)-plane, valid events are required to fulfil several selection criteria, 
 which can be summarised as follows: basic data quality cuts, energy selection and S2 threshold cut, veto cut for events with energy release in the detector's active LXe shield, 
-selection of single-scatter events and of a predefined fiducial volume.
+selection of single-scatter events and of a predefined fiducial volume 
+\textcolor{red}{of 34\,kg}.  
 Our analysis closely follows the event selection criteria described in detail in \cite{Aprile:2012vw} for Run-II, with only a few exceptions, as explained in the following. 
 The cut on the width of the S2 signal as a function of drift time (where the maximal drift time is 176\,$\mu$s and the width values range from $\sim$1-2\,$\mu$s) has been optimised on a sample of events selected from the 39.6\,keV line and set to a 95\% acceptance on these.
-This cut ensures that the S2-signal width is consistent with the $z$-position calculated from the observed time difference between the S1 and S1 signals.
+This cut ensures that the S2-signal width is consistent with the $z$-position calculated from the observed time difference between the S1 and S2 signals.
 Events are required to be single-scatters by applying a threshold cut on the size of the
 second largest S2 peak. For this analysis, the threshold has been optimised to 160\,PE and set constant as function of S2 signal size. 
-Finally, the chosen fiducial volume corresponds to 34\,kg of liquid xenon, which is identical to the one used for the elastic scattering channel~\cite{Aprile:2012vw}.
-
-\begin{figure}[t!]
-  \includegraphics[width=\linewidth]{images/bkg_in_sr.png}
-  \caption{Signal (1-9) and control (CR1 and CR2) regions for the inelastic WIMP-$^{129}$Xe interaction in the cS2 versus cS1 plane.
-Their definition is given in the text.
-{\textcolor{red} {We should also write which data is shown here; if this is the first plot in the paper, it may not be clear why the signal and control regions are where they are...}}}
-  \label{fig:SR}
-\end{figure}
+\sout{Finally, the chosen fiducial volume corresponds to 34\,kg of liquid xenon, which is identical to the one used for the elastic scattering channel~\cite{Aprile:2012vw}}.
 
@@
 \begin{multline}
-	f(cS1_{er},cS2_{er})  = {\rm exp} \Big\{ -\frac{1}{2(1-\rho^2)} \Big[ \frac{(cS1_{er} - \mu_{cS1_{er}})^2}{\sigma_{cs1}^2} + \\ 
-	 \frac{(cS2_{er} - \mu_{cS2_{er}})^2}{\sigma_{cs2}^2} - \frac{2\rho\cdot(cS1_{er} - \mu_{cs1}) (cS2_{er} - \mu_{cs2})} {\sigma_{cs1}\sigma_{cs2}} \Big] \Big\}
+	f(cS1_{er},cS2_{er})  = {\rm exp} \Big\{ -\frac{1}{2(1-\rho^2)} \Big[ \frac{(cS1_{er} - \mu_{cS1})^2}{\sigma_{cs1}^2} + \\ 
+	 \frac{(cS2_{er} - \mu_{cS2})^2}{\sigma_{cs2}^2} - \frac{2\rho\cdot(cS1_{er} - \mu_{cs1}) (cS2_{er} - \mu_{cs2})} {\sigma_{cs1}\sigma_{cs2}} \Big] \Big\}
 	%f(cS1,cS2) ~ = ~  \frac{1}{2 \pi \sigma_{cs1} \sigma_cs2 \sqrt{1-\rho^{2}} } exp \Big( -\frac{1}{2(1-\rho^2)} \Big[ \frac{(cS1 - \hat{cS1})^2}{\sigma_{cs1}^2} \Big] \Big)
@@
 while $\rho$ stands for the correlation between the cS1 and cS2 signals. The detector-related light yield $L_y$  at 39.6\,keV, necessary to evaluate the average number of prompt photons detected 
-($\mu_{cS1}$), is obtained from the NEST model~\cite{NEST,Geant1,Geant2} fit to data collected with several $\gamma$-lines.  The average light yield at 39.6\,keV is 2.7\,PE/keV.
+($\mu_{cS1}$), is obtained from the NEST model~\cite{NEST,Geant1,Geant2} fit to data collected with several $\gamma$-lines.
+%%%%% REMOVEME %%%%%%
+\sout{The average light yield at 39.6\,keV is 2.7\,PE/keV.}
 
@@
 
-{\textcolor{red} {Should we also give the numerical values of $L_Y$ and $Y$?}}
+%%%%% DEPENDING ON if we add it before %%%%%
+%{\textcolor{red} {Should we also give the numerical values of $L_Y$ and $Y$?}}
 The pdf of the ER and NR contributions are then convoluted together to obtain the overall pdf of the expected signal.
 A 2D (cS1 versus cS2) acceptance map is applied to the signal pdf to reproduce data selection effects. Acceptances are computed separately for each selection 
-criteria using the $^{124}$AmBe calibration sample. Other selections such as the liquid xenon veto cut, and the single-scatter interaction represent an exception  and 
+criteria using the $^{124}$AmBe calibration sample. \textcolor{red}{Acceptances of} other selections such as the liquid xenon veto cut, and the single-scatter interaction represent an exception  and 
 a dedicated computation has been performed in these cases. The combined acceptance  of all selection criteria in the region of interest averages to $\sim$$(0.80\pm0.05)$. 
@@
 The signal simulation procedure has been validated by reproducing the 39.6\,keV xenon line from interactions due to neutrons from the 
-$^{124}$AmBe source and comparison to data. For this comparison, the  $^{124}$AmBe nuclear recoil interactions and their acceptances
+$^{124}$AmBe source and compared to data. For this comparison, the  $^{124}$AmBe nuclear recoil interactions and their acceptances
 were simulated. The simulated events were in agreement  with calibration data within statistical uncertainties. 
-{\textcolor{red} {Should we show an example, namely a figure from the signal model note?}}
-
-\begin{figure}[t!]
-  \includegraphics[width=\linewidth]{images/wimp_in_sr.png}
-  \caption{Simulated signal (1-9) and control (CR1 and CR2) regions for a WIMP mass 100\,GeV/c$^2$.}
-  \label{fig:SR2}
-\end{figure}
+%%%%%% DEPENDS on the journal  %%%%%
+%{\textcolor{red} {Should we show an example, namely a figure from the signal model note?}}
 
@@
 
-The background in the region of interest for inelastic scattering is dominated by ERs due the residual radioactivity of detector materials, due to $^{85}$Kr present in the liquid xenon ($\sim$55\%) as well as due to $^{222}$Rn decays in the liquid ($<$7\%)~\cite{Aprile:2011vb}.
+The background in the region of interest for inelastic scattering is dominated by ERs due to the residual radioactivity of detector materials, due to $^{85}$Kr present in the liquid xenon ($\sim$55\%) as well as due to $^{222}$Rn decays in the liquid ($<$7\%)~\cite{Aprile:2011vb}.
 The background contribution from inelastic scatters of radiogenic or cosmogenic neutrons (producing a 39.6\,keV de-excitation line) is negligible thanks to the very low expected neutron scattering rate in the detector~\cite{Aprile:2013tov}.
@@
 factor $\tau_{bkg}$.
-This scale factor, which is merely the ratio between the data and calibration sample yields, is measured in the two control regions shown in Figure~\ref{fig:SR} (labelled CR1 and CR2).
+This scale factor, which is merely the ratio between the data and calibration sample yields, is measured in the two control regions shown in Figure~\ref{fig:SR} (labelled CR1 and CR2) separately.
 The two control regions give compatible results and the computed average is $\tau_{bkg} \, =  \, 0.034 \pm 0.002 $, where the reported uncertainty
@@
 and agreement was found within statistical uncertainties. Furthermore, $^{60}$Co calibration data have been compared in the region of interest to  
-data from the $^{232}$Th calibration campaign, and the largest deviation between the two shapes is within 4\%. An additional systematic
-uncertainty of 4\% has thus been applied to the expected background yield of each sub-region of the ROI.
-{\textcolor{red} {Should we show a figure, namely the agreement of data and BG model for the control regions? Like the second figure in the background model check note.}}
+data from the $^{232}$Th calibration campaign, and the largest deviation between the two shapes is within 4\%. 
+%%%%% Said later anyway, propose to remove it here %%%%%
+\sout{An additional systematic uncertainty of 4\% has thus been applied to the expected background yield of each sub-region of the ROI.}
+
+%%%%%% DEPENDS on the journal  %%%%%
+%{\textcolor{red} {Should we show a figure, namely the agreement of data and BG model for the control regions? Like the second figure in the background model check note.}}
 
@@
 
-%FIXME: maybe change region definitions in order to have the sub-region 9 labelled as 7, so the signal would "nicely" look like a bump.
 \begin{figure}[t!]
   \includegraphics[width=\linewidth]{images/wimp_sys_unc.png}
-  \caption{Predicted signal (blue curve), along with statistical and systematic uncertainties (cyan region) simulated for a WIMP mass of 100\,GeV/c$^2$.
-The signal and its uncertainties are shown as a function of the signal region number {\textcolor{red} {Maybe there is a better way to say this, or leave out?}}.
-The signal has been scaled for a total number of 50 events.
-}
+  \caption{Predicted signal \textcolor{red} {yield in each sub-region} (blue curve), along with statistical and systematic uncertainties (cyan area) simulated for a WIMP mass of 100\,GeV/c$^2$.  
+	   The signal has been scaled for a total number of 50 events. }
   \label{fig:unc}
@@
 Systematic uncertainty on the shape of the predicted background distribution are assessed by the maximal observed discrepancy in the ROI between
-the $^{60}$Co and $^{232}$Th calibration samples.  As explained, a 4\% systematic uncertainty is added  to the expected yield of each sub-region.
+the $^{60}$Co and $^{232}$Th calibration samples.  
+\sout{As explained} A 4\% systematic uncertainty is added  to the expected yield of each sub-region.
 Uncertainties belonging to different sub-regions in the ROI are considered independent from one another.
-%It is important not only to describe correctly the expected total background but also its distribution
 
@@
 that these uncertainties mainly affect the pdf of the signal model in the ROI, and very weakly the total signal yield. 
-%For each WIMP mass we simulate several signal pseudo-sample, which are produced varying the model parameters  respectively of $\pm 1$ standard deviation. 
 They are taken into account by simulating several signal pseudo-samples for each WIMP mass, where the pseudo-samples are produced 
@@
 For each sub-region an overall uncertainty is then computed, by adding in quadrature the variations of each pseudo-sample 
-%FIXME: explain this better, the up variation are separated from down variations and added together
 with respect to nominal. Figure~\ref{fig:unc} shows an example of such a systematic uncertainty computation for a WIMP mass of 100\,GeV/c$^2$.
 
-%FIXME: express this in an understandable way
-All the uncertainties discussed here are parameterised with a binned profile likelihood function using the framework from~\cite{roostat,roofit}.
+All the uncertainties discussed here are parameterised 
+\sout{with}  \textcolor{red}{within} 
+a binned profile likelihood function using the \textcolor{red}{ROOSTAT-ROOFIT framework}~\cite{roostat,roofit}.
+\sout{using the framework from}~\cite{roostat,roofit}.
 All the parameters related to systematic uncertainties are assumed to be normally distributed.

### 2017-01-23 Inelastic/intro.tex
Some editing after discussion

@@
 We consider the $^{129}\text{Xe}$ isotope, which has an abundance of 26.4\% in natural xenon, and a lowest-lying 
-3/2$^{+}$ state at 36.6\,keV above the 1/2$^+$ ground state. The electromagnetic nuclear decay has a half-life of 0.97\,s. 
+3/2$^{+}$ state at 36.6\,keV above the 1/2$^+$ ground state. The electromagnetic nuclear decay has a half-life of 0.97\,ns. 
 The signatures and structure functions for inelastic scattering in xenon have been studied in detail in~\cite{Baudis:2013bba}.
@@
 is produced. These photons carry the $(x,y)$ information of the interaction site, while the $z-$information comes from the drift time measurement. The TPC 
-thus yields a three-dimensional event localisation, with an $(x,y)$ resolution of $<$3\,mm (1\,$\sigma$), and a $z$ resolution of  $<$0.3\,mm (1\,$\sigma$), enabling to reject the majority of background events via fiducial volume cuts~\cite{Aprile:2011dd}.
+thus yields a three-dimensional event localisation, with an $(x,y)$ resolution of $<$3\,mm (1\,$\sigma$), and a $z$ resolution of  $<$0.3\,mm (1\,$\sigma$), enabling to reject the majority of background events via fiducial volume selections~\cite{Aprile:2011dd}.
 The ratio S2/S1 provides the basis for distinguishing between nuclear recoils (NRs), as induced by fast neutrons and expected from elastic WIMP-nucleus scatters, and electronic recoils (ERs) produced by $\beta$ and $\gamma$-rays.
@@
 and spin-dependent~\cite{Aprile:2013doa,Aprile:2016swn} elastic WIMP-nucleus 
-scatters, on solar axions and galactic ALPs~\cite{Aprile:2014eoa}, as well as on leptophilic dark matter models~\cite{Aprile:2015ade,Aprile:2015ibr,Aprile:2017yea} that were invented to explain the annual modulation signature observed in the DAMA/LIBRA experiment~\cite{Bernabei:2012in}.
+scatters, on solar axions and galactic ALPs~\cite{Aprile:2014eoa}, as well as on leptophilic dark matter models~\cite{Aprile:2015ade,Aprile:2015ibr,Aprile:2017yea} 
+%%%% possible to be CUTTED %%%%%%%%% 
+that were invented to explain the annual modulation signature observed in the DAMA/LIBRA experiment~\cite{Bernabei:2012in}.
 
+%%%%%% possible to be CUTTED %%%%%%%%%
 Here we explore a new potential dark matter channel in the XENON100 detector, caused by spin-dependent, inelastic WIMP-$^{129}$Xe interactions.

### 2017-01-23 Inelastic/results.tex
Some editing after discussion

--- 2017-01-19 Inelastic/results.tex
@@
 
-Using a fiducial volume containing 34\,kg of liquid xenon and 224.6~live days of data yields 764 events observed  in the region of interest.
-This number is compatible with the expectation of $756 \, \pm \, 5 \,{\rm (stat)} \, \pm 55\, {\rm (syst)}$ events from the background only hypothesis. 
+\textcolor{red} {This search is performed using XENON100 Run-II science data, which corresponds to an exposure of 34\,$\times$\,224.6\,kg\,$\cdot$\,days. 
+A total of 764 events are observed in the region of interest and no evidence of dark matter can be assessed base on an expected background of
+$756 \, \pm \, 5 \,{\rm (stat)} \, \pm 55\, {\rm (syst)}$ events. }
+\sout{Using a fiducial volume containing 34\,kg of liquid xenon and 224.6~live days of data yields 764 events observed  in the region of interest.
+This number is compatible with the expectation of $756 \, \pm \, 5 \,{\rm (stat)} \, \pm 55\, {\rm (syst)}$ events from the background only hypothesis.} 
 Figure~\ref{fig:dataVSbkg} shows the distribution of  events  in the region of interest, where the bottom panel displays the ratio
@@
 on the background expectation, respectively. The expected signal for a WIMP mass of 100\,GeV/c$^2$, and normalised to a total of 50 events, is also shown.
-
-%\newpage
 
@@
 and its asymptotic distributions, as  described in \cite{asympt}. 
-Assuming  an isothermal WIMP halo with a local density of $\rho_{\chi} \, = \, 0.3$\,GeV/cm$^3$, a local circular velocity of $v_0 \,= \, 220$\,km/s, and a galactic escape velocity of $v_{\rm{esc}} \, = \, 544$\,km/s,
-\textcolor{blue}{other assumptions...,} a 90\% CL$_s$~\cite{cls} confidence level upper limit on the spin-dependent inelastic WIMP-nucleon cross section as a function of WIMP mass is computed.
-We employ the nuclear structure factors as calculated in \cite{Baudis:2013qla}, based on state-of-the-art large-scale shell-model calculations, with chiral effective field theory WIMP-nucleon currents.
+Assuming  an isothermal WIMP halo with a local density of $\rho_{\chi} \, = \, 0.3$\,GeV/cm$^3$, a local circular velocity of $v_0 \,= \, 220$\,km/s, 
+a galactic escape velocity of $v_{\rm{esc}} \, = \, 544$\,km/s 
+\textcolor{red} {and the nuclear structure factors as computed in}~\cite{Baudis:2013qla}, 
+a 90\% CL$_s$~\cite{cls} confidence level upper limit is set on the spin-dependent inelastic WIMP-nucleon cross section as a function of the WIMP mass. 
+\sout{We employ the nuclear structure factors as calculated in \cite{Baudis:2013qla}, based on state-of-the-art large-scale shell-model calculations, with chiral effective field theory WIMP-nucleon currents.}
 
-\begin{figure}[h]
+\begin{figure}[th]
   \includegraphics[width=\linewidth]{images/limit_reb.png}
@@
 
-Our limit improves upon the XMASS result and constrains new parameter space for the spin-dependent, inelastic scattering cross section.
-While these upper limits are not competitive to spin-dependent, elastic scattering results, as obtained by XENON100~\cite{Aprile:2013doa} and LUX~\cite{Akerib:2016lao} (with a cross section minimum of $\sim2 \times 10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/cm$^2$ WIMP), our results set the pathway for a sensitive search of inelastic WIMP-nucleus scattering in running or upcoming liquid xenon experiments such as XENON1T~\cite{Aprile:2015uzo}, XENONnT~\cite{Aprile:2015uzo},  LZ~\cite{Akerib:2015cja}, and DARWIN~\cite{Aalbers:2016jon}.
+\sout{Our limit improves upon the XMASS result and constrains new parameter space for the spin-dependent, inelastic scattering cross section. }
+While these upper limits are not competitive to spin-dependent, elastic scattering results, as obtained by XENON100~\cite{Aprile:2013doa} and LUX~\cite{Akerib:2016lao} (with a cross section minimum of $\sim2 \times 10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/c$^2$ WIMP), our results set the pathway for a sensitive search of inelastic WIMP-nucleus scattering in running or upcoming liquid xenon experiments such as XENON1T~\cite{Aprile:2015uzo}, XENONnT~\cite{Aprile:2015uzo},  LZ~\cite{Akerib:2015cja}, and DARWIN~\cite{Aalbers:2016jon}.
 In these larger detectors, with lower intrinsic backgrounds from $^{85}$Kr and $^{222}$Rn decays, and improved self-shielding, the electronic recoil background will be reduced by a few orders of magnitude with respect to XENON100, and ultimately dominated by solar neutrino interactions~\cite{Baudis:2013qla}.
+The discovery of this interaction channel would be a clear signature for a spin-dependent nature of the interaction, and would provide a potential handle  to constrain the WIMP mass with data from one experiment only~\cite{Baudis:2013bba,McCabe:2016aof}.
 
-The discovery of this interaction channel would be a clear signature for a spin-dependent nature of the interaction, and would provide a potential handle  to constrain the WIMP mass~\cite{Baudis:2013bba}.
-
-%\newpage
+\newpage

### 2017-01-23 Inelastic/analysis.tex
Some editing after discussion

@@
 	\caption{\raggedright Signal (1-9) and control (CR1 and CR2) regions for the inelastic WIMP-$^{129}$Xe interaction in the (cS2,cS1)-plane.
-		Figure (a) shows the signal distribution for a simulated WIMP of mass 100\,GeV/c$^2$, while Figure (b) is obtained using  $^{60}$Co calibration data 
-		and represent the background expectation distribution.}
+		\textcolor{red}{Figure (a) shows the signal distribution for a simulated WIMP of mass 100\,GeV/c$^2$, while Figure (b) is obtained using  $^{60}$Co calibration data 
+	and represent the background expectation distribution.}}
   \label{fig:SR}

### 2017-01-23 Inelastic/analysis.tex
Some editing after discussion

@@
 This analysis is performed using XENON100 Run-II science data, with 224.6~live days of data taking.
-The detector's response to ERs has been characterised with $^{60}$Co and $^{232}$Th calibration sources, while the response to NRs was calibrated with an $^{241}$AmBe $(\alpha,n)$-source.
+The detector's response to ERs has been characterized with $^{60}$Co and $^{232}$Th calibration sources, while the response to NRs was calibrated with an $^{241}$AmBe $(\alpha,n)$-source.
 This fast neutron source gives rise to elastic and inelastic neutron-nucleus scatters, and can thus be employed to define the expected signal region for inelastic WIMP-nucleus scatters.
@@
 Apart from the condition to occur in the defined region of interest in the (cS1,cS2)-plane, valid events are required to fulfil several selection criteria, 
-which can be summarised as follows: basic data quality cuts, energy selection and S2 threshold cut, veto cut for events with energy release in the detector's active LXe shield, 
+which can be summarized as follows: basic data quality cuts, energy selection and S2 threshold cut, veto cut for events with energy release in the detector's active LXe shield, 
 selection of single-scatter events and of a predefined fiducial volume 
@@
 Our analysis closely follows the event selection criteria described in detail in \cite{Aprile:2012vw} for Run-II, with only a few exceptions, as explained in the following. 
-The cut on the width of the S2 signal as a function of drift time (where the maximal drift time is 176\,$\mu$s and the width values range from $\sim$1-2\,$\mu$s) has been optimised on a sample of events selected from the 39.6\,keV line and set to a 95\% acceptance on these.
+The cut on the width of the S2 signal as a function of drift time (where the maximal drift time is 176\,$\mu$s and the width values range from $\sim$1-2\,$\mu$s) has been optimized on a sample of events selected from the 39.6\,keV line and set to a 95\% acceptance on these.
 This cut ensures that the S2-signal width is consistent with the $z$-position calculated from the observed time difference between the S1 and S2 signals.
 Events are required to be single-scatters by applying a threshold cut on the size of the
-second largest S2 peak. For this analysis, the threshold has been optimised to 160\,PE and set constant as function of S2 signal size. 
+second largest S2 peak. For this analysis, the threshold has been optimized to 160\,PE and set constant as function of S2 signal size. 
 \sout{Finally, the chosen fiducial volume corresponds to 34\,kg of liquid xenon, which is identical to the one used for the elastic scattering channel~\cite{Aprile:2012vw}}.
@@
 The distribution of an ER induced by the de-excitation photon in the (cS1,cS2)-plane  is simulated assuming a two dimensional normal probability distribution function (pdf), $f(cS1_{er},cS2_{er})$, 
-described (apart from a constant normalisation factor) by the following equation:
+described (apart from a constant normalization factor) by the following equation:
 
@@
 quenching  of ER and NRs, respectively, due to the electric field \cite{ScintQuenching}.
-The parameterisation and uncertainties of $\mathcal{L}_{eff}$ as a function of nuclear recoil energy $E_{nr}$ are based on existing
-direct measurements \cite{run8Result}. The light yield for 122\,keV ERs is taken from the same NEST model fit as described above. For cS2, the parameterisation 
+The parameterization and uncertainties of $\mathcal{L}_{eff}$ as a function of nuclear recoil energy $E_{nr}$ are based on existing
+direct measurements \cite{run8Result}. The light yield for 122\,keV ERs is taken from the same NEST model fit as described above. For cS2, the parameterization 
 of $Q_{Y}(E_{nr})$ is taken from \cite{QY}. Finally, all detector related resolution effects are introduced following the prescriptions described in \cite{Aprile:2012vw}.

### 2017-01-23 Inelastic/intro.tex
Some editing after discussion

@@
 del Gran Sasso (LNGS) in Italy. It contains 161\,kg of xenon in total,  with  62\,kg in the active region of the TPC. These 
-are monitored by 178 1-inch square, low-radioactivity, UV-sensitive photomultiplier tubes (PMTs) arranged in two arrays, one in the liquid 
+are monitored by 178 1-inch square, low-radioactivity, UV-sensitive photo-multiplier tubes (PMTs) arranged in two arrays, one in the liquid 
 and one in the gas. The PMTs detect the prompt scintillation (S1) and the delayed, proportional scintillation signal (S2) 
-created by a particle interacting in the active TPC region. The S2-signal is generated due to ionisation electrons, drifted 
+created by a particle interacting in the active TPC region. The S2-signal is generated due to ionization electrons, drifted 
 in an electric field of 530\,V/cm and extracted into the gas phase by a stronger field of $\sim$ 12\,kV/cm, where the proportional scintillation, or electroluminiscence, 
 is produced. These photons carry the $(x,y)$ information of the interaction site, while the $z-$information comes from the drift time measurement. The TPC 
-thus yields a three-dimensional event localisation, with an $(x,y)$ resolution of $<$3\,mm (1\,$\sigma$), and a $z$ resolution of  $<$0.3\,mm (1\,$\sigma$), enabling to reject the majority of background events via fiducial volume selections~\cite{Aprile:2011dd}.
+thus yields a three-dimensional event localization, with an $(x,y)$ resolution of $<$3\,mm (1\,$\sigma$), and a $z$ resolution of  $<$0.3\,mm (1\,$\sigma$), enabling to reject the majority of background events via fiducial volume selections~\cite{Aprile:2011dd}.
 The ratio S2/S1 provides the basis for distinguishing between nuclear recoils (NRs), as induced by fast neutrons and expected from elastic WIMP-nucleus scatters, and electronic recoils (ERs) produced by $\beta$ and $\gamma$-rays.

### 2017-01-23 Inelastic/results.tex
Some editing after discussion

@@
 between data and expected background. The grey and orange shaded areas represent the statistical and systematic uncertainty 
-on the background expectation, respectively. The expected signal for a WIMP mass of 100\,GeV/c$^2$, and normalised to a total of 50 events, is also shown.
+on the background expectation, respectively. The expected signal for a WIMP mass of 100\,GeV/c$^2$, and normalized to a total of 50 events, is also shown.
 
@@
   \includegraphics[width=\linewidth]{images/data_vs_bkg.png}
-  \caption{Distribution of  observed events  in the region of interest (data points), along with the normalised distribution from calibration data (filled histogram).
+  \caption{Distribution of  observed events  in the region of interest (data points), along with the normalized distribution from calibration data (filled histogram).
 The bottom panel displays the ratio
 between data and expected background, where the grey and orange shaded areas represent the statistical and systematic uncertainty 
-on the background expectation, respectively. The expected signal for a WIMP mass of 100\,GeV/c$^2$ (blue dashed), and normalised to a total of 50 events, is also shown.}
+on the background expectation, respectively. The expected signal for a WIMP mass of 100\,GeV/c$^2$ (blue dashed), and normalized to a total of 50 events, is also shown.}
   \label{fig:dataVSbkg}

### 2017-01-24 Inelastic/analysis.tex
Added_abstract_removed_sout_text

@@
 		\textcolor{red}{Figure (a) shows the signal distribution for a simulated WIMP of mass 100\,GeV/c$^2$, while Figure (b) is obtained using  $^{60}$Co calibration data 
-	and represent the background expectation distribution.}}
+	and represents the background expectation distribution.}}
   \label{fig:SR}
@@
 The selected region of interest (ROI) for this analysis surrounds the 39.6\,keV xenon line in the (cS1,cS2)-plane 
-\textcolor{red} {and is based on $^{124}$AmBe calibration data, it extends from 60 to 200\,PE in cS1 and from 4$\times \, 10^3$ to 16$\times \, 10^3$\,PE in cS2, it is further divided  into sub-regions}
-\sout{and is further divided into sub-regions,} as shown 
+\textcolor{red} {and is based on $^{241}$AmBe calibration data.
+It extends from 60 to 200\,PE in cS1 and from 4$\times \, 10^3$ to 16$\times \, 10^3$\,PE in cS2, and it is further divided  into sub-regions}, as shown
 in Figure~\ref{fig:SR}.
@@
 second largest S2 peak. For this analysis, the threshold has been optimized to 160\,PE and set constant as function of S2 signal size.
-\sout{Finally, the chosen fiducial volume corresponds to 34\,kg of liquid xenon, which is identical to the one used for the elastic scattering channel~\cite{Aprile:2012vw}}.
 
@@
 
-The distribution of an ER induced by the de-excitation photon in the (cS1,cS2)-plane  is simulated assuming a two dimensional normal probability distribution function (pdf), $f(cS1_{er},cS2_{er})$, 
+The distribution of an ER induced by the de-excitation photon in the (cS1,cS2)-plane  is simulated assuming a two dimensional normal probability distribution function (pdf), $f(\rm{cS1}_{er},\rm{cS2}_{er})$,
 described (apart from a constant normalization factor) by the following equation:
@@
 where $\mu_{cS1}$ and $\mu_{cS2}$ 
-represent the average observed $cS1_{er}$ and $cS2_{er}$ signals given a 39.6\,keV ER, $\sigma_{cs1}$ and $\sigma_{cs2}$ are the standard deviation in $cS1_{er}$ and $cS2_{er}$ respectively,
+represent the average observed $\rm{cS1_{er}}$ and $\rm{cS2_{er}}$ signals given a 39.6\,keV ER, $\sigma_{cs1}$ and $\sigma_{cs2}$ are the standard deviation in $\rm{cS1_{er}}$ and $\rm{cS2_{er}}$ respectively,
 while $\rho$ stands for the correlation between the cS1 and cS2 signals. The detector-related light yield $L_y$  at 39.6\,keV, necessary to evaluate the average number of prompt photons detected 
@@
 %%%%% REMOVEME %%%%%%
-\sout{The average light yield at 39.6\,keV is 2.7\,PE/keV.}
+%The average light yield at 39.6\,keV is 2.7\,PE/keV.
 
@@
 deviations $\sigma_{cs1}$, $\sigma_{cs2}$.  The correlation parameter is assumed to be independent of energy (at least in the considered narrow energy range) and measured
-using the 164\,keV line from the decay of the $^{131m}$Xe isomer ($T_{1/2}$=11.8\,d) produced during the  $^{124}$AmBe run.
+using the 164\,keV line from the decay of the $^{131m}$Xe isomer ($T_{1/2}$=11.8\,d) produced during the  $^{241}$AmBe run.
 This $\gamma$-line is chosen because it allows to disentangle efficiently the contribution from the nuclear recoil.
@@
 A 2D (cS1 versus cS2) acceptance map is applied to the signal pdf to reproduce data selection effects. Acceptances are computed separately for each selection 
-criteria using the $^{124}$AmBe calibration sample. \textcolor{red}{Acceptances of} other selections such as the liquid xenon veto cut, and the single-scatter interaction represent an exception  and 
+criteria using the $^{241}$AmBe calibration sample. \textcolor{red}{Acceptances of} other selections such as the liquid xenon veto cut, and the single-scatter interaction represent an exception  and 
 a dedicated computation has been performed in these cases. The combined acceptance  of all selection criteria in the region of interest averages to $\sim$$(0.80\pm0.05)$. 
@@
 %%%%% Said later anyway, propose to remove it here %%%%%
-\sout{An additional systematic uncertainty of 4\% has thus been applied to the expected background yield of each sub-region of the ROI.}
+%\sout{An additional systematic uncertainty of 4\% has thus been applied to the expected background yield of each sub-region of the ROI.}
 
@@
 \caption{Predicted signal \textcolor{red} {yield in each sub-region} (blue curve), along with statistical and systematic uncertainties (cyan area) simulated for a WIMP mass of 100\,GeV/c$^2$.
-	   The signal has been scaled for a total number of 50 events. }
+The signal has been scaled for a total number of 50 events.}
   \label{fig:unc}
@@
 the $^{60}$Co and $^{232}$Th calibration samples.  
-\sout{As explained} A 4\% systematic uncertainty is added  to the expected yield of each sub-region.
+ A 4\% systematic uncertainty is added  to the expected yield of each sub-region.
 Uncertainties belonging to different sub-regions in the ROI are considered independent from one another.
@@
 All the uncertainties discussed here are parameterised 
-\sout{with}  \textcolor{red}{within} 
+ \textcolor{red}{within} 
 a binned profile likelihood function using the \textcolor{red}{ROOSTAT-ROOFIT framework}~\cite{roostat,roofit}.
-\sout{using the framework from}~\cite{roostat,roofit}.
 All the parameters related to systematic uncertainties are assumed to be normally distributed.

### 2017-01-24 Inelastic/inelastic_main.tex
updated_intro_and_ref
updated_xenon100_started_analysis_section
Some editing after discussion
Added_abstract_removed_sout_text

@@
 
+\usepackage[normalem]{ulem}
 \usepackage{color}
-\usepackage{graphicx}% Include figure files
+\usepackage{subcaption,graphicx}% Include figure files
 \usepackage{dcolumn}% Align table columns on decimal point
@@
 
-\title{Search for WIMP Inelastic Scattering Off Xenon Nuclei With Xenon100 Data}% Force line breaks with \\
+\title{Search for WIMP Inelastic Scattering Off Xenon Nuclei With XENON100 Data}% Force line breaks with \\
 
@@
 \begin{abstract}
-	Some nice abstract here.....
+We present first constraints on the spin-dependent, inelastic scattering cross section of Weakly Interacting Massive Particles (WIMPs) on nucleons from XENON100 data with an exposure of 7.64$\times$10$^3$\,kg\,day.
+XENON100 is a dual-phase xenon time projection chamber with 62\,kg of active mass, operated at the Laboratori Nazionali del Gran Sasso (LNGS) in Italy and designed to search for nuclear recoils from WIMP-nucleus interactions.
+Here we explore inelastic scattering, where a transition to a low-lying excited nuclear state of $^{129}$Xe is induced, with the experimental signature being a nuclear recoil observed together with the prompt de-excitation photon.
+We see no evidence for inelastic WIMP-$^{129}$Xe interactions, and a profile likelihood analysis allows us to set a 90\% C.L.
+upper limit on the inelastic, spin-dependent WIMP-nucleon cross section of $3.3 \times 10^{-38}$\,cm$^{2}$  at 100\,GeV/c$^2$.
+This is the most constraining result to date, and sets the pathway for an analysis of this interaction channel in upcoming, larger dual-phase xenon detectors.
+
 \end{abstract}
@@
 
-%\input{biblio.tex}
-
 \bibliography{inelastic_main} 

### 2017-01-24 Inelastic/results.tex
Added_abstract_removed_sout_text

@@
 \textcolor{red} {This search is performed using XENON100 Run-II science data, which corresponds to an exposure of 34\,$\times$\,224.6\,kg\,$\cdot$\,days. 
-A total of 764 events are observed in the region of interest and no evidence of dark matter can be assessed base on an expected background of
+A total of 764 events are observed in the region of interest and no evidence of dark matter can be assessed based on an expected background of
 $756 \, \pm \, 5 \,{\rm (stat)} \, \pm 55\, {\rm (syst)}$ events. }
-\sout{Using a fiducial volume containing 34\,kg of liquid xenon and 224.6~live days of data yields 764 events observed  in the region of interest.
-This number is compatible with the expectation of $756 \, \pm \, 5 \,{\rm (stat)} \, \pm 55\, {\rm (syst)}$ events from the background only hypothesis.} 
 Figure~\ref{fig:dataVSbkg} shows the distribution of  events  in the region of interest, where the bottom panel displays the ratio
@@
 a 90\% CL$_s$~\cite{cls} confidence level upper limit is set on the spin-dependent inelastic WIMP-nucleon cross section as a function of the WIMP mass. 
-\sout{We employ the nuclear structure factors as calculated in \cite{Baudis:2013qla}, based on state-of-the-art large-scale shell-model calculations, with chiral effective field theory WIMP-nucleon currents.}
+%\sout{We employ the nuclear structure factors as calculated in \cite{Baudis:2013qla}, based on state-of-the-art large-scale shell-model calculations, with chiral effective field theory WIMP-nucleon currents.}
 
@@
 
-\sout{Our limit improves upon the XMASS result and constrains new parameter space for the spin-dependent, inelastic scattering cross section. }
-While these upper limits are not competitive to spin-dependent, elastic scattering results, as obtained by XENON100~\cite{Aprile:2013doa} and LUX~\cite{Akerib:2016lao} (with a cross section minimum of $\sim2 \times 10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/c$^2$ WIMP), our results set the pathway for a sensitive search of inelastic WIMP-nucleus scattering in running or upcoming liquid xenon experiments such as XENON1T~\cite{Aprile:2015uzo}, XENONnT~\cite{Aprile:2015uzo},  LZ~\cite{Akerib:2015cja}, and DARWIN~\cite{Aalbers:2016jon}.
+%\sout{Our limit improves upon the XMASS result and constrains new parameter space for the spin-dependent, inelastic scattering cross section. }
+While these upper limits are not competitive to spin-dependent, elastic scattering results, as obtained by XENON100~\cite{Aprile:2013doa} and LUX~\cite{Akerib:2016lao} (with a cross section minimum of $\sim2 \times 10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/c$^2$ WIMP), our results
+\textcolor{red} {are the most stringent for the spin-dependent inelastic channel, and}
+set the pathway for a sensitive search of inelastic WIMP-nucleus scattering in running or upcoming liquid xenon experiments such as XENON1T~\cite{Aprile:2015uzo}, XENONnT~\cite{Aprile:2015uzo},  LZ~\cite{Akerib:2015cja}, and DARWIN~\cite{Aalbers:2016jon}.
 In these larger detectors, with lower intrinsic backgrounds from $^{85}$Kr and $^{222}$Rn decays, and improved self-shielding, the electronic recoil background will be reduced by a few orders of magnitude with respect to XENON100, and ultimately dominated by solar neutrino interactions~\cite{Baudis:2013qla}.

### 2017-01-25 Inelastic/analysis.tex
Added figure, good candidate for VERSION 1.0

@@
 \begin{figure*}[t!]
-	\begin{subfigure}{0.49\linewidth}
-		\includegraphics[width=\linewidth]{images/wimp_in_sr.png}
-		\subcaption{}
-	\end{subfigure}
-	\begin{subfigure}{0.49\linewidth}
-		\includegraphics[width=\linewidth]{images/bkg_in_sr.png}
-		\subcaption{}
-	\end{subfigure}
-	\caption{\raggedright Signal (1-9) and control (CR1 and CR2) regions for the inelastic WIMP-$^{129}$Xe interaction in the (cS2,cS1)-plane.
-		\textcolor{red}{Figure (a) shows the signal distribution for a simulated WIMP of mass 100\,GeV/c$^2$, while Figure (b) is obtained using  $^{60}$Co calibration data 
-	and represents the background expectation distribution.}}
+	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/wimp_in_sr.png}}
+	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/bkg_in_sr.png}}
+	\caption{Signal (1-9) and control (CR1 and CR2) regions for the inelastic WIMP-$^{129}$Xe interaction in the (cS2,cS1)-plane.
+		Figure (a) shows the signal distribution for a simulated WIMP of mass 100\,GeV/c$^2$ normalized to 50\,events, while Figure (b) is obtained using  
+		normalized $^{60}$Co calibration data and represents the background expectation distribution.}
   \label{fig:SR}
@@
 This represents an unusual signature compared to the one expected from an elastic scatter, and brings the signal region to overlap with the ER background region.
-%{\textcolor{red} {Should we mention that AmBe data is used here, to define these regions? And should we provide somewhere the used energy ranges in cS1 and cS2?}}
 The selected region of interest (ROI) for this analysis surrounds the 39.6\,keV xenon line in the (cS1,cS2)-plane 
-\textcolor{red} {and is based on $^{241}$AmBe calibration data.
-It extends from 60 to 200\,PE in cS1 and from 4$\times \, 10^3$ to 16$\times \, 10^3$\,PE in cS2, and it is further divided  into sub-regions}, as shown
-in Figure~\ref{fig:SR}.
+and is based on $^{241}$AmBe calibration data.
+The ROI extends from 60 to 210\,PE in cS1 and from 4$\times \, 10^3$ to 16$\times \, 10^3$\,PE in cS2, furthermore it is divided  into sub-regions, as shown in Figure~\ref{fig:SR}.
 These sub-regions were defined such as to roughly contain a similar number of expected background events in each region.
-The control regions (denoted as CR1 and CR2 in the figures), are selected to be as close as possible to the signal regions,  and are used for cross checks of the background shape distribution.
+The control regions (denoted as CR1 and CR2 in the figures), are selected to be as close as possible to the ROI,  and are used for cross checks of the background shape distribution.
 
 Apart from the condition to occur in the defined region of interest in the (cS1,cS2)-plane, valid events are required to fulfil several selection criteria, 
-which can be summarized as follows: basic data quality cuts, energy selection and S2 threshold cut, veto cut for events with energy release in the detector's active LXe shield, 
-selection of single-scatter events and of a predefined fiducial volume 
-\textcolor{red}{of 34\,kg}.  
+which can be summarized as follows: basic data quality cuts, energy selection and S2 threshold cut, veto cut for events with energy release in the detector's 
+active LXe shield, selection of single-scatter events and of a predefined fiducial volume of 34\,kg.  
 Our analysis closely follows the event selection criteria described in detail in \cite{Aprile:2012vw} for Run-II, with only a few exceptions, as explained in the following. 
@@
 %The average light yield at 39.6\,keV is 2.7\,PE/keV.
-
 The same model is used to predict the charge yield at 39.6\,keV, which is then scaled according to the detector's secondary scintillation gain $Y$. 
@@
 A 2D (cS1 versus cS2) acceptance map is applied to the signal pdf to reproduce data selection effects. Acceptances are computed separately for each selection 
-criteria using the $^{241}$AmBe calibration sample. \textcolor{red}{Acceptances of} other selections such as the liquid xenon veto cut, and the single-scatter interaction represent an exception  and 
+criteria using the $^{241}$AmBe calibration sample. Acceptances of other selections such as the liquid xenon veto cut, and the single-scatter interaction represent an exception  and 
 a dedicated computation has been performed in these cases. The combined acceptance  of all selection criteria in the region of interest averages to $\sim$$(0.80\pm0.05)$. 
-Figure~\ref{fig:unc} shows an example of fully simulated signal model for a WIMP mass of 100\,GeV/c$^2$.
+Figure~\ref{fig:SR}\,(a) shows an example of fully simulated signal model for a WIMP mass of 100\,GeV/c$^2$.
 
@@
   \includegraphics[width=\linewidth]{images/wimp_sys_unc.png}
-\caption{Predicted signal \textcolor{red} {yield in each sub-region} (blue curve), along with statistical and systematic uncertainties (cyan area) simulated for a WIMP mass of 100\,GeV/c$^2$.
+\caption{Predicted signal yield in each sub-region (blue curve), along with statistical and systematic uncertainties (shaded area) simulated for a WIMP mass of 100\,GeV/c$^2$.
 The signal has been scaled for a total number of 50 events.}
@@
 by varying the model parameters within their $\pm 1$ standard deviations. 
-For each sub-region an overall uncertainty is then computed, by adding in quadrature the variations of each pseudo-sample 
+For each sub-region, an overall uncertainty is then computed by adding in quadrature the variations of each pseudo-sample 
 with respect to nominal. Figure~\ref{fig:unc} shows an example of such a systematic uncertainty computation for a WIMP mass of 100\,GeV/c$^2$.
 
-All the uncertainties discussed here are parameterised 
- \textcolor{red}{within} 
-a binned profile likelihood function using the \textcolor{red}{ROOSTAT-ROOFIT framework}~\cite{roostat,roofit}.
+All the uncertainties discussed here are parameterised within a binned profile likelihood function using the ROOSTAT-ROOFIT framework~\cite{roostat,roofit}.
 All the parameters related to systematic uncertainties are assumed to be normally distributed.

### 2017-01-25 Inelastic/results.tex
Added figure, good candidate for VERSION 1.0

@@
 
-\textcolor{red} {This search is performed using XENON100 Run-II science data, which corresponds to an exposure of 34\,$\times$\,224.6\,kg\,$\cdot$\,days. 
+This search is performed using XENON100 Run-II science data, which corresponds to an exposure of 34\,$\times$\,224.6\,kg\,$\cdot$\,days. 
 A total of 764 events are observed in the region of interest and no evidence of dark matter can be assessed based on an expected background of
-$756 \, \pm \, 5 \,{\rm (stat)} \, \pm 55\, {\rm (syst)}$ events. }
+$756 \, \pm \, 5 \,{\rm (stat)} \, \pm 55\, {\rm (syst)}$ events. 
 Figure~\ref{fig:dataVSbkg} shows the distribution of  events  in the region of interest, where the bottom panel displays the ratio
-between data and expected background. The grey and orange shaded areas represent the statistical and systematic uncertainty 
-on the background expectation, respectively. The expected signal for a WIMP mass of 100\,GeV/c$^2$, and normalized to a total of 50 events, is also shown.
+between data and expected background. The light and dark blue shaded areas represent the statistical and systematic uncertainty 
+on the background expectation, respectively. The expected signal for a WIMP mass of 100\,GeV/c$^2$, normalized to a total of 50 events, is also shown.
 
@@
 The bottom panel displays the ratio
-between data and expected background, where the grey and orange shaded areas represent the statistical and systematic uncertainty 
-on the background expectation, respectively. The expected signal for a WIMP mass of 100\,GeV/c$^2$ (blue dashed), and normalized to a total of 50 events, is also shown.}
+between data and expected background, where the light  and dark blue shaded areas represent the statistical and systematic uncertainty 
+on the background expectation, respectively. The expected signal for a WIMP mass of 100\,GeV/c$^2$ (blue dashed), normalized to a total of 50 events, is also shown.}
   \label{fig:dataVSbkg}
@@
 a galactic escape velocity of $v_{\rm{esc}} \, = \, 544$\,km/s 
-\textcolor{red} {and the nuclear structure factors as computed in}~\cite{Baudis:2013qla}, 
+and the nuclear structure factors as computed in~\cite{Baudis:2013qla}, 
 a 90\% CL$_s$~\cite{cls} confidence level upper limit is set on the spin-dependent inelastic WIMP-nucleon cross section as a function of the WIMP mass. 
@@
   \includegraphics[width=\linewidth]{images/limit_reb.png}
-  \caption{Upper limit (black curve) on the spin-dependent, inelastic WIMP-nucleon cross section as a function of WIMP mass.
-The expected median sensitivity (dashed curve) along with the relative one (green area) and two (yellow area) standard deviation uncertainty is also shown.
+  \caption{Upper limit (blue curve) on the spin-dependent, inelastic WIMP-nucleon cross section as a function of WIMP mass.  
+	  %The expected median sensitivity (dashed curve) along with 
+	  The expected one (light shaded area) and two ( dark shaded area) standard deviation uncertainty is also shown. 
 	  This result is compared to the upper limit (at 90\% C.L.) obtained by the XMASS experiment (red curve)~\cite{Uchida:2014cnn}.}
@@
 
-Our result is shown in Figure~\ref{fig:limits}, together with the expected median sensitivity and its relative one and two  standard deviation uncertainty.
-The most constraining upper limit is  at a cross section of $3.3 \times 10^{-38}$\,cm$^{2}$ (at 90\% CL$_s$ confidence level), for a WIMP of mass 100\,GeV/c$^2$.
+Our result is shown in Figure~\ref{fig:limits}, together with its expected one and two  standard deviation uncertainty.
+The most constraining upper limit is  set for for a WIMP of mass 100\,GeV/c$^2$ to a cross section of $3.3 \times 10^{-38}$\,cm$^{2}$ (at 90\% CL$_s$ confidence level).
 
 This results is compared to the one obtained by the XMASS experiment~\cite{Uchida:2014cnn}, a single phase liquid xenon detector, which used a fiducial volume containing 41\,kg of LXe and 165.9~live days of data.
-\textcolor{blue}{Decide which other experiment to also plot - DAMA LXe?
-However only XMASS uses the same form factors as we do.}
 
-%\sout{Our limit improves upon the XMASS result and constrains new parameter space for the spin-dependent, inelastic scattering cross section. }
-While these upper limits are not competitive to spin-dependent, elastic scattering results, as obtained by XENON100~\cite{Aprile:2013doa} and LUX~\cite{Akerib:2016lao} (with a cross section minimum of $\sim2 \times 10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/c$^2$ WIMP), our results
-\textcolor{red} {are the most stringent for the spin-dependent inelastic channel, and}
-set the pathway for a sensitive search of inelastic WIMP-nucleus scattering in running or upcoming liquid xenon experiments such as XENON1T~\cite{Aprile:2015uzo}, XENONnT~\cite{Aprile:2015uzo},  LZ~\cite{Akerib:2015cja}, and DARWIN~\cite{Aalbers:2016jon}.
+While these upper limits are not competitive to spin-dependent, elastic scattering results, as obtained by XENON100~\cite{Aprile:2013doa} and LUX~\cite{Akerib:2016lao} 
+(bounding the cross section to be $<\,10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/c$^2$ WIMP), 
+%(with a cross section minimum of $\sim2 \times 10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/c$^2$ WIMP), 
+our results are the most stringent for the spin-dependent inelastic channel, and set the pathway for a sensitive search of inelastic WIMP-nucleus scattering in running or upcoming liquid xenon experiments such as XENON1T~\cite{Aprile:2015uzo}, XENONnT~\cite{Aprile:2015uzo},  LZ~\cite{Akerib:2015cja}, and DARWIN~\cite{Aalbers:2016jon}.
 In these larger detectors, with lower intrinsic backgrounds from $^{85}$Kr and $^{222}$Rn decays, and improved self-shielding, the electronic recoil background will be reduced by a few orders of magnitude with respect to XENON100, and ultimately dominated by solar neutrino interactions~\cite{Baudis:2013qla}.

### 2017-01-25 Inelastic/results.tex
fixed small typo on possible VERSION 1.0

@@
 While these upper limits are not competitive to spin-dependent, elastic scattering results, as obtained by XENON100~\cite{Aprile:2013doa} and LUX~\cite{Akerib:2016lao} 
-(bounding the cross section to be $<\,10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/c$^2$ WIMP), 
+(bounding the cross section to be $<\,2 \times 10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/c$^2$ WIMP), 
 %(with a cross section minimum of $\sim2 \times 10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/c$^2$ WIMP), 

### 2017-03-15 Inelastic/analysis.tex
added all minor comments from reviwers

@@
 The detector's response to ERs has been characterized with $^{60}$Co and $^{232}$Th calibration sources, while the response to NRs was calibrated with an $^{241}$AmBe $(\alpha,n)$-source.
-This fast neutron source gives rise to elastic and inelastic neutron-nucleus scatters, and can thus be employed to define the expected signal region for inelastic WIMP-nucleus scatters.
+The fast neutron from the latter gives rise to elastic and inelastic neutron-nucleus scatters, and can thus be employed to define the expected signal region for inelastic WIMP-nucleus scatters.
 
@@
 The warping of the top meshes (inducing a variation in the width of the gas gap between the anode and the liquid-gas interface), the absorption of electrons by residual impurities as they drift towards the gas region, as well as solid angle effects lead to a position-dependent S2 signal.
-These signals are thus corrected in 3 dimensions, using various calibration data, as detailed in~\cite{Aprile:2011dd,Aprile:2012vw}, with the corrected quantities denoted as cS1 and cS2, and defined in~\cite{Aprile:2012vw}.
+These signals are thus corrected in 3 dimensions, using various calibration data, as detailed in~\cite{Aprile:2011dd,Aprile:2012vw}, with the corrected quantities denoted as cS1 and cS2, defined in~\cite{Aprile:2012vw}.
 %The trigger efficiency in this run was 100\% for S2$>$300\,PE.
@@
 
-As explained in Section~\ref{sec:intro}, the inelastic scattering of a WIMP with a $^{129}$Xe nucleus is expected to produce an energy deposit via a NR with subsequent emission of  
-a 39.6\,keV de-excitation photon. The largest fraction of the energy released in the event is via an ER, due to the emitted photon which loses its energy in the LXe.
-This represents an unusual signature compared to the one expected from an elastic scatter, and brings the signal region to overlap with the ER background region.
-The selected region of interest (ROI) for this analysis surrounds the 39.6\,keV xenon line in the (cS1,cS2)-plane 
+As explained in Section~\ref{sec:intro}, the inelastic scattering of a WIMP with a $^{129}$Xe nucleus is expected to produce an energy deposit via a NR with the subsequent emission of  
+a 39.6\,keV de-excitation photon. The largest fraction of the energy released in the event is via the ER, due to the emitted photon which loses its energy in the LXe.
+This represents an unusual signature compared to the one expected from an elastic scatter, and makes the signal region to overlap the ER background region.
+The region of interest (ROI) selected for this analysis surrounds the 39.6\,keV xenon line in the (cS1,cS2)-plane 
 and is based on $^{241}$AmBe calibration data.
 The ROI extends from 60 to 210\,PE in cS1 and from 4$\times \, 10^3$ to 16$\times \, 10^3$\,PE in cS2, furthermore it is divided  into sub-regions, as shown in Figure~\ref{fig:SR}.
-These sub-regions were defined such as to roughly contain a similar number of expected background events in each region.
+These sub-regions were defined to  contain a (roughly) similar number of expected background events in each region.
 The control regions (denoted as CR1 and CR2 in the figures), are selected to be as close as possible to the ROI,  and are used for cross checks of the background shape distribution.
 
-Apart from the condition to occur in the defined region of interest in the (cS1,cS2)-plane, valid events are required to fulfil several selection criteria, 
+Apart from the condition to occur in the defined ROI, valid events are required to fulfil several selection criteria, 
 which can be summarized as follows: basic data quality cuts, energy selection and S2 threshold cut, veto cut for events with energy release in the detector's 
 active LXe shield, selection of single-scatter events and of a predefined fiducial volume of 34\,kg.  
-Our analysis closely follows the event selection criteria described in detail in \cite{Aprile:2012vw} for Run-II, with only a few exceptions, as explained in the following. 
+Our analysis closely follows the event selection criteria described in detail in \cite{Aprile:2012vw} for Run-II, with the few exceptions described below. 
 The cut on the width of the S2 signal as a function of drift time (where the maximal drift time is 176\,$\mu$s and the width values range from $\sim$1-2\,$\mu$s) has been optimized on a sample of events selected from the 39.6\,keV line and set to a 95\% acceptance on these.
-This cut ensures that the S2-signal width is consistent with the $z$-position calculated from the observed time difference between the S1 and S2 signals.
+This cut ensures that the broadening of S2-signals due to diffusion is consistent with the $z$-position calculated from the observed time difference between the S1 and S2 signals.
 Events are required to be single-scatters by applying a threshold cut on the size of the
-second largest S2 peak. For this analysis, the threshold has been optimized to 160\,PE and set constant as function of S2 signal size.
+second largest S2 peak. For this analysis, the threshold has been optimized to 160\,PE and is constant with respect to S2 signal size.
 
@@
 
-The detector response to inelastic WIMP-$^{129}$Xe interactions was simulated using an empirical signal model.
+The detector response to inelastic WIMP-$^{129}$Xe interactions was simulated using an empirical signal model, described in this section.
 The total deposited energy is divided into two independent contributions: one coming from the 39.6\,keV de-excitation photon and the other  from  
@@
 using the 164\,keV line from the decay of the $^{131m}$Xe isomer ($T_{1/2}$=11.8\,d) produced during the  $^{241}$AmBe run.
-This $\gamma$-line is chosen because it allows to disentangle efficiently the contribution from the nuclear recoil.
+This $\gamma$-line is chosen since, unlike the 39.6\,keV line,  is not associated with a NR and a measure of the (cS1,cS2) correlation of a pure ER interaction is possible.
 The measured correlation coefficient is $\rho \, = \, -0.45 \pm 0.10$.
@@
 of WIMP inelastic interactions~\cite{Baudis:2013bba}. The average cS1 and cS2 are given by equations~\ref{f:cs1} and~\ref{f:cs2} respectively,
-where $\mathcal{L}_{eff}$ is the liquid xenon relative scintillation efficiency for NRs, while $S_{ee} \, = \, 0.58$  and $S_{nr} \, = \, 0.95$ describe the scintillation 
-quenching  of ER and NRs, respectively, due to the electric field \cite{ScintQuenching}.
-The parameterization and uncertainties of $\mathcal{L}_{eff}$ as a function of nuclear recoil energy $E_{nr}$ are based on existing
-direct measurements \cite{run8Result}. The light yield for 122\,keV ERs is taken from the same NEST model fit as described above. For cS2, the parameterization 
+where $\mathcal{L}_{eff}$ is the liquid xenon scintillation efficiency for NRs relative to 122\,keVee, while $S_{ee} \, = \, 0.58$  and $S_{nr} \, = \, 0.95$ describe the scintillation 
+quenching due to the electric field of ER and NRs, respectively~\cite{ScintQuenching}. The parameterization and uncertainties of $\mathcal{L}_{eff}$ as a function of nuclear
+recoil energy $E_{nr}$ are based on existing direct measurements \cite{run8Result}.
+The light yield for 122\,keV ERs is taken from the same NEST model fit as described above.
+For cS2, the parameterization
 of $Q_{Y}(E_{nr})$ is taken from \cite{QY}. Finally, all detector related resolution effects are introduced following the prescriptions described in \cite{Aprile:2012vw}.
@@
 %{\textcolor{red} {Should we also give the numerical values of $L_Y$ and $Y$?}}
-The pdf of the ER and NR contributions are then convoluted together to obtain the overall pdf of the expected signal.
+The pdf of the ER and NR contributions are then convolved  to obtain the overall pdf of the expected signal.
 A 2D (cS1 versus cS2) acceptance map is applied to the signal pdf to reproduce data selection effects. Acceptances are computed separately for each selection 
@@
 
-The background in the region of interest for inelastic scattering is dominated by ERs due to the residual radioactivity of detector materials, due to $^{85}$Kr present in the liquid xenon ($\sim$55\%) as well as due to $^{222}$Rn decays in the liquid ($<$7\%)~\cite{Aprile:2011vb}.
+The background in the region of interest for inelastic scattering is dominated by ERs and due to the residual radioactivity of detector materials, to $^{85}$Kr present in the liquid xenon as well as due to $^{222}$Rn decays in the liquid~\cite{Aprile:2011vb}.
 The background contribution from inelastic scatters of radiogenic or cosmogenic neutrons (producing a 39.6\,keV de-excitation line) is negligible thanks to the very low expected neutron scattering rate in the detector~\cite{Aprile:2013tov}.
 
-The expected background is modelled using data from the $^{60}$Co calibration campaign, which are assumed to well represent the background density distribution 
+The expected background is modelled using data from the $^{60}$Co calibration campaign, which are assumed to represent well the background density distribution 
 in the (cS1,cS2)-plane. The calibration sample yields  about $2.2\times10^4$ events in the ROI; these are then scaled to the science data according to a measured scale 
@@
 Systematic uncertainty on the shape of the predicted background distribution are assessed by the maximal observed discrepancy in the ROI between
-the $^{60}$Co and $^{232}$Th calibration samples.  
- A 4\% systematic uncertainty is added  to the expected yield of each sub-region.
+the $^{60}$Co and $^{232}$Th calibration samples, the two samples normalized yield are compared in each sub-region and the largest deviation (incompatible
+with statistical fluctuation) is found to be within 4\%.  A  systematic uncertainty of 4\% is then assigned  to the expected yield of each sub-region.
 Uncertainties belonging to different sub-regions in the ROI are considered independent from one another.
@@
 They are taken into account by simulating several signal pseudo-samples for each WIMP mass, where the pseudo-samples are produced 
-by varying the model parameters within their $\pm 1$ standard deviations. 
-For each sub-region, an overall uncertainty is then computed by adding in quadrature the variations of each pseudo-sample 
-with respect to nominal. Figure~\ref{fig:unc} shows an example of such a systematic uncertainty computation for a WIMP mass of 100\,GeV/c$^2$.
+by varying the model parameters by their $\pm 1$~standard deviation. 
+For each sub-region, an overall uncertainty is then computed by adding in quadrature the residual of each pseudo-sample 
+with respect to the nominal. Figure~\ref{fig:unc} shows an example of such a systematic uncertainty computation for a WIMP mass of 100\,GeV/c$^2$.
 

### 2017-03-15 Inelastic/inelastic_main.tex
Added figure, good candidate for VERSION 1.0
added all minor comments from reviwers

@@
 \usepackage{color}
-\usepackage{subcaption,graphicx}% Include figure files
+\usepackage{graphicx}% Include figure files
+\usepackage[raggedright]{subfigure}
 \usepackage{dcolumn}% Align table columns on decimal point
@@
 \begin{abstract}
-We present first constraints on the spin-dependent, inelastic scattering cross section of Weakly Interacting Massive Particles (WIMPs) on nucleons from XENON100 data with an exposure of 7.64$\times$10$^3$\,kg\,day.
+We present the first constraints on the spin-dependent, inelastic scattering cross section of Weakly Interacting Massive Particles (WIMPs) on nucleons from XENON100 data with an exposure of 7.64$\times$10$^3$\,kg\,day.
 XENON100 is a dual-phase xenon time projection chamber with 62\,kg of active mass, operated at the Laboratori Nazionali del Gran Sasso (LNGS) in Italy and designed to search for nuclear recoils from WIMP-nucleus interactions.
 Here we explore inelastic scattering, where a transition to a low-lying excited nuclear state of $^{129}$Xe is induced, with the experimental signature being a nuclear recoil observed together with the prompt de-excitation photon.
-We see no evidence for inelastic WIMP-$^{129}$Xe interactions, and a profile likelihood analysis allows us to set a 90\% C.L.
+We see no evidence for such inelastic WIMP-$^{129}$Xe interactions, and a profile likelihood analysis allows us to set a 90\% C.L.
 upper limit on the inelastic, spin-dependent WIMP-nucleon cross section of $3.3 \times 10^{-38}$\,cm$^{2}$  at 100\,GeV/c$^2$.

### 2017-03-15 Inelastic/intro.tex
added all minor comments from reviwers

@@
 Astrophysical and cosmological evidence indicates that the dominant mass fraction of our Universe consists of some yet unknown
-form of dark, or invisible matter. The dark matter could be made of new, stable or long-lived and yet undiscovered particles. Well-motivated
-theoretical models going beyond the Standard Model of particle physics predict the existence of Weakly Interacting Massive
+form of dark, or invisible matter. The dark matter could be made of stable or long-lived and yet undiscovered particles. Well-motivated
+theoretical models beyond the Standard Model of particle physics predict the existence of Weakly Interacting Massive
 Particles (WIMPs), which are natural candidates for dark matter. This hypothesis is currently being tested by several direct
@@
 
-This paper is structured as follows.  In Section~\ref{sec:xenon100} we briefly describe the main features of the XENON100 detector.  In Section~\ref{sec:analysis} we introduce the employed data 
-set in this analysis and detail the data analysis method, including the simulation of the expected signal and the 
+This paper is structured as follows.  In Section~\ref{sec:xenon100} we briefly describe the main features of the XENON100 detector.  In Section~\ref{sec:analysis} we introduce the data 
+sets employed in this analysis and detail the data analysis method, including the simulation of the expected signal and the 
 background model. We conclude in Section~\ref{sec:results} with our results, and discuss the new constraints on inelastic WIMP-nucleus interactions.
@@
 in an electric field of 530\,V/cm and extracted into the gas phase by a stronger field of $\sim$ 12\,kV/cm, where the proportional scintillation, or electroluminiscence, 
-is produced. These photons carry the $(x,y)$ information of the interaction site, while the $z-$information comes from the drift time measurement. The TPC 
-thus yields a three-dimensional event localization, with an $(x,y)$ resolution of $<$3\,mm (1\,$\sigma$), and a $z$ resolution of  $<$0.3\,mm (1\,$\sigma$), enabling to reject the majority of background events via fiducial volume selections~\cite{Aprile:2011dd}.
+take place.
+The horizontal position, $(x,y)$, of the interaction site is reconstructed from the position of the S2 shower, while the depth of the interaction, $z$, is given by the drift time measurement.
+%These photons carry the $(x,y)$ information of the interaction site, while the $z-$information comes from the drift time measurement. 
+The TPC thus yields a three-dimensional event localization, with an $(x,y)$ resolution of $<$3\,mm (1\,$\sigma$), and a $z$ resolution of  $<$0.3\,mm (1\,$\sigma$), enabling to reject the majority of background events via fiducial volume selections~\cite{Aprile:2011dd}.
 The ratio S2/S1 provides the basis for distinguishing between nuclear recoils (NRs), as induced by fast neutrons and expected from elastic WIMP-nucleus scatters, and electronic recoils (ERs) produced by $\beta$ and $\gamma$-rays.
@@
 and spin-dependent~\cite{Aprile:2013doa,Aprile:2016swn} elastic WIMP-nucleus 
-scatters, on solar axions and galactic ALPs~\cite{Aprile:2014eoa}, as well as on leptophilic dark matter models~\cite{Aprile:2015ade,Aprile:2015ibr,Aprile:2017yea} 
+scatters, on solar axions and galactic ALPs~\cite{Aprile:2014eoa}, as well as on leptophilic dark matter models~\cite{Aprile:2015ade,Aprile:2015ibr,Aprile:2017yea}. 
 %%%% possible to be CUTTED %%%%%%%%% 
-that were invented to explain the annual modulation signature observed in the DAMA/LIBRA experiment~\cite{Bernabei:2012in}.
+%that were invented to explain the annual modulation signature observed in the DAMA/LIBRA experiment~\cite{Bernabei:2012in}.
 
 %%%%%% possible to be CUTTED %%%%%%%%%
-Here we explore a new potential dark matter channel in the XENON100 detector, caused by spin-dependent, inelastic WIMP-$^{129}$Xe interactions.
+Here we explore a new potential dark matter interaction channel in the XENON100 detector, caused by spin-dependent, inelastic WIMP-$^{129}$Xe interactions.
 The expected inelastic scattering signature is a combination between an ER and a NR, due to the short lifetime of the excited nuclear state and  the short mean free path of $\sim$0.15\,mm of the 39.6\,keV de-excitation photon.

### 2017-03-15 Inelastic/results.tex
added all minor comments from reviwers

@@
 
-Our result is shown in Figure~\ref{fig:limits}, together with its expected one and two  standard deviation uncertainty.
-The most constraining upper limit is  set for for a WIMP of mass 100\,GeV/c$^2$ to a cross section of $3.3 \times 10^{-38}$\,cm$^{2}$ (at 90\% CL$_s$ confidence level).
+Our result is shown in Figure~\ref{fig:limits}, together with its expected one and two sigma statistical variation.
+The most constraining limit is  set for for a WIMP of mass 100\,GeV/c$^2$ to a cross section of $3.3 \times 10^{-38}$\,cm$^{2}$ (at 90\% CL$_s$ confidence level).
 
-This results is compared to the one obtained by the XMASS experiment~\cite{Uchida:2014cnn}, a single phase liquid xenon detector, which used a fiducial volume containing 41\,kg of LXe and 165.9~live days of data.
+This result is compared to the one obtained by the XMASS experiment~\cite{Uchida:2014cnn}, a single phase liquid xenon detector, which used a fiducial volume containing 41\,kg of LXe and 165.9~live days of data.
 
@@
 %(with a cross section minimum of $\sim2 \times 10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/c$^2$ WIMP), 
-our results are the most stringent for the spin-dependent inelastic channel, and set the pathway for a sensitive search of inelastic WIMP-nucleus scattering in running or upcoming liquid xenon experiments such as XENON1T~\cite{Aprile:2015uzo}, XENONnT~\cite{Aprile:2015uzo},  LZ~\cite{Akerib:2015cja}, and DARWIN~\cite{Aalbers:2016jon}.
-In these larger detectors, with lower intrinsic backgrounds from $^{85}$Kr and $^{222}$Rn decays, and improved self-shielding, the electronic recoil background will be reduced by a few orders of magnitude with respect to XENON100, and ultimately dominated by solar neutrino interactions~\cite{Baudis:2013qla}.
-The discovery of this interaction channel would be a clear signature for a spin-dependent nature of the interaction, and would provide a potential handle  to constrain the WIMP mass with data from one experiment only~\cite{Baudis:2013bba,McCabe:2016aof}.
+our results are the most stringent for the spin-dependent inelastic channel, and set the stage for a sensitive search of inelastic WIMP-nucleus scattering in running or upcoming liquid xenon experiments such as XENON1T~\cite{Aprile:2015uzo}, XENONnT~\cite{Aprile:2015uzo},  LZ~\cite{Akerib:2015cja}, and DARWIN~\cite{Aalbers:2016jon}.
+In these larger detectors, with lower intrinsic backgrounds from $^{85}$Kr and $^{222}$Rn decays, and improved self-shielding, the electronic recoil background will be reduced by a few orders of magnitude with respect to XENON100, and ultimately limited by solar neutrino interactions~\cite{Baudis:2013qla}.
+The discovery of this interaction channel would be a clear signature for a spin-dependent nature of the dark matter interaction, and would provide a potential handle  to constrain the WIMP mass with data from one experiment only~\cite{Baudis:2013bba,McCabe:2016aof}.
 

### 2017-03-16 Inelastic/analysis.tex
Added appendix and rho correction

@@
 \subsection{Signal Simulation} 
+\label{sec:signal}
 
@@
 deviations $\sigma_{cs1}$, $\sigma_{cs2}$.  The correlation parameter is assumed to be independent of energy (at least in the considered narrow energy range) and measured
-using the 164\,keV line from the decay of the $^{131m}$Xe isomer ($T_{1/2}$=11.8\,d) produced during the  $^{241}$AmBe run.
-This $\gamma$-line is chosen since, unlike the 39.6\,keV line,  is not associated with a NR and a measure of the (cS1,cS2) correlation of a pure ER interaction is possible.
-The measured correlation coefficient is $\rho \, = \, -0.45 \pm 0.10$.
+using the 164\,keV line from the decay of the $^{131m}$Xe isomer ($T_{1/2}$=11.8\,d) produced during the  $^{241}$AmBe run. This $\gamma$-line is chosen since, unlike the 39.6\,keV line, 
+it is not associated with a NR and a measure of the (cS1,cS2) correlation of a pure ER interaction is possible. The correlation coefficient however depends on energy due to 
+recombination effects, its measured value at 164\,keV is then corrected based on the NEST expected recombination fractions for those energies. 
+The corrected correlation coefficient is then $\rho \, = \, -0.4 \pm 0.1$.
 
@@
 The signal simulation procedure has been validated by reproducing the 39.6\,keV xenon line from interactions due to neutrons from the 
-$^{124}$AmBe source and compared to data. For this comparison, the  $^{124}$AmBe nuclear recoil interactions and their acceptances
-were simulated. The simulated events were in agreement  with calibration data within statistical uncertainties. 
+$^{124}$AmBe source and compared to data. The simulated events were in agreement  with calibration data within statistical uncertainties, 
+more detail on this validation campaign are reported in the appendix. 
 %%%%%% DEPENDS on the journal  %%%%%

### 2017-03-16 Inelastic/appendix.tex
Added appendix and rho correction

\appendix*

\section{}

\begin{figure*}[h!]
	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_contour.png}}
	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice1.png}} \\
	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice2.png}}
	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice3.png}}
	\caption{A simulation of the 39.6\,keV  xenon line activated from $^{243}$AmBe neutrons is compared with the actual data.
		 Figure~(a) compare counturs of equal density in the (cS1,cS2)-plane, while Figures~(b), (c) and (d) shows the same distribution projected in cS1 for
		 several ranges of cS2, the histograms are normalized to unit area. Light and dark blue represent simulation and data, respectively.
		}

  \label{fig:mc_comp}
\end{figure*}

The detector response to inelastic WIMP-$^{129}$Xe interactions was simulated using an empirical signal model. 
The procedure, described in detail in section~\ref{sec:signal}, take advantage of several 
assumptions and approximations which have been validated extesively. 
The main cross check was to reproduce with simulation the 39.6\,keV xenon line activated from $^{124}$AmBe neutrons. 
For this purpose the NR energy spectrum expected from inelastic neutron-$^{129}$Xe scattering has been obtained via  Monte Carlo techniques, 
we take into account detector response and the non-uniform spatial distribution. Acceptance of analysis selections to this type of interaction 
have been recomputed accordingly, in particular, acceptance to the double scatter cut differ greatly between neutrons and WIMPs scatterings. 
Except for acceptances and NR energy spectrum the simulation has been performed following the receipe described in the main text. Figure~\ref{fig:mc_comp}
shows a comparisons between simulation (light blue) and calibration data (dark blue), countour lines of equal densities are compared in Figure~(a), 
while Figures~(b), (c) and (d) shows cS1 projected distributions for different ranges in cS2.

### 2017-03-16 Inelastic/analysis.tex
Added appendix and rho correction

@@
 The energy resolution at 39.6\,keV in cS1 and cS2 has been measured to be 15.8\% and 14.7\%, respectively, and is used to extract the standard 
-deviations $\sigma_{cs1}$, $\sigma_{cs2}$.  The correlation parameter is assumed to be independent of energy (at least in the considered narrow energy range) and measured
+deviations $\sigma_{cs1}$, $\sigma_{cs2}$.  The correlation parameter is measured
 using the 164\,keV line from the decay of the $^{131m}$Xe isomer ($T_{1/2}$=11.8\,d) produced during the  $^{241}$AmBe run. This $\gamma$-line is chosen since, unlike the 39.6\,keV line, 
 it is not associated with a NR and a measure of the (cS1,cS2) correlation of a pure ER interaction is possible. The correlation coefficient however depends on energy due to 
-recombination effects, its measured value at 164\,keV is then corrected based on the NEST expected recombination fractions for those energies. 
+electron recombination effects, its measured value at 164\,keV is then corrected based on the NEST expected recombination fractions for those energies. 
 The corrected correlation coefficient is then $\rho \, = \, -0.4 \pm 0.1$.

### 2017-03-16 Inelastic/appendix.tex
typo fixed

@@
 	\caption{A simulation of the 39.6\,keV  xenon line activated from $^{243}$AmBe neutrons is compared with the actual data.
-		 Figure~(a) compare counturs of equal density in the (cS1,cS2)-plane, while Figures~(b), (c) and (d) shows the same distribution projected in cS1 for
+		 Figure~(a) compare contours of equal density in the (cS1,cS2)-plane, while Figures~(b), (c) and (d) shows the same distribution projected in cS1 for
 		 several ranges of cS2, the histograms are normalized to unit area. Light and dark blue represent simulation and data, respectively.
@@
 The procedure, described in detail in section~\ref{sec:signal}, take advantage of several 
-assumptions and approximations which have been validated extesively. 
+assumptions and approximations which have been validated extensively. 
 The main cross check was to reproduce with simulation the 39.6\,keV xenon line activated from $^{124}$AmBe neutrons. 
@@
 we take into account detector response and the non-uniform spatial distribution. Acceptance of analysis selections to this type of interaction 
-have been recomputed accordingly, in particular, acceptance to the double scatter cut differ greatly between neutrons and WIMPs scatterings. 
-Except for acceptances and NR energy spectrum the simulation has been performed following the receipe described in the main text. Figure~\ref{fig:mc_comp}
-shows a comparisons between simulation (light blue) and calibration data (dark blue), countour lines of equal densities are compared in Figure~(a), 
+have been recomputed accordingly, in particular, acceptance to the double scatter cut differ greatly between neutrons and WIMPs scattering. 
+Except for acceptances and NR energy spectrum the simulation has been performed following the receipt described in the main text. Figure~\ref{fig:mc_comp}
+shows a comparisons between simulation (light blue) and calibration data (dark blue), contour lines of equal densities are compared in Figure~(a), 
 while Figures~(b), (c) and (d) shows cS1 projected distributions for different ranges in cS2.

### 2017-03-19 Inelastic/appendix.tex
after Laura's comments on appendix

@@
 	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice3.png}}
-	\caption{A simulation of the 39.6\,keV  xenon line activated from $^{243}$AmBe neutrons is compared with the actual data.
-		 Figure~(a) compare contours of equal density in the (cS1,cS2)-plane, while Figures~(b), (c) and (d) shows the same distribution projected in cS1 for
+	\caption{A simulation of the 39.6\,keV  xenon line activated from $^{243}$AmBe neutrons is compared with  data.
+		 Figure~(a) compares contours of equal density in the (cS1,cS2)-plane, while Figures~(b), (c) and (d) show the same distribution projected in cS1 for
 		 several ranges of cS2, the histograms are normalized to unit area. Light and dark blue represent simulation and data, respectively.
@@
 The detector response to inelastic WIMP-$^{129}$Xe interactions was simulated using an empirical signal model. 
-The procedure, described in detail in section~\ref{sec:signal}, take advantage of several 
-assumptions and approximations which have been validated extensively. 
-The main cross check was to reproduce with simulation the 39.6\,keV xenon line activated from $^{124}$AmBe neutrons. 
+The procedure, described in detail in section~\ref{sec:signal}, takes advantage of several 
+approximations that have been validated extensively. 
+The main aim of the cross check was to reproduce the 39.6\,keV xenon line activated from $^{124}$AmBe neutrons with simulation.
 For this purpose the NR energy spectrum expected from inelastic neutron-$^{129}$Xe scattering has been obtained via  Monte Carlo techniques, 
-we take into account detector response and the non-uniform spatial distribution. Acceptance of analysis selections to this type of interaction 
-have been recomputed accordingly, in particular, acceptance to the double scatter cut differ greatly between neutrons and WIMPs scattering. 
-Except for acceptances and NR energy spectrum the simulation has been performed following the receipt described in the main text. Figure~\ref{fig:mc_comp}
+where we take into account the  detector response and the non-uniform spatial distribution. The Acceptance of analysis selections to this type of interaction 
+have been recomputed, in particular, the acceptance to the double scatter cut differs greatly between neutrons and WIMPs scattering. 
+Except for acceptances and NR energy spectrum the simulation has been performed following the recipe described in the main text. Figure~\ref{fig:mc_comp}
 shows a comparisons between simulation (light blue) and calibration data (dark blue), contour lines of equal densities are compared in Figure~(a), 
-while Figures~(b), (c) and (d) shows cS1 projected distributions for different ranges in cS2.
+while Figures~(b), (c) and (d) show the cS1 projected distributions for different ranges in cS2.

### 2017-04-03 Inelastic/analysis.tex
added Rafael comments + figures edits

@@
+\begin{figure*}[t!]
+	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/wimp_in_sr.png}}
+	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/bkg_in_sr.png}}
+	\caption{Signal (1-9) and control (CR1 and CR2) regions for the inelastic WIMP-$^{129}$Xe search in the (cS2,cS1)-plane.
+		Figure (a) shows the signal distribution for a simulated WIMP of mass 100\,GeV/c$^2$ normalized to 50\,events, while Figure (b) is obtained using  
+		normalized $^{60}$Co calibration data and represents the background expectation distribution.}
+  \label{fig:SR}
+\end{figure*}
+
 \section{Data Analysis}
@@
 
-\begin{figure*}[t!]
-	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/wimp_in_sr.png}}
-	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/bkg_in_sr.png}}
-	\caption{Signal (1-9) and control (CR1 and CR2) regions for the inelastic WIMP-$^{129}$Xe interaction in the (cS2,cS1)-plane.
-		Figure (a) shows the signal distribution for a simulated WIMP of mass 100\,GeV/c$^2$ normalized to 50\,events, while Figure (b) is obtained using  
-		normalized $^{60}$Co calibration data and represents the background expectation distribution.}
-  \label{fig:SR}
-\end{figure*}
-
 \subsection{Signal Correction}
@@
 The non-uniform scintillation light collection by the PMT arrays, due to solid angle effects, Rayleigh scattering length, reflectivity, transmission of the electrodes, etc, lead to a position-dependent S1 signal.
-The warping of the top meshes (inducing a variation in the width of the gas gap between the anode and the liquid-gas interface), the absorption of electrons by residual impurities as they drift towards the gas region, as well as solid angle effects lead to a position-dependent S2 signal.
+The warping of the top meshes (inducing a variation in the width of the gas gap between the anode and the liquid-gas interface), the absorption of electrons by residual impurities as they drift towards the gas region, as well as solid angle effects, lead to a position-dependent S2 signal.
 These signals are thus corrected in 3 dimensions, using various calibration data, as detailed in~\cite{Aprile:2011dd,Aprile:2012vw}, with the corrected quantities denoted as cS1 and cS2, defined in~\cite{Aprile:2012vw}.
@@
 
-As explained in Section~\ref{sec:intro}, the inelastic scattering of a WIMP with a $^{129}$Xe nucleus is expected to produce an energy deposit via a NR with the subsequent emission of  
+The inelastic scattering of a WIMP with a $^{129}$Xe nucleus is expected to produce an energy deposit via a NR with the subsequent emission of  
 a 39.6\,keV de-excitation photon. The largest fraction of the energy released in the event is via the ER, due to the emitted photon which loses its energy in the LXe.
@@
 The region of interest (ROI) selected for this analysis surrounds the 39.6\,keV xenon line in the (cS1,cS2)-plane 
-and is based on $^{241}$AmBe calibration data.
-The ROI extends from 60 to 210\,PE in cS1 and from 4$\times \, 10^3$ to 16$\times \, 10^3$\,PE in cS2, furthermore it is divided  into sub-regions, as shown in Figure~\ref{fig:SR}.
+and is based on $^{241}$AmBe calibration data, where such inelastic scatters are induced by fast neutrons.
+The ROI extends from 60 to 210\,PE in cS1, from 4$\times \, 10^3$ to 16$\times \, 10^3$\,PE in cS2 and is further divided  into sub-regions as shown in Figure~\ref{fig:SR}.
 These sub-regions were defined to  contain a (roughly) similar number of expected background events in each region.
@@
 active LXe shield, selection of single-scatter events and of a predefined fiducial volume of 34\,kg.  
-Our analysis closely follows the event selection criteria described in detail in \cite{Aprile:2012vw} for Run-II, with the few exceptions described below. 
-The cut on the width of the S2 signal as a function of drift time (where the maximal drift time is 176\,$\mu$s and the width values range from $\sim$1-2\,$\mu$s) has been optimized on a sample of events selected from the 39.6\,keV line and set to a 95\% acceptance on these.
+Our analysis closely follows the event selection criteria described in detail in \cite{Aprile:2012vw} for Run-II, with the following few exceptions. 
+The cut on the width of the S2 signal as a function of drift time (where the maximal drift time is 176\,$\mu$s and the width values range from $\sim$1-2\,$\mu$s) has been optimized on a sample of events selected from the 39.6\,keV line and set to a 95\% acceptance of these.
 This cut ensures that the broadening of S2-signals due to diffusion is consistent with the $z$-position calculated from the observed time difference between the S1 and S2 signals.
@@
 The same model is used to predict the charge yield at 39.6\,keV, which is then scaled according to the detector's secondary scintillation gain $Y$. 
- The latter is determined from detector's response to single electrons~\cite{SingleE}.
+ The latter is determined from the detector's response to single electrons~\cite{SingleE}.
 The energy resolution at 39.6\,keV in cS1 and cS2 has been measured to be 15.8\% and 14.7\%, respectively, and is used to extract the standard 
 deviations $\sigma_{cs1}$, $\sigma_{cs2}$.  The correlation parameter is measured
-using the 164\,keV line from the decay of the $^{131m}$Xe isomer ($T_{1/2}$=11.8\,d) produced during the  $^{241}$AmBe run. This $\gamma$-line is chosen since, unlike the 39.6\,keV line, 
+using the 164\,keV line from the decay of the $^{131m}$Xe isomer ($T_{1/2}$=11.8\,d) produced during the  $^{241}$AmBe calibration. This $\gamma$-line is chosen since, unlike the 39.6\,keV line, 
 it is not associated with a NR and a measure of the (cS1,cS2) correlation of a pure ER interaction is possible. The correlation coefficient however depends on energy due to 
-electron recombination effects, its measured value at 164\,keV is then corrected based on the NEST expected recombination fractions for those energies. 
+electron recombination effects. Its measured value at 164\,keV is thus corrected based on the NEST expected recombination fractions for those energies. 
 The corrected correlation coefficient is then $\rho \, = \, -0.4 \pm 0.1$.
@@
 The cS1 and cS2 distributions from the NR contribution are predicted starting from the expected nuclear recoil energy spectrum
-of WIMP inelastic interactions~\cite{Baudis:2013bba}. The average cS1 and cS2 are given by equations~\ref{f:cs1} and~\ref{f:cs2} respectively,
-where $\mathcal{L}_{eff}$ is the liquid xenon scintillation efficiency for NRs relative to 122\,keVee, while $S_{ee} \, = \, 0.58$  and $S_{nr} \, = \, 0.95$ describe the scintillation 
-quenching due to the electric field of ER and NRs, respectively~\cite{ScintQuenching}. The parameterization and uncertainties of $\mathcal{L}_{eff}$ as a function of nuclear
-recoil energy $E_{nr}$ are based on existing direct measurements \cite{run8Result}.
-The light yield for 122\,keV ERs is taken from the same NEST model fit as described above.
-For cS2, the parameterization
-of $Q_{Y}(E_{nr})$ is taken from \cite{QY}. Finally, all detector related resolution effects are introduced following the prescriptions described in \cite{Aprile:2012vw}.
-
+of WIMP inelastic interactions~\cite{Baudis:2013bba}. The average cS1 and cS2 are given by equations~\ref{f:cs1} and~\ref{f:cs2} respectively:
 \begin{equation}
-cS1_{nr} ~=~ E_{nr} \, \mathcal{L}_{eff}(E_{nr}) \, L_{y} \, \frac{S_{nr}}{S_{ee}}
+cS1_{nr} ~=~ E_{nr} \, \mathcal{L}_{\text{eff}}(E_{nr}) \, L_{y} \, \frac{S_{nr}}{S_{ee}}
 \label{f:cs1}
@@
 \end{equation}
+where $\mathcal{L}_{\text{eff}}$ is the liquid xenon scintillation efficiency for NRs relative to 122\,keVee, while $S_{ee} \, = \, 0.58$  and $S_{nr} \, = \, 0.95$ describe the scintillation 
+quenching due to the electric field of ER and NRs, respectively~\cite{ScintQuenching}. The parameterization and uncertainties of $\mathcal{L}_{\text{eff}}$ as a function of nuclear
+recoil energy $E_{nr}$ are based on existing direct measurements \cite{run8Result}.
+The light yield for 122\,keV ERs is taken from the same NEST model fit as described above.
+For cS2, the parameterization
+of $Q_{Y}(E_{nr})$ is taken from \cite{QY}. Finally, all detector related resolution effects are introduced following the prescriptions described in \cite{Aprile:2012vw}.
 
@@
 A 2D (cS1 versus cS2) acceptance map is applied to the signal pdf to reproduce data selection effects. Acceptances are computed separately for each selection 
-criteria using the $^{241}$AmBe calibration sample. Acceptances of other selections such as the liquid xenon veto cut, and the single-scatter interaction represent an exception  and 
-a dedicated computation has been performed in these cases. The combined acceptance  of all selection criteria in the region of interest averages to $\sim$$(0.80\pm0.05)$. 
+criteria using the $^{241}$AmBe calibration sample. Acceptances of other selections such as the liquid xenon veto cut, and the single-scatter interaction, represent an exception  for which  
+a dedicated computation has been performed. The combined acceptance  of all selection criteria in the region of interest averages to $\sim$$(0.80\pm0.05)$. 
 Figure~\ref{fig:SR}\,(a) shows an example of fully simulated signal model for a WIMP mass of 100\,GeV/c$^2$.
@@
 The signal simulation procedure has been validated by reproducing the 39.6\,keV xenon line from interactions due to neutrons from the 
-$^{124}$AmBe source and compared to data. The simulated events were in agreement  with calibration data within statistical uncertainties, 
-more detail on this validation campaign are reported in the appendix. 
+$^{124}$AmBe source and compared to data. The simulated events were in agreement  with calibration data within statistical uncertainties. 
+More detail on this validation campaign are reported in the appendix. 
 %%%%%% DEPENDS on the journal  %%%%%
@@
 
-The background in the region of interest for inelastic scattering is dominated by ERs and due to the residual radioactivity of detector materials, to $^{85}$Kr present in the liquid xenon as well as due to $^{222}$Rn decays in the liquid~\cite{Aprile:2011vb}.
+The background in the region of interest for inelastic scattering is dominated by ERs and due to the residual radioactivity of detector materials, to $^{85}$Kr present in the liquid xenon, as well as due to $^{222}$Rn decays in the liquid~\cite{Aprile:2011vb}.
 The background contribution from inelastic scatters of radiogenic or cosmogenic neutrons (producing a 39.6\,keV de-excitation line) is negligible thanks to the very low expected neutron scattering rate in the detector~\cite{Aprile:2013tov}.
@@
 in the (cS1,cS2)-plane. The calibration sample yields  about $2.2\times10^4$ events in the ROI; these are then scaled to the science data according to a measured scale 
-factor $\tau_{bkg}$.
+factor $\tau_{\text{bkg}}$.
 This scale factor, which is merely the ratio between the data and calibration sample yields, is measured in the two control regions shown in Figure~\ref{fig:SR} (labelled CR1 and CR2) separately.
-The two control regions give compatible results and the computed average is $\tau_{bkg} \, =  \, 0.034 \pm 0.002 $, where the reported uncertainty
+The two control regions give compatible results and the computed average is $\tau_{\text{bkg}} \, =  \, 0.034 \pm 0.002 $, where the reported uncertainty
 is of statistical nature only.
@@
 Uncertainties on the  prediction of the total number of background events arise from the uncertainty on the measurement of the normalisation 
-factor, $\tau_{bkg}$, and amount to 6\%. % contribution of radiogenic neutrons are neglected. 
+factor, $\tau_{\text{bkg}}$, and amount to 6\%. % contribution of radiogenic neutrons are neglected. 
 Systematic uncertainty on the shape of the predicted background distribution are assessed by the maximal observed discrepancy in the ROI between
-the $^{60}$Co and $^{232}$Th calibration samples, the two samples normalized yield are compared in each sub-region and the largest deviation (incompatible
+the $^{60}$Co and $^{232}$Th calibration samples. The two sample's normalized yield are compared in each sub-region and the overall largest deviation (incompatible
 with statistical fluctuation) is found to be within 4\%.  A  systematic uncertainty of 4\% is then assigned  to the expected yield of each sub-region.
@@
 
-Uncertainties on the total yield of signal events arising from selections acceptance uncertainties are found to be very weakly dependent on 
+Uncertainties on the total yield of signal events arising from selections are found to be only very weakly dependent on 
 the WIMP mass, and an overall 6\% acceptance uncertainty is applied to all WIMP hypotheses.
@@
 Uncertainties on the energy scale and, more generally, related to detector responses  are parameterised 
-using the respective uncertainties on the measures of $L_y$, $\mathcal{L}_{eff}$, $Y$, $Q_Y$ and $\rho$. The simulation shows 
+using the respective uncertainties on the measures of $L_y$, $\mathcal{L}_{\text{eff}}$, $Y$, $Q_Y$ and $\rho$. The simulation shows 
 that these uncertainties mainly affect the pdf of the signal model in the ROI, and very weakly the total signal yield. 

### 2017-04-03 Inelastic/appendix.tex
added Rafael comments + figures edits

@@
 
-\begin{figure*}[h!]
+\begin{figure*}[tbh!]
 	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_contour.png}}
-	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice1.png}} \\
-	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice2.png}}
-	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice3.png}}
+	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/test_projections.png}} 
+%	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice1.png}} \\
+%	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice2.png}}
+%	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice3.png}}
 	\caption{A simulation of the 39.6\,keV  xenon line activated from $^{243}$AmBe neutrons is compared with  data.
-		 Figure~(a) compares contours of equal density in the (cS1,cS2)-plane, while Figures~(b), (c) and (d) show the same distribution projected in cS1 for
+		 Figure~(a) compares contours of equal density in the (cS1,cS2)-plane, while Figure~(b) shows the same distribution projected in cS1 for
 		 several ranges of cS2, the histograms are normalized to unit area. Light and dark blue represent simulation and data, respectively.
@@
 where we take into account the  detector response and the non-uniform spatial distribution. The Acceptance of analysis selections to this type of interaction 
-have been recomputed, in particular, the acceptance to the double scatter cut differs greatly between neutrons and WIMPs scattering. 
-Except for acceptances and NR energy spectrum the simulation has been performed following the recipe described in the main text. Figure~\ref{fig:mc_comp}
+have been recomputed. In particular, the acceptance to the double scatter cut differs greatly between neutrons and WIMPs scattering. 
+Except for acceptances and NR energy spectrum, the simulation has been performed following the recipe described in the main text. Figure~\ref{fig:mc_comp}
 shows a comparisons between simulation (light blue) and calibration data (dark blue), contour lines of equal densities are compared in Figure~(a), 
-while Figures~(b), (c) and (d) show the cS1 projected distributions for different ranges in cS2.
+while Figure~(b) shows the cS1 projected distributions for different ranges in cS2. These considerations thus validate our analysis.
+
+\newpage

### 2017-04-03 Inelastic/inelastic_main.tex
Added appendix and rho correction
added Rafael comments + figures edits

@@
 
-\title{Search for WIMP Inelastic Scattering Off Xenon Nuclei With XENON100 Data}% Force line breaks with \\
+\title{Search for WIMP Inelastic Scattering Off Xenon Nuclei With XENON100}% Force line breaks with \\
 
@@
 XENON100 is a dual-phase xenon time projection chamber with 62\,kg of active mass, operated at the Laboratori Nazionali del Gran Sasso (LNGS) in Italy and designed to search for nuclear recoils from WIMP-nucleus interactions.
-Here we explore inelastic scattering, where a transition to a low-lying excited nuclear state of $^{129}$Xe is induced, with the experimental signature being a nuclear recoil observed together with the prompt de-excitation photon.
-We see no evidence for such inelastic WIMP-$^{129}$Xe interactions, and a profile likelihood analysis allows us to set a 90\% C.L.
+Here we explore inelastic scattering, where a transition to a low-lying excited nuclear state of $^{129}$Xe is induced.
+The experimental signature is a nuclear recoil observed together with the prompt de-excitation photon.
+We see no evidence for such inelastic WIMP-$^{129}$Xe interactions.
+A profile likelihood analysis allows us to set a 90\% C.L.
 upper limit on the inelastic, spin-dependent WIMP-nucleon cross section of $3.3 \times 10^{-38}$\,cm$^{2}$  at 100\,GeV/c$^2$.
@@
 
+\input{appendix}
+
 \bibliography{inelastic_main} 
@@
 %\printbibliography
+
 \end{document}

### 2017-04-03 Inelastic/intro.tex
added Rafael comments + figures edits

@@
 Most direct detection searches focus on elastic scattering of galactic dark matter particles off nuclei, where the keV-scale 
-nuclear recoil energy is to be detected~\cite{Baudis:2012ig,Undagoitia:2015gya,Baudis:2015mpa}. In this work, the 
+nuclear recoil energy is to be detected~\cite{Undagoitia:2015gya,Baudis:2015mpa}. In this work, the 
 alternative process of inelastic scattering is explored, where a WIMP-nucleus scattering induces a transition to a low-lying 
@@
 The signatures and structure functions for inelastic scattering in xenon have been studied in detail in~\cite{Baudis:2013bba}.
-It was found that this channel is complementary to spin-dependent, elastic scattering, and that it dominates the integrated rates above $\simeq10$\,keV energy depositions.
+It was found that this channel is complementary to spin-dependent, elastic scattering, and that it dominates the integrated rates above $\simeq10$\,keV of deposited energy.
 In addition, in case of a positive signal, the observation of inelastic scattering would provide a clear 
@@
 in an electric field of 530\,V/cm and extracted into the gas phase by a stronger field of $\sim$ 12\,kV/cm, where the proportional scintillation, or electroluminiscence, 
-take place.
+takes place.
 The horizontal position, $(x,y)$, of the interaction site is reconstructed from the position of the S2 shower, while the depth of the interaction, $z$, is given by the drift time measurement.
@@
 The TPC thus yields a three-dimensional event localization, with an $(x,y)$ resolution of $<$3\,mm (1\,$\sigma$), and a $z$ resolution of  $<$0.3\,mm (1\,$\sigma$), enabling to reject the majority of background events via fiducial volume selections~\cite{Aprile:2011dd}.
-The ratio S2/S1 provides the basis for distinguishing between nuclear recoils (NRs), as induced by fast neutrons and expected from elastic WIMP-nucleus scatters, and electronic recoils (ERs) produced by $\beta$ and $\gamma$-rays.
+The ratio S2/S1 provides the basis for distinguishing between nuclear recoils (NRs), as induced by fast neutrons and expected from elastic WIMP-nucleus scatters, and electronic recoils (ERs) produced by $\beta$- and $\gamma$-rays.
 A 4\,cm thick liquid xenon (LXe) layer surrounds the TPC and is monitored by 64 1-inch square PMTs, providing an effective active veto for further background reduction.

### 2017-04-03 Inelastic/results.tex
Added appendix and rho correction
added Rafael comments + figures edits

@@
 
-\begin{figure}[t!]
+\begin{figure}[t]
   \includegraphics[width=\linewidth]{images/data_vs_bkg.png}
@@
 
+\begin{figure}[t]
+  \includegraphics[width=\linewidth]{images/limit_reb.png}
+  \caption{Upper limit (blue curve) on the spin-dependent, inelastic WIMP-nucleon cross section as a function of WIMP mass.  
+	  %The expected median sensitivity (dashed curve) along with 
+	  The expected one (light shaded area) and two (dark shaded area) standard deviation uncertainty is also shown. 
+	  This result is compared to the upper limit (at 90\% C.L.) obtained by the XMASS experiment (dashed line)~\cite{Uchida:2014cnn}.}
+  \label{fig:limits}
+\end{figure}
+
 This result is interpreted via a binned profiled likelihood approach by means of the test statistic $\tilde{q}$
@@
 Assuming  an isothermal WIMP halo with a local density of $\rho_{\chi} \, = \, 0.3$\,GeV/cm$^3$, a local circular velocity of $v_0 \,= \, 220$\,km/s, 
-a galactic escape velocity of $v_{\rm{esc}} \, = \, 544$\,km/s 
-and the nuclear structure factors as computed in~\cite{Baudis:2013qla}, 
+a galactic escape velocity of $v_{\rm{esc}} \, = \, 544$\,km/s~\cite{Smith:2006ym}  
+and the nuclear structure factors as computed in~\cite{Baudis:2013bba}, 
 a 90\% CL$_s$~\cite{cls} confidence level upper limit is set on the spin-dependent inelastic WIMP-nucleon cross section as a function of the WIMP mass. 
@@
 
-\begin{figure}[th]
-  \includegraphics[width=\linewidth]{images/limit_reb.png}
-  \caption{Upper limit (blue curve) on the spin-dependent, inelastic WIMP-nucleon cross section as a function of WIMP mass.  
-	  %The expected median sensitivity (dashed curve) along with 
-	  The expected one (light shaded area) and two ( dark shaded area) standard deviation uncertainty is also shown. 
-	  This result is compared to the upper limit (at 90\% C.L.) obtained by the XMASS experiment (red curve)~\cite{Uchida:2014cnn}.}
-  \label{fig:limits}
-\end{figure}
-
 Our result is shown in Figure~\ref{fig:limits}, together with its expected one and two sigma statistical variation.
-The most constraining limit is  set for for a WIMP of mass 100\,GeV/c$^2$ to a cross section of $3.3 \times 10^{-38}$\,cm$^{2}$ (at 90\% CL$_s$ confidence level).
+The most constraining limit is  set for a WIMP of mass 100\,GeV/c$^2$ to a cross section of $3.3 \times 10^{-38}$\,cm$^{2}$ (at 90\% CL$_s$ confidence level).
 
@@
 The discovery of this interaction channel would be a clear signature for a spin-dependent nature of the dark matter interaction, and would provide a potential handle  to constrain the WIMP mass with data from one experiment only~\cite{Baudis:2013bba,McCabe:2016aof}.
-
-\newpage

### 2017-04-24 Inelastic/analysis.tex
add all comments, final version

@@
 \label{sec:signal}
+
+\begin{figure*}[t!]
+	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_contour.png}}
+	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/test_projections.png}} 
+%	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice1.png}} \\
+%	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice2.png}}
+%	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice3.png}}
+	\caption{A simulation of the 39.6\,keV  xenon line activated from $^{241}$AmBe neutrons is compared with  data.
+		 Figure~(a) compares contours of equal density in the (cS1,cS2)-plane, while Figure~(b) shows the same distribution projected in cS1 for
+		 several ranges of cS2, the histograms are normalized to unit area. Light and dark blue represent simulation and data, respectively.
+		}
+
+  \label{fig:mc_comp}
+\end{figure*}
 
@@
 a dedicated computation has been performed. The combined acceptance  of all selection criteria in the region of interest averages to $\sim$$(0.80\pm0.05)$. 
-Figure~\ref{fig:SR}\,(a) shows an example of fully simulated signal model for a WIMP mass of 100\,GeV/c$^2$.
+Figure~\ref{fig:SR}\,(a) shows an example of fully simulated signal model for a WIMP mass of 100\,GeV/c$^2$, normalized to 50 events.
 
-The signal simulation procedure has been validated by reproducing the 39.6\,keV xenon line from interactions due to neutrons from the 
-$^{124}$AmBe source and compared to data. The simulated events were in agreement  with calibration data within statistical uncertainties. 
-More detail on this validation campaign are reported in the appendix. 
+\input{appendix} 
+%The signal simulation procedure has been validated by reproducing the 39.6\,keV xenon line from interactions due to neutrons from the 
+%$^{241}$AmBe source and compared to data. The simulated events were in agreement  with calibration data within statistical uncertainties. 
+%More detail on this validation campaign are reported in the appendix. 
 %%%%%% DEPENDS on the journal  %%%%%
@@
 and agreement was found within statistical uncertainties. Furthermore, $^{60}$Co calibration data have been compared in the region of interest to  
-data from the $^{232}$Th calibration campaign, and the largest deviation between the two shapes is within 4\%. 
+data from the $^{232}$Th calibration campaign, and systematic uncertainties assessed based on it.
 %%%%% Said later anyway, propose to remove it here %%%%%
@@
   \caption{Predicted signal yield in each sub-region (blue curve), along with statistical and systematic uncertainties (shaded area) simulated for a WIMP mass of 100\,GeV/c$^2$.
-The signal has been scaled for a total number of 50 events.}
+The signal has been scaled for a total number of 50 events.
+The sub-regions are defined in Figure~\ref{fig:SR}.}
   \label{fig:unc}
@@
 the $^{60}$Co and $^{232}$Th calibration samples. The two sample's normalized yield are compared in each sub-region and the overall largest deviation (incompatible
-with statistical fluctuation) is found to be within 4\%.  A  systematic uncertainty of 4\% is then assigned  to the expected yield of each sub-region.
+with statistical fluctuation) is found to be within 4\%.  Consequently, a systematic uncertainty of 4\% is assigned  to the expected yield of each sub-region.
 Uncertainties belonging to different sub-regions in the ROI are considered independent from one another.

### 2017-04-24 Inelastic/appendix.tex
add all comments, final version

@@
-\appendix*
+%\appendix*
 
-\section{}
-
-\begin{figure*}[tbh!]
-	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_contour.png}}
-	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/test_projections.png}} 
-%	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice1.png}} \\
-%	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice2.png}}
-%	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice3.png}}
-	\caption{A simulation of the 39.6\,keV  xenon line activated from $^{243}$AmBe neutrons is compared with  data.
-		 Figure~(a) compares contours of equal density in the (cS1,cS2)-plane, while Figure~(b) shows the same distribution projected in cS1 for
-		 several ranges of cS2, the histograms are normalized to unit area. Light and dark blue represent simulation and data, respectively.
-		}
-
-  \label{fig:mc_comp}
-\end{figure*}
+\subsection{Signal Validation}
 
@@
 approximations that have been validated extensively. 
-The main aim of the cross check was to reproduce the 39.6\,keV xenon line activated from $^{124}$AmBe neutrons with simulation.
+The main aim of the cross check was to reproduce the 39.6\,keV xenon line activated from $^{241}$AmBe neutrons with simulation.
 For this purpose the NR energy spectrum expected from inelastic neutron-$^{129}$Xe scattering has been obtained via  Monte Carlo techniques, 
-where we take into account the  detector response and the non-uniform spatial distribution. The Acceptance of analysis selections to this type of interaction 
+where we take into account the  detector response and the non-uniform spatial distribution. The acceptance of analysis selections to this type of interaction 
 have been recomputed. In particular, the acceptance to the double scatter cut differs greatly between neutrons and WIMPs scattering. 
@@
 while Figure~(b) shows the cS1 projected distributions for different ranges in cS2. These considerations thus validate our analysis.
-
-\newpage

### 2017-04-24 Inelastic/inelastic_main.tex
add all comments, final version

@@
 
+\newcommand{\bern}{\affiliation{Albert Einstein Center for Fundamental Physics, University of Bern, 3012 Bern, Switzerland}}
+
+\newcommand{\bologna}{\affiliation{Department of Physics and Astrophysics, University of Bologna and INFN-Bologna, 40126 Bologna, Italy}}
+
+\newcommand{\chicago}{\affiliation{Department of Physics \& Kavli Institute of Cosmological Physics, University of Chicago, Chicago, IL 60637, USA}}
+
+\newcommand{\coimbra}{\affiliation{LIBPhys, Department of Physics, University of Coimbra, 3004-516 Coimbra, Portugal}}
+
+\newcommand{\columbia}{\affiliation{Physics Department, Columbia University, New York, NY 10027, USA}}
+
+\newcommand{\lngs}{\affiliation{INFN-Laboratori Nazionali del Gran Sasso and Gran Sasso Science Institute, 67100 L'Aquila, Italy}}
+
+\newcommand{\mainz}{\affiliation{Institut f\"ur Physik \& Exzellenzcluster PRISMA, Johannes Gutenberg-Universit\"at Mainz, 55099 Mainz, Germany}}
+
+\newcommand{\heidelberg}{\affiliation{Max-Planck-Institut f\"ur Kernphysik, 69117 Heidelberg, Germany}}
+
+\newcommand{\munster}{\affiliation{Institut f\"ur Kernphysik, Westf\"alische Wilhelms-Universit\"at M\"unster, 48149 M\"unster, Germany}}
+
+\newcommand{\nikhef}{\affiliation{Nikhef and the University of Amsterdam, Science Park, 1098XG Amsterdam, Netherlands}}
+
+\newcommand{\nyuad}{\affiliation{New York University Abu Dhabi, Abu Dhabi, United Arab Emirates}}
+
+\newcommand{\purdue}{\affiliation{Department of Physics and Astronomy, Purdue University, West Lafayette, IN 47907, USA}}
+
+\newcommand{\rpi}{\affiliation{Department of Physics, Applied Physics and Astronomy, Rensselaer Polytechnic Institute, Troy, NY 12180, USA}}
+
+\newcommand{\rice}{\affiliation{Department of Physics and Astronomy, Rice University, Houston, TX 77005, USA}}
+
+\newcommand{\stockholm}{\affiliation{Oskar Klein Centre, Department of Physics, Stockholm University, AlbaNova, Stockholm SE-10691, Sweden}}
+
+\newcommand{\subatech}{\affiliation{SUBATECH, IMT Atlantique, CNRS/IN2P3, Universit\'e de Nantes, Nantes 44307, France}}
+
+\newcommand{\torino}{\affiliation{INFN-Torino and Osservatorio Astrofisico di Torino, 10125 Torino, Italy}}
+
+\newcommand{\ucla}{\affiliation{Physics \& Astronomy Department, University of California, Los Angeles, CA 90095, USA}}
+
+\newcommand{\ucsd}{\affiliation{Department of Physics, University of California, San Diego, CA 92093, USA}}
+
+\newcommand{\wis}{\affiliation{Department of Particle Physics and Astrophysics, Weizmann Institute of Science, Rehovot 7610001, Israel}}
+
+\newcommand{\zurich}{\affiliation{Physik-Institut, University of Zurich, 8057  Zurich, Switzerland}}
+
+\newcommand{\paris}{\affiliation{LPNHE, Université Pierre et Marie Curie, Université Paris Diderot, CNRS/IN2P3, Paris 75252, France}}
+
+\newcommand{\freiburg}{\affiliation{Physikalisches Institut, Universität Freiburg, 79104 Freiburg, Germany}}
+
 \begin{document}
@@
 \title{Search for WIMP Inelastic Scattering Off Xenon Nuclei With XENON100}% Force line breaks with \\
+\author{E.~Aprile}\columbia
 
-\collaboration{The XENON100 Collaboration}\noaffiliation
+\author{J.~Aalbers}\nikhef
+
+\author{F.~Agostini}\lngs\bologna
+
+\author{M.~Alfonsi}\mainz
+
+\author{F.~D.~Amaro}\coimbra
+
+\author{M.~Anthony}\columbia
+
+\author{F.~Arneodo}\nyuad
+
+\author{P.~Barrow}\zurich
+
+\author{L.~Baudis}\zurich
+
+\author{B.~Bauermeister}\stockholm
+
+\author{M.~L.~Benabderrahmane}\nyuad
+
+\author{T.~Berger}\rpi
+
+\author{P.~A.~Breur}\nikhef
+
+\author{A.~Brown}\nikhef
+
+\author{E.~Brown}\rpi
+
+\author{S.~Bruenner}\heidelberg
+
+\author{G.~Bruno}\lngs
+
+\author{R.~Budnik}\wis
+
+\author{L.~B\"utikofer}\freiburg\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}
+
+\author{J.~Calv\'en}\stockholm
+
+\author{J.~M.~R.~Cardoso}\coimbra
+
+\author{M.~Cervantes}\purdue
+
+\author{D.~Cichon}\heidelberg
+
+\author{D.~Coderre}\freiburg\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}
+
+\author{A.~P.~Colijn}\nikhef
+
+\author{J.~Conrad}\altaffiliation{Wallenberg Academy Fellow}\stockholm
+
+\author{J.~P.~Cussonneau}\subatech
+
+\author{M.~P.~Decowski}\nikhef
+
+\author{P.~de~Perio}\columbia
+
+\author{P.~Di~Gangi}\bologna
+
+\author{A.~Di~Giovanni}\nyuad
+
+\author{S.~Diglio}\subatech
+
+\author{G.~Eurin}\heidelberg
+
+\author{J.~Fei}\ucsd
+
+\author{A.~D.~Ferella}\stockholm
+
+\author{A.~Fieguth}\munster
+
+\author{W.~Fulgione}\lngs\torino
+
+\author{A.~Gallo Rosso}\lngs
+
+\author{M.~Galloway}\zurich
+
+\author{F.~Gao}\columbia
+
+\author{M.~Garbini}\bologna
+
+\author{C.~Geis}\mainz
+
+\author{L.~W.~Goetzke}\columbia
+
+\author{Z.~Greene}\columbia
+
+\author{C.~Grignon}\mainz
+
+\author{C.~Hasterok}\heidelberg
+
+\author{E.~Hogenbirk}\nikhef
+
+\author{R.~Itay}\wis
+
+\author{B.~Kaminsky}\freiburg\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}
+
+\author{S.~Kazama}\zurich
+
+\author{G.~Kessler}\zurich
+
+\author{A.~Kish}\zurich
+
+\author{H.~Landsman}\wis
+
+\author{R.~F.~Lang}\purdue
+
+\author{D.~Lellouch}\wis
+
+\author{L.~Levinson}\wis
+
+\author{Q.~Lin}\columbia
+
+\author{S.~Lindemann}\heidelberg\freiburg
+
+\author{M.~Lindner}\heidelberg
+
+\author{F.~Lombardi}\ucsd
+
+\author{J.~A.~M.~Lopes}\altaffiliation[Also with ]{Coimbra Engineering Institute, Coimbra, Portugal}\coimbra
+
+\author{A.~Manfredini}\wis
+
+\author{I.~Maris}\nyuad
+
+\author{T.~Marrod\'an~Undagoitia}\heidelberg
+
+\author{J.~Masbou}\subatech
+
+\author{F.~V.~Massoli}\bologna
+
+\author{D.~Masson}\purdue
+
+\author{D.~Mayani}\zurich
+
+\author{M.~Messina}\columbia
+
+\author{K.~Micheneau}\subatech
+
+\author{A.~Molinario}\lngs
+
+\author{K.~Mora}\stockholm
+
+\author{M.~Murra}\munster
+
+\author{J.~Naganoma}\rice
+
+\author{K.~Ni}\ucsd
+
+\author{U.~Oberlack}\mainz
+
+\author{P.~Pakarha}\zurich
+
+\author{B.~Pelssers}\stockholm
+
+\author{R.~Persiani}\subatech
+
+\author{F.~Piastra}\zurich
+
+\author{J.~Pienaar}\purdue
+
+\author{V.~Pizzella}\heidelberg
+
+\author{M.-C.~Piro}\rpi
+
+\author{G.~Plante}\columbia
+
+\author{N.~Priel}\wis
+
+\author{L.~Rauch}\heidelberg
+
+\author{S.~Reichard}\purdue
+
+\author{C.~Reuter}\purdue
+
+\author{A.~Rizzo}\columbia
+
+\author{S.~Rosendahl}\munster
+
+\author{N.~Rupp}\heidelberg
+
+\author{J.~M.~F.~dos~Santos}\coimbra
+
+\author{G.~Sartorelli}\bologna
+
+\author{M.~Scheibelhut}\mainz
+
+\author{S.~Schindler}\mainz
+
+\author{J.~Schreiner}\heidelberg
+
+\author{M.~Schumann}\freiburg
+
+\author{L.~Scotto~Lavina}\paris
+
+\author{M.~Selvi}\bologna
+
+\author{P.~Shagin}\rice
+
+\author{M.~Silva}\coimbra
+
+\author{H.~Simgen}\heidelberg
+
+\author{M.~v.~Sivers}\freiburg\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}
+
+\author{A.~Stein}\ucla
+
+\author{D.~Thers}\subatech
+
+\author{A.~Tiseni}\nikhef
+
+\author{G.~Trinchero}\torino
+
+\author{C.~Tunnell}\nikhef\chicago
+
+\author{M.~Vargas}\munster
+
+\author{H.~Wang}\ucla
+
+\author{Z.~Wang}\lngs
+
+\author{Y.~Wei}\zurich
+
+\author{C.~Weinheimer}\munster
+
+\author{J.~Wulf}\zurich
+
+\author{J.~Ye}\ucsd
+
+\author{Y.~Zhang.}\columbia
+
+\collaboration{XENON Collaboration}\email{xenon@lngs.infn.it}\noaffiliation
 
@@
 
-\input{appendix}
+%\input{appendix}
 

### 2017-04-24 Inelastic/intro.tex
add all comments, final version

@@
 We consider the $^{129}\text{Xe}$ isotope, which has an abundance of 26.4\% in natural xenon, and a lowest-lying 
-3/2$^{+}$ state at 36.6\,keV above the 1/2$^+$ ground state. The electromagnetic nuclear decay has a half-life of 0.97\,ns. 
+3/2$^{+}$ state at 36.9\,keV above the 1/2$^+$ ground state. The electromagnetic nuclear decay has a half-life of 0.97\,ns. 
 The signatures and structure functions for inelastic scattering in xenon have been studied in detail in~\cite{Baudis:2013bba}.
@@
 
-XENON100 has acquired science data between 2008-2015, and has set competitive constraints on spin-independent~\cite{Aprile:2012nq,Aprile:2016swn} 
+XENON100 has acquired science data between 2009-2015, and has set competitive constraints on spin-independent~\cite{Aprile:2012nq,Aprile:2016swn} 
 and spin-dependent~\cite{Aprile:2013doa,Aprile:2016swn} elastic WIMP-nucleus 

### 2017-04-24 Inelastic/results.tex
add all comments, final version

@@
 While these upper limits are not competitive to spin-dependent, elastic scattering results, as obtained by XENON100~\cite{Aprile:2013doa} and LUX~\cite{Akerib:2016lao} 
-(bounding the cross section to be $<\,2 \times 10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/c$^2$ WIMP), 
+(bounding the cross section to be $<\,1 \times 10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/c$^2$ WIMP), 
 %(with a cross section minimum of $\sim2 \times 10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/c$^2$ WIMP), 

### 2017-04-25 Inelastic/inelastic_main.tex
final, after luca's comments

@@
 linenumbers,
+longbibliography,
 %groupedaddress,
@@
 
-%\usepackage[showframe,%Uncomment any one of the following lines to test 
+%\usepackage[%showframe,%Uncomment any one of the following lines to test 
 %%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
@@
 %%margin=1.5in,
-%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
+%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
 %%height=10in,a5paper,hmargin={3cm,0.8in},
+%total={6.5in,8.75in},bottom=1.2in, top=0.5in
 %]{geometry}
@@
 
-\author{L.~Baudis}\zurich
+\author{L.~Baudis}\email[E-mail: ]{lbaudis@physik.uzh.ch}\zurich
 
@@
 
-\author{A.~Manfredini}\wis
+\author{A.~Manfredini}\email[E-mail: ]{alessandro.manfredini@weizmann.ac.il}\wis
 
@@
 
-\collaboration{XENON Collaboration}\email{xenon@lngs.infn.it}\noaffiliation
+\collaboration{XENON Collaboration}\email[E-mail: ]{xenon@lngs.infn.it}\noaffiliation
 
@@
 \bibliography{inelastic_main} 
-\bibliographystyle{unsrt}
+%\bibliographystyle{abbrv}
 %\printbibliography

### 2017-04-25 Inelastic/results.tex
final, after luca's comments

@@
+\begin{figure}[t]
+  \includegraphics[width=\linewidth]{images/data_vs_bkg.png}
+  \caption{Distribution of  observed events  in the region of interest (data points), along with the normalized distribution from calibration data (filled histogram).
+The bottom panel displays the ratio
+between data and expected background, where the light  and dark blue shaded areas represent the statistical and systematic uncertainty 
+on the background expectation, respectively. The expected signal for a WIMP mass of 100\,GeV/c$^2$ (blue dashed), normalized to a total of 50 events, is also shown.}
+  \label{fig:dataVSbkg}
+\end{figure}
+
 \section{Results and Discussion}
@@
 on the background expectation, respectively. The expected signal for a WIMP mass of 100\,GeV/c$^2$, normalized to a total of 50 events, is also shown.
-
-\begin{figure}[t]
-  \includegraphics[width=\linewidth]{images/data_vs_bkg.png}
-  \caption{Distribution of  observed events  in the region of interest (data points), along with the normalized distribution from calibration data (filled histogram).
-The bottom panel displays the ratio
-between data and expected background, where the light  and dark blue shaded areas represent the statistical and systematic uncertainty 
-on the background expectation, respectively. The expected signal for a WIMP mass of 100\,GeV/c$^2$ (blue dashed), normalized to a total of 50 events, is also shown.}
-  \label{fig:dataVSbkg}
-\end{figure}
 
@@
 The discovery of this interaction channel would be a clear signature for a spin-dependent nature of the dark matter interaction, and would provide a potential handle  to constrain the WIMP mass with data from one experiment only~\cite{Baudis:2013bba,McCabe:2016aof}.
+
+\section*{Acknowledgments}
+We gratefully acknowledge support from the National Science Foundation, Swiss National Science Foundation, Deutsche Forschungsgemeinschaft, Max Planck Gesellschaft, German Ministry for Education and Research, Netherlands Organisation for Scientific Research, Weizmann Institute of Science, I-CORE, Initial Training Network Invisibles (Marie Curie Actions, PITNGA-2011-289442), Fundacao para a Ciencia e a Tecnologia, Region des Pays de la Loire, Knut and Alice Wallenberg Foundation, Kavli Foundation, and Istituto Nazionale di Fisica Nucleare.
+We are grateful to Laboratori Nazionali del Gran Sasso for hosting and supporting the XENON project.

### 2017-05-01 Inelastic/analysis.tex
version uploaded to archive

@@
 \begin{figure*}[t!]
-	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/wimp_in_sr.png}}
-	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/bkg_in_sr.png}}
+	\subfigure[]{\includegraphics[width=0.49\linewidth]{wimp_in_sr.png}}
+	\subfigure[]{\includegraphics[width=0.49\linewidth]{bkg_in_sr.png}}
 	\caption{Signal (1-9) and control (CR1 and CR2) regions for the inelastic WIMP-$^{129}$Xe search in the (cS2,cS1)-plane.
@@
 \begin{figure*}[t!]
-	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_contour.png}}
-	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/test_projections.png}} 
+	\subfigure[]{\includegraphics[width=0.49\linewidth]{mc_ambe_comp_contour.png}}
+	\subfigure[]{\includegraphics[width=0.49\linewidth]{test_projections.png}} 
 %	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice1.png}} \\
@@
 \begin{figure}[t!]
-  \includegraphics[width=\linewidth]{images/wimp_sys_unc.png}
+  \includegraphics[width=\linewidth]{wimp_sys_unc.png}
   \caption{Predicted signal yield in each sub-region (blue curve), along with statistical and systematic uncertainties (shaded area) simulated for a WIMP mass of 100\,GeV/c$^2$.

### 2017-05-03 Inelastic/inelastic_main.tex
version to arxiv
version uploaded to archive
revisited author list and typo fix

@@
 superscriptaddress,
-linenumbers,
 longbibliography,
@@
 
-\newcommand{\freiburg}{\affiliation{Physikalisches Institut, Universität Freiburg, 79104 Freiburg, Germany}}
+\newcommand{\freiburg}{\affiliation{Physikalisches Institut, Universit\"at Freiburg, 79104 Freiburg, Germany}}
 
@@
 
-\author{L.~Baudis}\email[E-mail: ]{lbaudis@physik.uzh.ch}\zurich
+\author{L.~Baudis}\email[E-mail: ]{laura.baudis@uzh.ch}\zurich
 
@@
 
-\author{L.~B\"utikofer}\freiburg\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}
+\author{L.~B\"utikofer}\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}\freiburg
 
@@
 
-\author{D.~Coderre}\freiburg\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}
+\author{D.~Coderre}\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}\freiburg
 
@@
 
-\author{B.~Kaminsky}\freiburg\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}
+\author{B.~Kaminsky}\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}\freiburg
 
@@
 
-\author{M.~v.~Sivers}\freiburg\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}
+\author{M.~v.~Sivers}\altaffiliation[]{Also at Albert Einstein Center for Fundamental Physics, University of Bern, Bern, Switzerland}\freiburg
 

### 2017-05-03 Inelastic/intro.tex
revisited author list and typo fix

@@
 We consider the $^{129}\text{Xe}$ isotope, which has an abundance of 26.4\% in natural xenon, and a lowest-lying 
-3/2$^{+}$ state at 36.9\,keV above the 1/2$^+$ ground state. The electromagnetic nuclear decay has a half-life of 0.97\,ns. 
+3/2$^{+}$ state at 39.6\,keV above the 1/2$^+$ ground state. The electromagnetic nuclear decay has a half-life of 0.97\,ns. 
 The signatures and structure functions for inelastic scattering in xenon have been studied in detail in~\cite{Baudis:2013bba}.

### 2017-06-11 Inelastic/response_to_referee.tex
addedd response to referee

\documentclass{article}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usepackage{color}

\begin{document}

\title{ \textbf{ Search for WIMP inelastic scattering off xenon nuclei with XENON100} \\  Response on Referee report -- DE12171/Aprile  }
%\author{}

\maketitle

%\section{Introduction}
%Here is the text of your introduction.

\begin{itemize}
	\item {\em{General: are these new SD limits isospin independent, applying to both protons and neutrons, unlike the traditional elastic SD for dark matter? If so, should be indicated right off the bat in the abstract.}}
\end{itemize}

\begin{itemize}
	\item{ \em{Introduction, third paragraph: Can you add a sentence further
elucidating how it is possible for dark matter, of the masses and
cross-sections you probe in this paper, to fail to be detected through
elastic scattering, given current existing world-best limits from
XENON1T and LUX and PandaX, yet still be possible through inelastic?
It was still unclear to me. Basically, I want to understand if there
was any reasonable scenario under which you could’ve seen a signal, or
whether that was already impossible and you were “doomed” to only set
a limit. This changes the theme of the paper significantly in my mind
from discovery potential to a confirmation/cross-check of an existing
limit in a new channel. - “10 keV of deposited energy”: Does this
refer to nuclear or electron recoil or both? Unclear since we are now
dealing with inelastic scattering that produces a gamma too here.}}
\end{itemize}

\textcolor{red}{ We do explicitly say that this search is not competitive, but complementary, maybe express that better?}
Classical searches for spin dependent elastic scattering have, and will keep to have a 
higher sensitivity with respect to this search for spin dependent inelastic scattering.
However, in case dark matter would be found, this type of search ensures you that the type 
{\color{red} of interaction is spin-dependent, while for classical elastic scattering is much more difficult to tell.}

\begin{itemize}
	\item{ \em{
Section III: Is there a reason the complete 477 live-days cannot be
used for this paper? Wouldn’t this make your constraints even
stronger? Please explain reason}}
\end{itemize}

Yes, the limit would be stronger. However the scope of this paper is 
not to discover dark matter, for which one would use instead SD elastic
scattering channel, but rather explore a different analysis channel.
Doing a combination on three different science runs (each of them having 
different background conditions and acceptances) is very demandig.

\begin{itemize}
	\item \em{
III.B: How were the ROI limits chosen? Text doesn’t say: should
explain, are these +/- some number of sigma relative to the expected
means of the NR and ER in cS1 and cS2 space?}
\end{itemize}

{\color{red} The signal distribution changes according to wimp mass due to the NR component,
we choose the ROI so that it will embrace all the wimp hipothesys at least two 
sigma. Now added to the text.}

\begin{itemize}
	\item \em{
While I understand the sub-regions were chosen to have roughly equal
number of events, it is not very clear to me at all why there are so
many different ones, and why there seems to be no rhyme or reason to
their sizes/shapes. It is also unclear, especially since Figure 1a is
an example of only one mass (100 GeV WIMP) how these regions were
picked to be optimal for any WIMP mass studied, doesn’t seem to be
possible to me. (Lastly, why didn’t you just take equal slices in S1
and S2 and make squares for example?)}
\end{itemize}

It was shown ({\color{red} see figure} ) a non appreciable
difference in sensitivity dividing the region in more than 10 equal sized bins. 
So provided that bins have similar sizes their shape is irrelevant to the sensitivity.
There is a limiting factor tough, we are using asymptotic formulae for distribution of the
test statistic, these formulaes are valid in the assumption of Wilks theorem, so that the number
of events in each bin should "large". In order to not have bins with drammaticly low background, which
happens in case of equally sized bins, we opted for collapsing bins achieving similar background content. 
This reasults in a somewhat arbitrary choise for some region of the ROI, but it does not impact our sensitivity.

\begin{itemize}
	\item \em{
Multiple-scatter cut: While I understand the cut on a second largest
peak, what happens when the peaks from multiple scatters are merged
because they are too close together? Also, the language is slightly
unclear: does “regardless of S2 signal size” mean the primary S2 peak,
or all peaks added together in a given event, counting them all as
“the signal”?}
\end{itemize}

{\color{red} When multiple scatters are closer than few mm the they will be mearged. don't know. }

\begin{itemize}
	\item \em{
Figure 2 caption slightly unclear: I assume the figures include both
the ER and the NR associated with the inelastic scatter, and not just
the former as the text implies. Please correct, to better match up
with explanation below in Section C.}
\end{itemize}

{\color{red} Yes, indeed. Text has been edited. }

\begin{itemize}
	\item \em{
Equation 2: It is not clear where S1 photon detection efficiency gets
folded in here: currently this equation appears to yield photons not
PE (Ly?) Am I reading it incorrectly?}
\end{itemize}

{\color{red} need to check. I forgot.}

\begin{itemize}
	\item \em{
~0.80 +/- 0.05: Given the importance of knowing the final signal
acceptance fraction I don’t understand why this has a “~,” especially
since error bars are provided. Why is this still approximate? It
should not be, unless you meant it changes with WIMP mass, and in that
case a range should be provided, from the min to max masses you
considered.}
\end{itemize}

What we meant is that is approximately constant with the wimp mass.
Values being compatible within uncertainties with 0.80 +- 0.05.

\begin{itemize}
	\item \em{
Section D: seems odd, doesn’t seem to add much beyond C and Figure 2.
If there is no new information here, please remove it, or at reduce
the length of the paragraph to include only those, and merge with C.
Weird to have a section be one short paragraph by itself.}
\end{itemize}

\begin{itemize}
	\item \em{
E: It is not clear to me how 60Co and 232Th calibrations can tell you
the BG in the signal region, given they have different energy
spectra/distributions than BG? Isn’t it better to validate the
simulation for 60Co and 232Th then simulate using NEST for example
events of the same energy distribution as your actual ER BG? In fact,
the BG simulation here seems to contradict the signal simulation in
the earlier section. Why the dichotomy in methods, especially since
the 39.6 keV line was actually present in calibration data, and so
this all seems backwards to me. This could explain your unresolved
systematic in F. you write is outside statistical fluctuation
expectation. (You should have a BG prior from counting the parts of
XENON100 and simulating in Geant4, yes?)}
\end{itemize}

The suggested approach relies on ..., there is no such a proven MC-data
matching for XENON100, meaning we don't have a Geant4 of all radioactive material 
background that produces a spectra that we can fully trust... We opted instead
for a simpler approach, bla bla bla....

\begin{itemize}
	\item \em{
Figure 3: statistical and systematic uncertainties should be denoted
separately as is more standard practice, either splitting them off or
using color coded error bars, as you do later}
\end{itemize}

\begin{itemize}
	\item \em{Pseudo-samples: I am confused as to why these are necessary, doesn’t
the ROOT PLR function allow profiling out over multiple such
systematic uncertainties simultaneously and continuously, and not just
in discrete +/-1-sigma steps? You also should explain whether
parameters are all railed to their plus/minus 1-sigma’s all together
or separately? This could be over-conservative, or swing the other
way, depending on the correlations on these parameters, which I know
for a fact myself can be very tricky: for example, raising a light
yield can be canceled out by lowering light collection efficiency,
each within its respective uncertainties, and not necessarily in
integer multiples of their standard deviations of course. This sounds
to me like what would be done in an “enhanced” cut-and-count-style
analysis, but not in a PLR. Perhaps it is because you did binned and I
am used to using PLR continuous (unbinned)? Can you please clarify,
and justify your choice of binned versus unbinned? This goes back to
my original question about the 9 strange sub-regions: How, a priori,
were they selected, optimized, and validated? How does one choose
one’s bins? Was it blind? Speaking of which, it should be made clear
what was blind or not in the text. I imagine not much since you are
primarily an NR-search experiment and this has ER Bottom of p. 6: How
can all parameters related to systematics be justified as normal, as
opposed to Poisson or skewed-normal in at least some cases? What I
mean is, for example a low-energy NR with a very low expected number
of photons detected is not going to have a symmetric distribution,
since there is no such thing as a negative number of photons. Does not
apply to higher energies, but I thought you have low O(10 keV) from
the NR here too Figure 4: minor comment, but sentences just a bit out
of order. Last sentence should move earlier because it refers to
discussion about the top half of the figure.}
\end{itemize}

{color{red} not really sure what's the issue here, several issues in one question....}
The analysis was not technically blind, since this data region was explored in several 
other studies. The procedure we used was as if it was blind, since we didn't tune cuts on data.

\begin{itemize}
	\item \em{Section IV: Please briefly define in text the difference between CL(s)
and the more common CL, and add a sentence explaining the benefit of
CL(s), or at least a brief reason why it was used instead of CL. Not
all readers may be familiar with Read’s work.}
\end{itemize}

\begin{itemize}
	\item \em{
Figure 5: Was the result constrained, due to large BG
under-fluctuation, to be at -1-sigma-level, as it appears to be in
this figure? If so, this should be stated in the figure caption and/or
text and explained. Also, based on flat regions I see in the 1- and
2-sigma bands in the plot it appears as though the limit was smoothed,
but the bands were not. Both should be left as raw data points, or
both smoothed, please choose, but be consistent (personally I prefer
smooth, but a definite case can be made for discrete connected by
straight lines in log-log in between the individual mass points you
actually run in your PLR; past XENON and LUX and other results vary in
choice of what to do in a case like this). This discrepancy is most
noticeable between 100 and 200 GeV, where the blue bands are extremely
straight, while the limit is curved. Lastly, are there really no other
results to put on this plot? Not even an earlier XENON one? This is
very surprising, but it does underscore the significance of your work
here, as being in nearly virgin territory, and you can say that.}
\end{itemize}

\end{document}

### 2017-06-13 Inelastic/response_to_referee.tex
response to referee, first draft

@@
 \usepackage{color}
+
+\newcommand{\ale}{\color{red}}
 
@@
 
+We thank the referee for his/her's valuable comments, we really think these add a value to the paper. 
+You can find below the answer to the detailed questions, we implemented most of the suggestions in the new version of the paper.
+Below we report each  comment/question in blue and its related answer in black, we specifically state what modifications
+were applied to the paper in each single answer.
+
 \begin{itemize}
-	\item {\em{General: are these new SD limits isospin independent, applying to both protons and neutrons, unlike the traditional elastic SD for dark matter?
-If so, should be indicated right off the bat in the abstract.}}
+	\item {\color{blue} General: are these new SD limits isospin independent, applying to both protons and neutrons, unlike the traditional elastic SD for dark matter?
+If so, should be indicated right off the bat in the abstract.}
 \end{itemize}
 
+Looking at the paper "Signatures of Dark Matter Scattering Inelastically Off Nuclei" seems like he is right,
+and the interaction is isospin independent. {\color{red} please confirm.}, shall we change the abstract then?
+
 \begin{itemize}
-	\item{ \em{Introduction, third paragraph: Can you add a sentence further
+	\item {\color{blue} Introduction, third paragraph: Can you add a sentence further
 elucidating how it is possible for dark matter, of the masses and
@@
 refer to nuclear or electron recoil or both? Unclear since we are now
-dealing with inelastic scattering that produces a gamma too here.}}
+dealing with inelastic scattering that produces a gamma too here.}
 \end{itemize}
 
-\textcolor{red}{ We do explicitly say that this search is not competitive, but complementary, maybe express that better?}
-Classical searches for spin dependent elastic scattering have, and will keep to have a 
-higher sensitivity with respect to this search for spin dependent inelastic scattering.
-However, in case dark matter would be found, this type of search ensures you that the type 
-{\color{red} of interaction is spin-dependent, while for classical elastic scattering is much more difficult to tell.}
+Classical searches for spin dependent elastic scattering have higher sensitivity with respect to this search for spin 
+dependent inelastic scattering. However, in case dark matter would be found, this type of search ensures you that the type 
+of interaction is spin-dependent, while for classical elastic scattering is much more difficult to tell.
+In the text we say that this search is complementary to the standard SD. {\color{red} We modified the text to "It was found that this channel,  although not competitive in terms of sensitivity,  
+is complementary to the spin-dependent, elastic scattering one".} 
+The "10 KeV" of deposited energy referes to both, if one looks at integrated rated above 10KeV NR for elastic scattering 
+finds that is smaller than the integrated rate of  NR+ER for inelastic scattering.
+{\color{red} We think that deposited energy is the correct wording here, since indeed it differs for the two cases.}
 
 \begin{itemize}
-	\item{ \em{
+	\item {\color{blue} 
 Section III: Is there a reason the complete 477 live-days cannot be
 used for this paper? Wouldn’t this make your constraints even
-stronger? Please explain reason}}
+stronger? Please explain reason}
 \end{itemize}
@@
 \begin{itemize}
-	\item \em{
+	\item {\color{blue} 
 III.B: How were the ROI limits chosen? Text doesn’t say: should
@@
 
-{\color{red} The signal distribution changes according to wimp mass due to the NR component,
-we choose the ROI so that it will embrace all the wimp hipothesys at least two 
-sigma. Now added to the text.}
+The signal distribution changes according to wimp mass due to the NR component,
+we choose the ROI so that it will embrace all the wimp hipothesys at least at two 
+sigma. Now added to the text.
 
 \begin{itemize}
-	\item \em{
+	\item {\color{blue} 
 While I understand the sub-regions were chosen to have roughly equal
@@
 
-It was shown ({\color{red} see figure} ) a non appreciable
+\begin{figure}[t!]
+  \centerline{\includegraphics[width=0.7\linewidth]{inelastic_binning_check.png}}
+  \caption{ Sensitivity computed dividing the ROI in different numbers of equally sized bins.
+NOTE: this sensitivity curves where run in a test long ago before the final version, imost of nuissance parameter have different implementation or missing, so they are NOT directly comparable with the final one, altough similar.}
+  \label{fig:binning}
+\end{figure}
+
+If one follows an appropriate binning procedure, then the choice of bins is irrelevant, meaning that 
+the final result should not depend on binning. Furthermore we never said that this particular 
+choice is optimal for all masses.
+
+It was shown, see Figure~\ref{fig:binning}, a non appreciable
 difference in sensitivity dividing the region in more than 10 equal sized bins. 
-So provided that bins have similar sizes their shape is irrelevant to the sensitivity.
-There is a limiting factor tough, we are using asymptotic formulae for distribution of the
+So as soon as one divide the ROI in any number larger than 10 of equally sized bins would get the same result. So why not divide in 40 equally sized bins at this point?  
+There is a limiting factor: we are using asymptotic formulae for distribution of the
 test statistic, these formulaes are valid in the assumption of Wilks theorem, so that the number
-of events in each bin should "large". In order to not have bins with drammaticly low background, which
-happens in case of equally sized bins, we opted for collapsing bins achieving similar background content. 
-This reasults in a somewhat arbitrary choise for some region of the ROI, but it does not impact our sensitivity.
+of events in each bin should be "large". In order to not have bins with drammatically low background, which
+happens in case of equally sized bins, we needed to merge bins and we need to do it in a way to not disrupt sensitivity.
+So we started with a number of equally sized bins (roughly 20 if I remember corretly) and we grouped them achieving similar 
+background density,  in this way the discrimination power is conserved, meaning that the discrimination power will be equal or better than 
+the one using the same number of final bins (in this case 9) but produced in equal sizes.
+Within this prescription, which is very general, the chosed arrangement of bins and shapes is almost arbitrary and
+could have been done in many different ways, however it doesn't matter because following 
+this procedure whatever peculiar binning choice will not  impact  our 
+sensitivity, so we choosed the solution that was technically easier.
+We added to the text that "it has been crosschecked that changing bin choice does not impact sensitivity".
 
 \begin{itemize}
-	\item \em{
+	\item {\color{blue} 
 Multiple-scatter cut: While I understand the cut on a second largest
@@
 
-{\color{red} When multiple scatters are closer than few mm the they will be mearged. don't know. }
+{\color{red} Our detector position resolution is of the order of few mm, multiple scatters S2 that are 
+closer than that will be merged. These in any case are not a problem, since this cut is meant 
+to reduce neutron background, in the standard elastic analysis this turns into a small
+uncertainty in neutron bkg model, but for the energies deposits of this analysis neutron bkg 
+is irrelevant, so we could have even dropped that cut. When we say S2 we mean the primary peak. }
 
 \begin{itemize}
-	\item \em{
+	\item {\color{blue} 
 Figure 2 caption slightly unclear: I assume the figures include both
@@
 
-{\color{red} Yes, indeed. Text has been edited. }
+{\color{red} Changed to "a full simulation (NR and ER response) of the 39,6~KeV xenon line..." }
 
 \begin{itemize}
-	\item \em{
+	\item {\color{blue} 
 Equation 2: It is not clear where S1 photon detection efficiency gets
@@
 
-{\color{red} need to check. I forgot.}
+Ly is the measured light yield in PE/$KeV_{ee}$, so it encapsulate all the position dependence
+and collection efficiencies, as maybe described in more detail in 
+(https://arxiv.org/abs/1207.3458). This notation is common to XENON papers, but it might not be 
+general.
 
 \begin{itemize}
-	\item \em{
+	\item {\color{blue} 
 ~0.80 +/- 0.05: Given the importance of knowing the final signal
-acceptance fraction I don’t understand why this has a “~,” especially
+acceptance fraction I don’t understand why this has a “$\simeq$,” especially
 since error bars are provided. Why is this still approximate? It
@@
 Values being compatible within uncertainties with 0.80 +- 0.05.
+it has been changed to: "The combined acceptance  of all selection criteria in the region 
+of interest is roughly constant for all masses and averages to $(0.80\pm0.05)$."
 
 \begin{itemize}
-	\item \em{
+	\item {\color{blue} 
 Section D: seems odd, doesn’t seem to add much beyond C and Figure 2.
@@
 
+Section D has been merged to section C.
+
 \begin{itemize}
-	\item \em{
+	\item {\color{blue} 
 E: It is not clear to me how 60Co and 232Th calibrations can tell you
@@
 
-The suggested approach relies on ..., there is no such a proven MC-data
-matching for XENON100, meaning we don't have a Geant4 of all radioactive material 
-background that produces a spectra that we can fully trust... We opted instead
-for a simpler approach, bla bla bla....
+It has been proven by several XENON analysis that indeed 60Co and 232Th are very good
+and representative candidate for ER background, since they reproduce quite well the compton
+scattering band. They have been used multiple times in several xenon analysis, see for 
+example (https://arxiv.org/abs/1207.3458, and https://arxiv.org/abs/1609.06154).
+A full simulation with NEST will not give smaller uncertainties due to intrinsic
+NEST uncertainties and due to the MC radiogenic material uncertainty. 
+Furthermore, there is no such a proven MC-data matching for XENON100 for these energies, 
+meaning we don't have a Geant4 of all radioactive material 
+background that produces a spectra that we can fully trust. So we opted for a simple 
+but effective approach. 
+Regarding the "dicotomy of threatment": we could't use AmBe data as signal model due to 
+the non negligible difference between WIMP and AmBe introduced by the NR.
 
 \begin{itemize}
-	\item \em{
+	\item {\color{blue} 
 Figure 3: statistical and systematic uncertainties should be denoted
@@
 
+Done.
+
 \begin{itemize}
-	\item \em{Pseudo-samples: I am confused as to why these are necessary, doesn’t
+	\item {\color{blue} Pseudo-samples: I am confused as to why these are necessary, doesn’t
 the ROOT PLR function allow profiling out over multiple such
@@
 
-{color{red} not really sure what's the issue here, several issues in one question....}
-The analysis was not technically blind, since this data region was explored in several 
+This comment touches many topics and we try to reply in order in the following:
+\begin{enumerate}
+	\item Regarding Pseudo-samples, these are used to produce shape uncertainty, so histogram variation, of +/-1 sigma step.
+What typically one does with these "pseudo-samples" histograms  is to use them as seeds for interpolation techniques controlled by a nuissance parameter, as the referee is suggesting.
+Now we have several such shape uncertainties and we felt that this approach was overcomplicated.
+We opted for a conservative but simple approximation: we sum up in quadrature all the "positive" and "negative" variation for each bin separately, we then assign the maximal of the two as a symmetric Gaussian distributed uncertainty on the single bin.
+In this way we avoid the complication of histogram shape interpolation of several nuissance parameter.
+Being the uncertainty on each bin independent from the other this allows for much more freedom and has overcoverage of the shape variations.
+
+	\item The question on the regions is already answered above.
+
+	\item The analysis was not technically blind, since this data region was explored in several 
 other studies. The procedure we used was as if it was blind, since we didn't tune cuts on data.
 
+	\item All the systematic uncertainties come from auxiliary measurements, so real measurements either from our experiment or in the literature, some of them may not be expected to be gaussian distributed,
+for example Leff, but in these cases the parametrizzation chosen is the one commonly accepted.
+
+	\item The sentences Figure 4 have been swapped.
+\end{enumerate}
+
 \begin{itemize}
-	\item \em{Section IV: Please briefly define in text the difference between CL(s)
+	\item {\color{blue} Section IV: Please briefly define in text the difference between CL(s)
 and the more common CL, and add a sentence explaining the benefit of
@@
 
+The CLs was common practice of XENON100, and common practice of many high energy experimets. 
+This is a technique that target the same problem as power constrain (but in a less silly way),
+it protects the limit by data underfluctiation so that is difficult to exclude
+cross section to which the experiment is not sensitive to, paying the price of a bit worst sensitivity.
+The sentence {\color{red}"The CL$_s$ technique helps protecting against exclusion of a cross section
+smaller than experimental sensitivity" has been added}. Not really sure I wan to add that.
+
 \begin{itemize}
-	\item \em{
+	\item {\color{blue} 
 Figure 5: Was the result constrained, due to large BG
@@
 
+No the limit is not constrained, CLs is used instead of a power constrained limit.
+It just a coincidence that it stops at -1 sigma.
+Yes the bands are not smoothened while the curve is, this is due to a silly ROOT 
+problem which is {\color{red} fixed now} in another way.
+There is no other result that we know of that explores exactly this process.
+
 \end{document}

### 2017-06-13 Inelastic/analysis.tex
response to referee, first draft

@@
 and is based on $^{241}$AmBe calibration data, where such inelastic scatters are induced by fast neutrons.
-The ROI extends from 60 to 210\,PE in cS1, from 4$\times \, 10^3$ to 16$\times \, 10^3$\,PE in cS2 and is further divided  into sub-regions as shown in Figure~\ref{fig:SR}.
-These sub-regions were defined to  contain a (roughly) similar number of expected background events in each region.
+The ROI extends from 60 to 210\,PE in cS1, from 4$\times \, 10^3$ to 16$\times \, 10^3$\,PE in cS2,
+{\ale such that to have at least 95\% acceptance to all signal mass hypothes. The ROI }
+%this
+is further divided  into sub-regions as shown in Figure~\ref{fig:SR}.  These sub-regions were defined to  contain a (roughly) similar number of expected background events in each region, 
+{\ale it was crosschecked that changing binning choice does not impact the sensitivity.} 
 The control regions (denoted as CR1 and CR2 in the figures), are selected to be as close as possible to the ROI,  and are used for cross checks of the background shape distribution.
@@
 %	\subfigure[]{\includegraphics[width=0.49\linewidth]{images/mc_ambe_comp_slice3.png}}
-	\caption{A simulation of the 39.6\,keV  xenon line activated from $^{241}$AmBe neutrons is compared with  data.
+	\caption{A full simulation {\ale (NR and ER response)} of the 39.6\,keV  xenon line activated from $^{241}$AmBe neutrons is compared with  data.
 		 Figure~(a) compares contours of equal density in the (cS1,cS2)-plane, while Figure~(b) shows the same distribution projected in cS1 for
@@
 criteria using the $^{241}$AmBe calibration sample. Acceptances of other selections such as the liquid xenon veto cut, and the single-scatter interaction, represent an exception  for which  
-a dedicated computation has been performed. The combined acceptance  of all selection criteria in the region of interest averages to $\sim$$(0.80\pm0.05)$. 
+a dedicated computation has been performed. The combined acceptance  of all selection criteria in the region %of interest averages to $(0.80\pm0.05)$. 
+{\ale of interest is roughly constant for all masses and averages to $(0.80\pm0.05)$. }
 Figure~\ref{fig:SR}\,(a) shows an example of fully simulated signal model for a WIMP mass of 100\,GeV/c$^2$, normalized to 50 events.
 
-\input{appendix} 
-%The signal simulation procedure has been validated by reproducing the 39.6\,keV xenon line from interactions due to neutrons from the 
-%$^{241}$AmBe source and compared to data. The simulated events were in agreement  with calibration data within statistical uncertainties. 
-%More detail on this validation campaign are reported in the appendix. 
-%%%%%% DEPENDS on the journal  %%%%%
-%{\textcolor{red} {Should we show an example, namely a figure from the signal model note?}}
+{\ale  
+The described signal simulation was validated reproducing the 39.6\,keV xenon line activated from $^{241}$AmBe neutrons and comparing it with data.
+For this purpose the NR energy spectrum expected from inelastic neutron-$^{129}$Xe scattering has been obtained via  Monte Carlo techniques, 
+where we take into account the  detector response and the non-uniform spatial distribution. The acceptance of analysis selections to this type of interaction 
+have been recomputed. In particular, the acceptance to the double scatter cut differs greatly between neutrons and WIMPs scattering. 
+Figure~\ref{fig:mc_comp} shows a comparisons between simulation (light blue) and calibration data (dark blue), contour lines of equal densities are compared in Figure~(a), 
+while Figure~(b) shows the cS1 projected distributions for different ranges in cS2. 
+}
+%see appendix for original version
+%\input{appendix}
 

### 2017-06-13 Inelastic/intro.tex
response to referee, first draft

@@
 The signatures and structure functions for inelastic scattering in xenon have been studied in detail in~\cite{Baudis:2013bba}. 
-It was found that this channel is complementary to spin-dependent, elastic scattering, and that it dominates the integrated rates above $\simeq10$\,keV of deposited energy.
+It was found that this channel, 
+{\ale although not competitive in terms of sensitivity,}  
+is complementary to the spin-dependent, elastic scattering one, 
+and that it dominates the integrated rates above $\simeq10$\,keV of deposited energy. 
 In addition, in case of a positive signal, the observation of inelastic scattering would provide a clear 

### 2017-06-13 Inelastic/results.tex
version uploaded to archive
response to referee, first draft

@@
 \begin{figure}[t]
-  \includegraphics[width=\linewidth]{images/data_vs_bkg.png}
+  \includegraphics[width=\linewidth]{data_vs_bkg.png}
   \caption{Distribution of  observed events  in the region of interest (data points), along with the normalized distribution from calibration data (filled histogram).
-The bottom panel displays the ratio
-between data and expected background, where the light  and dark blue shaded areas represent the statistical and systematic uncertainty 
-on the background expectation, respectively. The expected signal for a WIMP mass of 100\,GeV/c$^2$ (blue dashed), normalized to a total of 50 events, is also shown.}
+The expected signal for a WIMP mass of 100\,GeV/c$^2$ (blue dashed), normalized to a total of 50 events, is also shown.
+	  The bottom panel displays the ratio between data and expected background, where the light  and dark blue shaded areas represent the statistical and systematic uncertainty on the background expectation, respectively.
+}
   \label{fig:dataVSbkg}
@@
 \begin{figure}[t]
-  \includegraphics[width=\linewidth]{images/limit_reb.png}
+  \includegraphics[width=\linewidth]{limit_reb.png}
   \caption{Upper limit (blue curve) on the spin-dependent, inelastic WIMP-nucleon cross section as a function of WIMP mass.  
@@
 %\sout{We employ the nuclear structure factors as calculated in \cite{Baudis:2013qla}, based on state-of-the-art large-scale shell-model calculations, with chiral effective field theory WIMP-nucleon currents.}
+{\ale The CL$_s$ technique helps protecting against exclusion of a cross section
+smaller than experimental sensitivity.}
 

### 2017-06-19 Inelastic/response_to_referee.tex
edited response and fixed figure in main text

@@
 
-We thank the referee for his/her's valuable comments, we really think these add a value to the paper. 
+We thank the referee for the valuable comments, we sincerily think these added  value to the paper. 
 You can find below the answer to the detailed questions, we implemented most of the suggestions in the new version of the paper.
@@
 of interaction is spin-dependent, while for classical elastic scattering is much more difficult to tell.
-In the text we say that this search is complementary to the standard SD. {\color{red} We modified the text to "It was found that this channel,  although not competitive in terms of sensitivity,  
-is complementary to the spin-dependent, elastic scattering one".} 
-The "10 KeV" of deposited energy referes to both, if one looks at integrated rated above 10KeV NR for elastic scattering 
-finds that is smaller than the integrated rate of  NR+ER for inelastic scattering.
-{\color{red} We think that deposited energy is the correct wording here, since indeed it differs for the two cases.}
+In the text we say that this search is complementary to the standard SD.  We modified the text to "It was found that this channel,  
+although not competitive in terms of sensitivity,  
+is complementary to the spin-dependent, elastic scattering one".
+The "10 KeV" of deposited energy refers to both, if one looks at integrated rated above 10KeV NR for elastic scattering 
+finds that is smaller than the integrated rate of  NR+ER for inelastic scattering, see Fig. 6 in (https://arxiv.org/abs/1309.0825).
+We think that deposited energy is the correct wording here, since indeed it differs for the two cases.
 
@@
 
-Yes, the limit would be stronger. However the scope of this paper is 
-not to discover dark matter, for which one would use instead SD elastic
-scattering channel, but rather explore a different analysis channel.
+Yes, the limit could have been stronger, a naive expectation for sensitivity improvement with respect to the current is about 30\%.
+However the scope of this paper is to explore a different analysis channel.
 Doing a combination on three different science runs (each of them having 
-different background conditions and acceptances) is very demandig.
+different background conditions and acceptances) is very demanding,
+this would have extended significantly the time scale for this analysis,
+which was not very well motivated at the time given the fact that we knew 
+Xenon1T data taking was starting soon.
 
@@
 The signal distribution changes according to wimp mass due to the NR component,
-we choose the ROI so that it will embrace all the wimp hipothesys at least at two 
+we choose the ROI so that it will embrace all the wimp hypothesis at least at two 
 sigma. Now added to the text.
@@
   \caption{ Sensitivity computed dividing the ROI in different numbers of equally sized bins.
-NOTE: this sensitivity curves where run in a test long ago before the final version, imost of nuissance parameter have different implementation or missing, so they are NOT directly comparable with the final one, altough similar.}
+NOTE: this sensitivity curves where run in a test long ago before the final version, most of nuisance parameter have different implementation or missing, so they are NOT directly comparable with the final one, although similar.}
   \label{fig:binning}
@@
 difference in sensitivity dividing the region in more than 10 equal sized bins. 
-So as soon as one divide the ROI in any number larger than 10 of equally sized bins would get the same result. So why not divide in 40 equally sized bins at this point?  
-There is a limiting factor: we are using asymptotic formulae for distribution of the
-test statistic, these formulaes are valid in the assumption of Wilks theorem, so that the number
-of events in each bin should be "large". In order to not have bins with drammatically low background, which
-happens in case of equally sized bins, we needed to merge bins and we need to do it in a way to not disrupt sensitivity.
-So we started with a number of equally sized bins (roughly 20 if I remember corretly) and we grouped them achieving similar 
-background density,  in this way the discrimination power is conserved, meaning that the discrimination power will be equal or better than 
-the one using the same number of final bins (in this case 9) but produced in equal sizes.
-Within this prescription, which is very general, the chosed arrangement of bins and shapes is almost arbitrary and
-could have been done in many different ways, however it doesn't matter because following 
-this procedure whatever peculiar binning choice will not  impact  our 
-sensitivity, so we choosed the solution that was technically easier.
+So as soon as one divide the ROI in any number larger than 10 of equally sized bins would get the same result. 
+%So why not divide in 40 equally sized bins at this point?  
+%There is a limiting factor: we are using asymptotic formulae for distribution of the
+%test statistic, these formulae are valid in the assumption of Wilks theorem, so that the number
+%of events in each bin should be "large". In order to not have bins with dramatically low background, which
+%happens in case of equally sized bins, we needed to merge bins and we need to do it in a way to not disrupt sensitivity.
+We choosed a rebinning strategy that depends on the background shape and is the same for all masses. The bin shapes are designed to have
+equal background density: this ensures high discrimination power while keeping a low number of bins and ensure that all bins are 
+well populated (assumption necessary for the used test statistic asymptotic formulae). 
+%So we started with a number of equally sized bins (roughly 20 if I remember correctly) and we grouped them achieving similar 
+%background density,  in this way the discrimination power is conserved, meaning that the discrimination power will be equal or better than 
+%the one using the same number of final bins (in this case 9) but produced in equal sizes.
+%Within this prescription, which is very general, the chosen arrangement of bins and shapes is almost arbitrary and
+%could have been done in many different ways, however it doesn't matter because following 
+%this procedure whatever peculiar binning choice will not  impact  our 
+%sensitivity, so we choose the solution that was technically easier.
 We added to the text that "it has been crosschecked that changing bin choice does not impact sensitivity".
@@
 
-{\color{red} Our detector position resolution is of the order of few mm, multiple scatters S2 that are 
+Our detector position resolution is of the order of few mm, multiple scatters S2 that are 
 closer than that will be merged. These in any case are not a problem, since this cut is meant 
 to reduce neutron background, in the standard elastic analysis this turns into a small
-uncertainty in neutron bkg model, but for the energies deposits of this analysis neutron bkg 
-is irrelevant, so we could have even dropped that cut. When we say S2 we mean the primary peak. }
+uncertainty in neutron background model, but for the energies deposits of this analysis neutron background 
+is irrelevant, so we could have even dropped that cut. When we say S2 we mean the primary peak.
 
@@
 
-{\color{red} Changed to "a full simulation (NR and ER response) of the 39,6~KeV xenon line..." }
+Changed to "a full simulation (NR and ER response) of the 39,6~KeV xenon line..."
 
@@
 
-Ly is the measured light yield in PE/$KeV_{ee}$, so it encapsulate all the position dependence
-and collection efficiencies, as maybe described in more detail in 
+Ly is the measured light yield in PE/$KeV_{ee}$, so it encapsulates all the position dependence
+and collection efficiencies, as described in more detail in 
 (https://arxiv.org/abs/1207.3458). This notation is common to XENON papers, but it might not be 
@@
 
-What we meant is that is approximately constant with the wimp mass.
-Values being compatible within uncertainties with 0.80 +- 0.05.
-it has been changed to: "The combined acceptance  of all selection criteria in the region 
+Changed to: "The combined acceptance  of all selection criteria in the region 
 of interest is roughly constant for all masses and averages to $(0.80\pm0.05)$."
@@
 It has been proven by several XENON analysis that indeed 60Co and 232Th are very good
-and representative candidate for ER background, since they reproduce quite well the compton
+and representative candidate for ER background, since they reproduce quite well the Compton
 scattering band. They have been used multiple times in several xenon analysis, see for 
@@
 but effective approach. 
-Regarding the "dicotomy of threatment": we could't use AmBe data as signal model due to 
+Regarding the "dichotomy of treatment": we couldn't use AmBe data as signal model due to 
 the non negligible difference between WIMP and AmBe introduced by the NR.
@@
 
-Done.
+Since we use a large MC sample the statistical uncertainty is negligible, the bin with largest uncertainty 
+has relative error of $<$1\%, this makes the stat uncertainty be smaller than the tickness of the line.
+So we removed the "statistical" uncertainty label as in here we want to underline the systematic uncertainties.
 
@@
 	\item Regarding Pseudo-samples, these are used to produce shape uncertainty, so histogram variation, of +/-1 sigma step.
-What typically one does with these "pseudo-samples" histograms  is to use them as seeds for interpolation techniques controlled by a nuissance parameter, as the referee is suggesting.
-Now we have several such shape uncertainties and we felt that this approach was overcomplicated.
+What typically one does with these "pseudo-samples" histograms  is to use them as seeds for interpolation techniques controlled by a nuisance parameter, as the referee is suggesting.
+Now we have several such shape uncertainties and we felt that this approach was over complicated.
 We opted for a conservative but simple approximation: we sum up in quadrature all the "positive" and "negative" variation for each bin separately, we then assign the maximal of the two as a symmetric Gaussian distributed uncertainty on the single bin.
-In this way we avoid the complication of histogram shape interpolation of several nuissance parameter.
-Being the uncertainty on each bin independent from the other this allows for much more freedom and has overcoverage of the shape variations.
+In this way we avoid the complication of histogram shape interpolation of several nuisance parameter.
+Being the uncertainty on each bin independent from the other this allows for much more freedom and has over coverage of the shape variations.
 
@@
 
-	\item The analysis was not technically blind, since this data region was explored in several 
-other studies. The procedure we used was as if it was blind, since we didn't tune cuts on data.
+	\item Since this data region was explored in several other studies, this analysis was not blind.
+		The procedure we used was as if it was blind, since we didn't tune cuts on data.
 
-	\item All the systematic uncertainties come from auxiliary measurements, so real measurements either from our experiment or in the literature, some of them may not be expected to be gaussian distributed,
-for example Leff, but in these cases the parametrizzation chosen is the one commonly accepted.
+	\item All the systematic uncertainties come from auxiliary measurements, either from our experiment or from the literature, so 
+		to the best of our knowledge their prior is indeed a Gaussian. 
+		However, some of them may not be expected to be Gaussianly distributed, for example Leff, but in these cases the chosen parameterization
+		is the one commonly accepted.
 
@@
 
-The CLs was common practice of XENON100, and common practice of many high energy experimets. 
-This is a technique that target the same problem as power constrain (but in a less silly way),
-it protects the limit by data underfluctiation so that is difficult to exclude
-cross section to which the experiment is not sensitive to, paying the price of a bit worst sensitivity.
-The sentence {\color{red}"The CL$_s$ technique helps protecting against exclusion of a cross section
-smaller than experimental sensitivity" has been added}. Not really sure I wan to add that.
+The sentence "The CL$_s$ technique helps protecting against exclusion 
+of a cross section smaller than experimental sensitivity" has been added.
 
@@
 No the limit is not constrained, CLs is used instead of a power constrained limit.
-It just a coincidence that it stops at -1 sigma.
-Yes the bands are not smoothened while the curve is, this is due to a silly ROOT 
-problem which is {\color{red} fixed now} in another way.
-There is no other result that we know of that explores exactly this process.
+It is just a coincidence that it stops at -1 sigma.
+Yes the bands are not smoothened while the curve is, this is due to a ROOT 
+problem (smoothening of a filled area does not work well in ROOT) which we  
+fixed now. There is no other result that we know of that explores 
+exactly this process.
 

### 2017-06-19 Inelastic/analysis.tex
edited response and fixed figure in main text

@@
   \includegraphics[width=\linewidth]{wimp_sys_unc.png}
-  \caption{Predicted signal yield in each sub-region (blue curve), along with statistical and systematic uncertainties (shaded area) simulated for a WIMP mass of 100\,GeV/c$^2$.
+  \caption{Predicted signal yield in each sub-region (blue curve), along with systematic uncertainties (shaded area) simulated for a WIMP mass of 100\,GeV/c$^2$.
 The signal has been scaled for a total number of 50 events.

### 2017-06-20 Inelastic/response_to_referee.tex
edited answer and manuscript

@@
 
-We thank the referee for the valuable comments, we sincerily think these added  value to the paper. 
-You can find below the answer to the detailed questions, we implemented most of the suggestions in the new version of the paper.
-Below we report each  comment/question in blue and its related answer in black, we specifically state what modifications
-were applied to the paper in each single answer.
+We thank the referee for the valuable comments, we sincerely think these added value to the paper.
+We addressed all the comments and implemented most of the suggestions in the new version of the manuscript.
+Below we list each comment/question in blue and its related answer in black, and we specifically state which modifications
+were implemented in the new version of the paper.
 
@@
 
-Looking at the paper "Signatures of Dark Matter Scattering Inelastically Off Nuclei" seems like he is right,
-and the interaction is isospin independent. {\color{red} please confirm.}, shall we change the abstract then?
+The new SD limits are indeed isospin dependent, we followed the literature and Ref.
+[6] and set limits on spin-dependent, WIMP-neutron interactions.
+Isospin independent constraints could be the subject of a different publication.
 
@@
 It was still unclear to me. Basically, I want to understand if there
-was any reasonable scenario under which you could’ve seen a signal, or
-whether that was already impossible and you were “doomed” to only set
+was any reasonable scenario under which you could have seen a signal, or
+whether that was already impossible and you were doomed to only set
 a limit. This changes the theme of the paper significantly in my mind
 from discovery potential to a confirmation/cross-check of an existing
-limit in a new channel. - “10 keV of deposited energy”: Does this
+limit in a new channel. - “10 keV of deposited energy: Does this
 refer to nuclear or electron recoil or both? Unclear since we are now
@@
 
-Classical searches for spin dependent elastic scattering have higher sensitivity with respect to this search for spin 
-dependent inelastic scattering. However, in case dark matter would be found, this type of search ensures you that the type 
-of interaction is spin-dependent, while for classical elastic scattering is much more difficult to tell.
-In the text we say that this search is complementary to the standard SD.  We modified the text to "It was found that this channel,  
+Classical searches for spin-dependent elastic scattering have higher sensitivity compared to this search for 
+spin-dependent inelastic scattering. However, in case dark matter would be found, a positive signal in the inelastic channel would deliver a clear evidence for  
+the spin-dependent nature of the interaction. 
+In the text we mention that this search is complementary to the standard SD search.  We modified the text to "It was found that this channel,  
 although not competitive in terms of sensitivity,  
 is complementary to the spin-dependent, elastic scattering one".
-The "10 KeV" of deposited energy refers to both, if one looks at integrated rated above 10KeV NR for elastic scattering 
-finds that is smaller than the integrated rate of  NR+ER for inelastic scattering, see Fig. 6 in (https://arxiv.org/abs/1309.0825).
+The "10\,keV" of deposited energy refers to both; if one looks at integrated rated above 10\,keV NR for elastic scattering, one  
+finds that is below the integrated rate of  NR+ER for inelastic scattering, see Fig. 6 in (https://arxiv.org/abs/1309.0825).
 We think that deposited energy is the correct wording here, since indeed it differs for the two cases.
@@
 
-Yes, the limit could have been stronger, a naive expectation for sensitivity improvement with respect to the current is about 30\%.
-However the scope of this paper is to explore a different analysis channel.
-Doing a combination on three different science runs (each of them having 
-different background conditions and acceptances) is very demanding,
-this would have extended significantly the time scale for this analysis,
-which was not very well motivated at the time given the fact that we knew 
-Xenon1T data taking was starting soon.
+Yes, the limit would have been stronger, a naive expectation for the sensitivity improvement with respect to the current one is $\sim$30\%.
+However the main scope of this paper is to explore a different analysis channel, and not to improve the sensitivity for SD searches, as mentioned above.
+Combining three different science runs (each acquired under different background conditions and with different acceptances) is very demanding,
+and would have extended significantly the time scale for this analysis. Such an extension  was not well-motivated at the time given the fact that XENON1T was to start data taking soon.
 
@@
 
-The signal distribution changes according to wimp mass due to the NR component,
-we choose the ROI so that it will embrace all the wimp hypothesis at least at two 
-sigma. Now added to the text.
+The signal distribution changes with the WIMP mass due to the NR component.
+We selected the ROI such that it will contain the WIMP hypothesis at least at two 
+sigma. This statement is now added to the text.
 
@@
   \caption{ Sensitivity computed dividing the ROI in different numbers of equally sized bins.
-NOTE: this sensitivity curves where run in a test long ago before the final version, most of nuisance parameter have different implementation or missing, so they are NOT directly comparable with the final one, although similar.}
+Please note: these sensitivity curves where obtained in a test long before the final version, most of nuisance parameter have  a different implementation or are missing, hence they are not directly comparable with the final one, although similar.}
   \label{fig:binning}
@@
 If one follows an appropriate binning procedure, then the choice of bins is irrelevant, meaning that 
-the final result should not depend on binning. Furthermore we never said that this particular 
-choice is optimal for all masses.
+the final result should not depend on the binning. Furthermore, we did not specify that this particular 
+choice is optimal for all WIMP masses.
 
-It was shown, see Figure~\ref{fig:binning}, a non appreciable
-difference in sensitivity dividing the region in more than 10 equal sized bins. 
-So as soon as one divide the ROI in any number larger than 10 of equally sized bins would get the same result. 
+We have shown, please see Figure~\ref{fig:binning}, that once we divide the region in more than 10 equally sized bins,
+the difference in sensitivity is small. Hence, as soon as we divide the ROI in any number $>$10 of equally sized bins, we practically obtain the same result. 
 %So why not divide in 40 equally sized bins at this point?  
@@
 %happens in case of equally sized bins, we needed to merge bins and we need to do it in a way to not disrupt sensitivity.
-We choosed a rebinning strategy that depends on the background shape and is the same for all masses. The bin shapes are designed to have
-equal background density: this ensures high discrimination power while keeping a low number of bins and ensure that all bins are 
-well populated (assumption necessary for the used test statistic asymptotic formulae). 
+We selected a rebinning strategy that depends on the background shape and is the same for all masses. The bin shapes are designed to have
+equal background density: this ensures high discrimination power while keeping a low number of bins and ensures that all bins are 
+well populated (this assumption is necessary for the used test statistic asymptotic formulae). 
 %So we started with a number of equally sized bins (roughly 20 if I remember correctly) and we grouped them achieving similar 
@@
 %sensitivity, so we choose the solution that was technically easier.
-We added to the text that "it has been crosschecked that changing bin choice does not impact sensitivity".
+We added to the text that "it has been cross-checked that changing the bin choice does not impact the sensitivity".
 
@@
 
-Our detector position resolution is of the order of few mm, multiple scatters S2 that are 
-closer than that will be merged. These in any case are not a problem, since this cut is meant 
-to reduce neutron background, in the standard elastic analysis this turns into a small
-uncertainty in neutron background model, but for the energies deposits of this analysis neutron background 
-is irrelevant, so we could have even dropped that cut. When we say S2 we mean the primary peak.
+Our detector position resolution is of the order of a few mm, multiple-scatter S2s that are 
+closer than the resolution will be merged. These present however not a problem for our analysis, since this cut is designed 
+to reduce the neutron background. In the standard elastic analysis this turns into a small
+uncertainty in neutron background model, but for the energy deposits of this analysis the neutron background 
+is irrelevant (hence we could have even dropped this selection criterium). When we say S2 we mean the primary peak.
 
@@
 
-Changed to "a full simulation (NR and ER response) of the 39,6~KeV xenon line..."
+Indeed, and we changed to "a full simulation (NR and ER response) of the 39,6\,keV xenon line..."
 
@@
 
-Ly is the measured light yield in PE/$KeV_{ee}$, so it encapsulates all the position dependence
-and collection efficiencies, as described in more detail in 
+Ly is the measured light yield in PE/keV$_{ee}$, hence it contains the position dependence
+and the collection efficiencies of the signal, as described in more detail in 
 (https://arxiv.org/abs/1207.3458). This notation is common to XENON papers, but it might not be 
@@
 
-Changed to: "The combined acceptance  of all selection criteria in the region 
+This is correct, and we changed to: "The combined acceptance  of all selection criteria in the region 
 of interest is roughly constant for all masses and averages to $(0.80\pm0.05)$."
@@
 
-Section D has been merged to section C.
+We agree, and section D has now been merged to section C.
 
@@
 
-It has been proven by several XENON analysis that indeed 60Co and 232Th are very good
-and representative candidate for ER background, since they reproduce quite well the Compton
-scattering band. They have been used multiple times in several xenon analysis, see for 
-example (https://arxiv.org/abs/1207.3458, and https://arxiv.org/abs/1609.06154).
+It has been shown in several XENON analyses that indeed $^{60}$Co and $^{232}$Th are good
+representations of the ER background at low energies, since they reproduce well the Compton-scatter band. They have been used several  times, 
+see for example (https://arxiv.org/abs/1207.3458, and https://arxiv.org/abs/1609.06154).
 A full simulation with NEST will not give smaller uncertainties due to intrinsic
-NEST uncertainties and due to the MC radiogenic material uncertainty. 
-Furthermore, there is no such a proven MC-data matching for XENON100 for these energies, 
-meaning we don't have a Geant4 of all radioactive material 
-background that produces a spectra that we can fully trust. So we opted for a simple 
+NEST uncertainties and due to the  uncertainty in the MC prediction of the radiogenic neutron background from materials.
+Furthermore, we do not have a full MC-data matching for XENON100 at these energies, 
+meaning we don't have a Geant4-based model of all the material 
+backgrounds that produces spectra that we can fully trust. Hence we opted for a simple 
 but effective approach. 
-Regarding the "dichotomy of treatment": we couldn't use AmBe data as signal model due to 
-the non negligible difference between WIMP and AmBe introduced by the NR.
+Regarding the "dichotomy of treatment": we could not use AmBe data as a signal model due to 
+the non-negligible difference between WIMP and AmBe introduced by the mass-dependent NR.
 
@@
 
-Since we use a large MC sample the statistical uncertainty is negligible, the bin with largest uncertainty 
-has relative error of $<$1\%, this makes the stat uncertainty be smaller than the tickness of the line.
-So we removed the "statistical" uncertainty label as in here we want to underline the systematic uncertainties.
+Since we use a large MC sample the statistical uncertainties are negligible, the bin with the largest uncertainty 
+has  a relative error of $<$1\%. This makes the statistical uncertainty smaller than the thickness of the line.
+We thus removed the "statistical" uncertainty label, as here we aim to underline the systematic uncertainties.
 
@@
 
-This comment touches many topics and we try to reply in order in the following:
+This comment touches many topics and we try to reply to each in the following:
 \begin{enumerate}
-	\item Regarding Pseudo-samples, these are used to produce shape uncertainty, so histogram variation, of +/-1 sigma step.
-What typically one does with these "pseudo-samples" histograms  is to use them as seeds for interpolation techniques controlled by a nuisance parameter, as the referee is suggesting.
-Now we have several such shape uncertainties and we felt that this approach was over complicated.
-We opted for a conservative but simple approximation: we sum up in quadrature all the "positive" and "negative" variation for each bin separately, we then assign the maximal of the two as a symmetric Gaussian distributed uncertainty on the single bin.
+	\item Regarding the pseudo-samples, these are used to produce the shape uncertainty, hence histogram variation, in $\pm$1-sigma steps.
+One typically uses these "pseudo-samples" histograms  as seeds for interpolation techniques controlled by a nuisance parameter, as the referee suggest.
+We have several such shape uncertainties and we felt that this approach was over complicated.
+We opted for a conservative but simple approximation: we sum up in quadrature all the "positive" and "negative" variations for each bin separately, we then assign the maximal of the two as a symmetric Gaussian distributed uncertainty on the single bin.
 In this way we avoid the complication of histogram shape interpolation of several nuisance parameter.
-Being the uncertainty on each bin independent from the other this allows for much more freedom and has over coverage of the shape variations.
+As the uncertainty in each bin is independent from one another, this allows for more freedom and has over coverage of the shape variations.
 
@@
 
-	\item Since this data region was explored in several other studies, this analysis was not blind.
-		The procedure we used was as if it was blind, since we didn't tune cuts on data.
+	\item Since this parameter space in the data was explored in several other studies, our analysis was not blind.
+		Nonetheless, the employed analysis procedure was as if the signal region were blind, since we didn't tune our event selection criteria on the data in the ROI.
 
@@
 		to the best of our knowledge their prior is indeed a Gaussian. 
-		However, some of them may not be expected to be Gaussianly distributed, for example Leff, but in these cases the chosen parameterization
-		is the one commonly accepted.
+		However, some of these may not be expected to feature a Gaussian distribution, for example L$_{\rm{eff}}$, but in these cases the chosen parameterisation
+		is the one commonly accepted in the field.
 
-	\item The sentences Figure 4 have been swapped.
+	\item We agree, and the sentences in the caption of Figure 4 have been swapped.
 \end{enumerate}
@@
 
-The sentence "The CL$_s$ technique helps protecting against exclusion 
-of a cross section smaller than experimental sensitivity" has been added.
+We agree, and the sentence   "The CL$_s$ technique helps to protect against excluding  a cross section which is smaller than the experimental sensitivity."  has been added.
 
@@
 No the limit is not constrained, CLs is used instead of a power constrained limit.
-It is just a coincidence that it stops at -1 sigma.
-Yes the bands are not smoothened while the curve is, this is due to a ROOT 
+It is simply a coincidence that it stops at -1 sigma.
+The referee is correct, the bands are not smoothened while the curve is -  this is due to a ROOT 
 problem (smoothening of a filled area does not work well in ROOT) which we  
-fixed now. There is no other result that we know of that explores 
-exactly this process.
+fixed now. 
+There is no other result that we know of which explores 
+exactly this inelastic scattering process. In particular, this is the first time we analysed the XENON data for 
+such a signature (we note that new structure function calculations were only available in 2013).
 

### 2017-06-20 Inelastic/analysis.tex
edited answer and manuscript

@@
 The ROI extends from 60 to 210\,PE in cS1, from 4$\times \, 10^3$ to 16$\times \, 10^3$\,PE in cS2,
-{\ale such that to have at least 95\% acceptance to all signal mass hypothes. The ROI }
+{\ale such as to have at least 95\% acceptance to all signal mass hypotheses. The ROI }
 %this
 is further divided  into sub-regions as shown in Figure~\ref{fig:SR}.  These sub-regions were defined to  contain a (roughly) similar number of expected background events in each region, 
-{\ale it was crosschecked that changing binning choice does not impact the sensitivity.} 
+{\ale where we crosschecked that changing the binning choice does not impact the sensitivity.} 
 The control regions (denoted as CR1 and CR2 in the figures), are selected to be as close as possible to the ROI,  and are used for cross checks of the background shape distribution.
@@
 {\ale  
-The described signal simulation was validated reproducing the 39.6\,keV xenon line activated from $^{241}$AmBe neutrons and comparing it with data.
-For this purpose the NR energy spectrum expected from inelastic neutron-$^{129}$Xe scattering has been obtained via  Monte Carlo techniques, 
-where we take into account the  detector response and the non-uniform spatial distribution. The acceptance of analysis selections to this type of interaction 
-have been recomputed. In particular, the acceptance to the double scatter cut differs greatly between neutrons and WIMPs scattering. 
-Figure~\ref{fig:mc_comp} shows a comparisons between simulation (light blue) and calibration data (dark blue), contour lines of equal densities are compared in Figure~(a), 
+The described signal simulation was validated by reproducing the 39.6\,keV xenon line activated from $^{241}$AmBe neutrons and comparing it with data.
+For this purpose, the NR energy spectrum expected from inelastic neutron-$^{129}$Xe scatters has been obtained via  Monte Carlo techniques, 
+where we take into account the  detector response and the non-uniform spatial distribution of events. The acceptance of our analysis selection criteria to this type of interaction 
+have been recomputed. In particular, the acceptance to the double-scatter cut differs greatly between neutron and WIMPs scatters. 
+Figure~\ref{fig:mc_comp} shows a comparisons between simulation (light blue) and calibration data (dark blue). Contour lines of equal densities are compared in Figure~(a), 
 while Figure~(b) shows the cS1 projected distributions for different ranges in cS2. 

### 2018-08-17 SR1_detailed_note/Sections/DetectorSignalResponse.tex
SR1

XENON1T WIMP signal and background model used in the statistical inference are built based on the simulation which takes into consideration the detailed characterizations of the detector systematics, as well as the most comprehensible modeling of the recombination process of the liquid xenon.
The coherent modeling of the electronic recoils (ERs) and nuclear recoils (NR) is of high accuracy in terms of the uncertainty of the nuisance parameters and their correlations.
In this chapter, the details of the detector signal response model will be given.

\subsection{Basic Signal Response in Liquid Xenon}
% @Qing

\subsection{Recombination in Low Energy}
% @Qing

\subsection{Influence by Detector Reconstruction}
% @Qing

### 2018-08-17 SR1_detailed_note/Sections/Likelihood.tex
SR1

\newcommand{\lagr}{\mathcal{L}} %likelihood
\newcommand{\LL}{\log \mathcal{L}} %likelihood
\newcommand{\sr}{\mathrm{SR}}
\newcommand{\nuis}{\theta}
\newcommand{\nuiss}{\vec{\nuis}}
\newcommand{\Pois}[2]{\mathrm{Pois}(#1 | #2)}
\newcommand{\Gaus}[3]{\mathrm{Gaus}(#1 | #2,#3)}
\newcommand{\Uniform}[3]{\mathrm{Uniform}(#1 | #2,#3)}

\subsection{The XENON1T Combined Likelihood}
%Knut
The log-likelihood used in the spin-independent analysis is a sum of extended un-binned likelihoods for the two science runs, extended un-binned likelihoods for ER calibration data, and terms expressing ancillary measurements of nuisance parameters $\nuis_m$: 
\\
Where $\sr$ runs over data-taking periods, \SRzero and \SRone, $\sigma$ is the WIMP-nucleon cross-section, and $\LL_\mathrm{sci}$,$\LL_\mathrm{cal}$ are the likelihood terms for the dark matter search data and \rnzero calibration data, respectively. Ancillary measurements  The un-binned likelihoods take the form:

\subsection{Analysis Dimensions}
%radial choice
%benefit of less analysis space
%does FV definition go here? 
\subsection{Core Volume Segmentation}

\subsection{Safeguard}
A mismodelling term, proposed in~\cite{safeguard} is added to the ER model, consisting of a signal-like component added or subtracted to the nominal ER model:

Since the PDF is constrained to be non-negative, the

\subsection{Nuisance Parameters}
%Mention here: 
%BBF nuisance parameter propagation
%Radiogenics common parameter, others uncorrelated
%wall shape parameter consideration
%why signal shape was dropped
%signal rate uncertainties

\subsection{Trial Correction}
As discovery significances are computed for WIMP-masses between $6$ and $1000$ GeV, the final p-value of the experiment must reflect that multiple hypotheses were tested, and the lowest local p-value is picked as the most significant excess. The result is correlated between multiple masses, with a lower correlation between the peaked low-mass WIMP, and complete correlation between dark matter masses above $~200$ GeV, where the recoil spectrum converges. Toy Monte-Carlo data samples are generated without a dark matter signal, and discovery significances are computed for the entire mass range. The lowest local p-value is stored to compute the distribution of most significant local p-values. The global significance of the actual dataset is the percentile of the lowest p-value from the actual data of this distribution. Using local p-values rather than log-likelihood rations directly corrects for the uneven weighting that would result as different masses do not have the same null-distribution of the discovery log-likelihood ratio.

\subsection{Coverage}
The fraction of repeated experiments where the confidence interval contains the true parameter is called the coverage. Perfect coverage is equal to the confidence interval, $0.9$ in the case of XENON. As the experiment decided to report only the upper edge of the confidence interval for discovery significances $<3\sigma$, there will be over-coverage at very low signal sizes. This has a similar effect to the power constraint. Figure~\ref{fig:coverage}n shows the coverage for a $50$ GeV WIMP, with the red line representing the profile construction coverage, and blue the coverage including the $3\sigma$ threshold. The orange band, shows the $-\sigma$ to $\sigma$ sensitivity band. The result is consistent with perfect coverage (marked by the gray band, including limited statistics), with overcoverage for the $3\sigma$ threshold only under the $-1\sigma$ edge of the sensitivity band.

\begin{figure}[tbp]
\centering
\includegraphics[width=\columnwidth]{{Plots/blueice_coverage_FCplus3sigma_wimp_mass50_livetime278.87151m}.pdf}
\caption{\label{fig:coverage} 
}
\end{figure}

### 2018-08-17 SR1_detailed_note/Sections/SurfaceBackground.tex
SR1

\subsection{Surface Backgrounds}
% @Fei
Just add the content to start, will modify the description further.....

Interactions in the inner part of the detector can be nicely modelled by combining our knowledge on LXe's properties to ionizing particles and the detector related properties like charge/light collections. In cases where the latter information is missing/incomplete, we need to develop new algorithms to model the events. In this and following sections, two classes of background components are analyzed for the XENON1T dark matter searches.

As has been proved by several experiments~\cite{cdms, deap}, detector surfaces exposed long to ambient air during construction phase are contaminated by large amount of radon progeny, in particular the $^{210}$Pb. With a 22\,y half-life, $^{210}$Pb basically decays constantly within the XENON1T's operation of a few years. For dark matter searches, ion recoil of $^{206}$Pb from $^{210}$Po $\alpha$-decays, $\beta$-decays and the resulting X-rays, Auger electrons of $^{210}$Pb are particularly important. Due to unknown LXe's properties and detector physics in presence of PTFE as well as the complicated decay structures, a precise modeling based on Monte-Carlo simulation approach has not been achieved in XENON1T yet. Instead, a data driven approach is adopted to predict the event distribution of this background.

\begin{figure}[tbp]
\centering
\includegraphics[width=\columnwidth]{Plots/surface_s2s1_distribution_blessed_sr1.pdf}
\caption{\label{fig:surface_bg} 
}
\end{figure}

### 2018-08-17 SR1_detailed_note/bibliography.tex
SR1

\begin{thebibliography}{24}
\addcontentsline{toc}{chapter}{Bibliography}

\bibitem{wimp_hooper} G.~Bertone, D.~Hooper and J.~Silk, Phys. Rep. \textbf{405}, 279 (2005).

\bibitem{wimp_review} L.~Roszkowski {\it et al.} Rep. Prog. Phys. \textbf{81}, 066201 (2018). %[arXiv:1707.06277]

\bibitem{teresa_review} T.~Marrod\'an Undagoitia and L.~Rauch, J.\ Phys.\ G {\bf 43}, no. 1, 013001 (2016)

\bibitem{indirect} L.~E.~Strigari, Phys. Rep. \textbf{531}, 1 (2012).
%6
\bibitem{xe_sr0} E.~Aprile {\it et al.} (XENON Collaboration), Phys. Rev. Lett. \textbf{119}, 181301 (2017). %[arXiv:1705.06655].
%7
\bibitem{lux_dm} D. S. Akerib {\it et al.} (LUX Collaboration), Phys. Rev. Lett. \textbf{118}, 021303 (2016). %[arXiv:1608.07648].
%8
\bibitem{panda_dm} X. Cui {\it et al.} (PandaX-II Collaboration), Phys. Rev. Lett. \textbf{119}, 181302 (2017). %[arXiv:1708.06917].
%9
\bibitem{xe_instrument} E.~Aprile {\it et al.} (XENON Collaboration), Eur. Phys. J. C \textbf{77}: 881 (2017). %[arXiv:1708.07051].
\bibitem{xe_pmts} E.~Aprile {\it et al.} (XENON Collaboration), Eur. Phys. J. C \textbf{75}: 546 (2015). %[arXiv:1503.07698]. 
\bibitem{pmt2} P. Barrow {\it et al.} JINST \textbf{12}, no. 01, P01024 (2017). % [arXiv:1609.01654].

%10
\bibitem{xe_muonveto} E.~Aprile {\it et al.} (XENON Collaboration), JINST \textbf{9}, P11006 (2014). %[arxiv:1406.2374].

\bibitem{sorensen} P.~Sorensen, K.~Kamdin. JINST \textbf{13}, P02032 (2018). %[arxiv:1711.07025].

\bibitem{kemfield} D.~Furse {\it et al.}. New J. Phys. \textbf{19} 053012 (2017)

\bibitem{luxkr} D. S. Akerib {\it et al.}, Phys. Rev. D \textbf{96}, 112009 (2017). % [arXiv:1708.02566].

% rn220
\bibitem{xe_rn220} E.~Aprile {\it et al.} (XENON Collaboration), Phys. Rev. D \textbf{95}, 072008 (2017).

%11
\bibitem{xe1t_ng} R.~F.~Lang {\it et al.}, Nucl. Inst. and Meth. A \textbf{879}, 31 (2018).

\bibitem{pearc_computing} B. Riedel {\it et al.} PEARC '18, ISBN 978-1-4503-6446-1 (2018). doi:10.1145/3219104.3219155.

\bibitem{pax} XENON Collaboration. (2018). The pax data processor v6.8.0. Zenodo. http://doi.org/10.5281/zenodo.1195785
%14
\bibitem{pmt_calibration} R.~Saldanha {\it et al.}, Nucl. Inst. and Meth. A \textbf{863}, 35 (2017). %[arXiv:1602.03150].
%15
\bibitem{double_pe} C. H. Faham {\it et al.}, JINST \textbf{10}, P09010 (2015).

\bibitem{lux_field} D. S. Akerib {\it et al.} (LUX Collaboration), JINST \textbf{12}, P11022 (2017).

\bibitem{lewin} J. Lewin and P. Smith, Astropart. Phys. \textbf{6} 87 (1996).

\bibitem{xe_kr} E.~Aprile {\it et al.} (XENON Collaboration), Eur. Phys. J. C \textbf{77}: 275 (2017). %[arXiv:1612.04284].
%16
\bibitem{xe_sebastian} S. Lindemann, H. Simgen, Eur. Phys. J. C \textbf{74}, 2746 (2014). %[arXiv:1308.4806].

\bibitem{xe_rn} E.~Aprile {\it et al.} (XENON Collaboration),	Eur. Phys. J. C \textbf{78} :132 (2018). %[arXiv:1708.03617]

%17
\bibitem{solarflux} A.~M.~Serenelli {\it et al.}, Astro. Phys. Journal \textbf{743}, 29 (2011). %[arXiv:1104.1639].
%18
\bibitem{coherent} D.~Akimov {\it et al.} (COHERENT Collaboration), Science \textbf{357}, 1123-1126 (2017). %[arXiv:1708.01294].

\bibitem{geant4} S.~Agostinelli {\it et al.}, Nucl. Inst. and Meth. A \textbf{506}, 250 (2003).

\bibitem{xenon1t_mc_paper} E.~Aprile {\it et al.} (XENON Collaboration), J.\ Cosmol.\ Astropart.\ Phys. \textbf{1604}, no. 04, 027 (2016)

\bibitem{xe_screen} E.~Aprile {\it et al.} (XENON Collaboration), Eur. Phys. J. C \textbf{77}: 890 (2017).

\bibitem{sources4a} W.B.~Wilson {\it et al.}, LANL technical note LA-13639-MS (1999).

\bibitem{mcnpx} R.~Lemrani {\it et al.}, Nucl. Inst. and Meth. A \textbf{560}, 454 (2006). %[arXiv:0601030].

\bibitem{xe100_tritium} E.~Aprile {\it et al.} (XENON Collaboration), Phys. Rev. D \textbf{97}, 092007 (2018).

\bibitem{ti_model} J. Thomas, and D. A. Imel, Phys. Rev. A \textbf{36}, 614 (1987).

\bibitem{NEST_v1} B. Lenardo {\it et al.} IEEE Trans. Nucl. Sci. \textbf{62}, 3387 (2015).

\bibitem{lux_tritium} D. S. Akerib et al. (LUX Collaboration), Phys. Rev. D \textbf{93}, 072009 (2016).

\bibitem{pixey_ar37} E. M. Boulton {\it et al.}, JINST \textbf{12}, P08004 (2017).

\bibitem{lux_xe127} D. S. Akerib {\it et al.} (LUX Collaboration), Phys. Rev. D \textbf{96}, 112011 (2017).

\bibitem{feldmancousins} G.~J.~Feldman and R.~D.~Cousins, Phys. Rev. D {\bf 57}, 3873 (1998).

\bibitem{PDG} C.~Patrignani {\it et al.} (Particle Data Group), Chin. Phys. C \textbf{40}, 100001 (2016).

\bibitem{James:1980ci} F.~James, Comput.\ Phys.\ Commun.\  \textbf{ 20}, 29 (1980).

\bibitem{Bartlett:1953} M. S. Bartlett, Biometrika \textbf{40} 3/4 (1953).

\bibitem{safeguard} N. Priel, L. Rauch, H. Landsman, A. Manfredini, and R. Budnik, J.\ Cosmol.\ Astropart.\ Phys. \textbf{5} 13 (2017).

\bibitem{exo_nature} J.~B.~Albert {\it et al.} (EXO-200 Collaboration), Nature \textbf{510}, 225 (2014).

\end{thebibliography}

### 2018-08-17 SR1_detailed_note/main.tex
SR1

%\RequirePackage{lineno}\linenumbers\newdimen\linenumbersep\linenumbersep=2pt
\documentclass[prd,aps,twocolumn,superscriptaddress,showpacs,showkeys,amsmath,amssymb,floatfix]{revtex4}
\usepackage[colorlinks=true,citecolor=blue,filecolor=blue,linkcolor=blue,urlcolor=blue,pdftex]{hyperref}

\usepackage{xspace} 
\usepackage[usenames,dvipsnames]{color}
\usepackage{booktabs,graphicx,mathrsfs,verbatim,amsmath,units,soul}
\usepackage{xspace} 
\usepackage{upgreek}
\usepackage{gensymb}
\usepackage{amsmath}
\usepackage{tabularx}

\sloppy

% NUMBERS

%% **********************
%Intro
%% **********************
\newcommand{\ton}{t}
% total mass LXe
\newcommand{\nxenontotalmass}{$3.2$\;\ton\xspace}
% target mass LXe
\newcommand{\nxenontargetmass}{$2.00$\;\ton\xspace}
% distance cathode to gate
\newcommand{\ntpcdriftlength}{$97~\mathrm{cm}$\xspace}
% diameter of TPC
\newcommand{\ntpcdiameter}{$96~\mathrm{cm}$\xspace}
% extraction field in V/cm
% https://xe1t-wiki.lngs.infn.it/doku.php?id=xenon:xenon1t:julien:xenon1t_3d_field_simulation#s1-region_-_sr1
%  ^ Warning: seems incorrect...
\newcommand{\nextractionfield}{$\sim$4~kV/cm\xspace}
\newcommand{\nmultiplicationfield}{$\sim$8~kV/cm\xspace}
% X ER rejection at Y NR acceptance
\newcommand{\nerrejectionpct}{99.7\%\xspace}
\newcommand{\nnracceptance}{50\%\xspace}
\newcommand{\nxenonnttargetmass}{5.9\;\ton\xspace}

%% **********************
% Detector Parameters 
%% **********************
% Liquid level tolerance
\newcommand{\nliquidleveltolerance}{2\%~RMS\xspace}
% Liquid level above gate
\newcommand{\nliquidlevelabovegate}{$2.5~\mathrm{mm}$\xspace}
% LXe temperature
\newcommand{\nxenoninternaltemp}{$-96.0$\,$^\circ$C\xspace}
% LXe temperature tolerance
\newcommand{\nxenoninternaltemptolerance}{0.02\%~RMS\xspace}
% GXe pressure
\newcommand{\nxenonpressure}{1.94~bar\xspace}
% GXe pressure tolerance
\newcommand{\nxenonpressuretolerance}{0.01\%~RMS\xspace}
% Largest S2 x-y map correction (in middle)
\newcommand{\nlargeststwoxycorrection}{32\%\xspace}
% Drift Fields 
% https://xe1t-wiki.lngs.infn.it/doku.php?id=xenon:xenon1t:jingqiang:field:data_driven_3d_electric_field_map
\newcommand{\driftfieldsrzero}{$120$~V/cm\xspace} %\;\pm\;8
\newcommand{\driftfieldsrone}{$81$~V/cm\xspace} %\;\pm\;7
\newcommand{\driftfielderror}{2.2~V/cm RMS\xspace} %\;\pm\;7

%% **********************
% Livetimes
%% **********************
\newcommand{\SRzero}{SR0\xspace}
\newcommand{\SRone}{SR1\xspace}
% Livetime-corrected SR0
\newcommand{\nlivetimesrzero}{32.1~days\xspace}
% Livetime-corrected SR1
\newcommand{\nlivetimesrone}{246.7~days\xspace}
% Livetime-corrected combined
\newcommand{\nlivetimetotal}{278.8~days\xspace}
% Start date of sciencerun0
\newcommand{\nstartofsciencerunzero}{November~22,~2016\xspace}
% End date of sciencerun1
\newcommand{\nendofsciencerunone}{February~8,~2018\xspace}
% Power outage of sciencerun1
\newcommand{\npoweroutsciencerunone}{February~24,~2018\xspace}
% SR0 DAQ livetime
\newcommand{\ndaqlivetimesrzero}{†92.2\%\xspace}
\newcommand{\ndaqdeadtimesrzero}{7.8\%\xspace}
% SR1 DAQ livetime
\newcommand{\ndaqlivetimesrone}{98.8\%\xspace}
\newcommand{\ndaqdeadtimesrone}{1.2\%\xspace}
% Date of run-ending earthquake
\newcommand{\nearthquakedate}{January~18,~2017\xspace}
% Date SR1 start
\newcommand{\nsronestart}{February~2,~2017\xspace}
% Magnitude of run-ending earthquake
\newcommand{\nearthquakemagnitude}{5.7\xspace}
% Total gain zero PMTs
\newcommand{\nblindedpmts}{36\xspace}
% Gain zero PMTs due to leaks
\newcommand{\nleakypmts}{26\xspace}
% Gain zero PMTs not due to leaks (should add up to total)
\newcommand{\notherpmts}{6\xspace}
% Days lost from muon veto cut
\newcommand{\nlossmuon}{1.2\%\xspace}%{3.4~days\xspace}
% Days lost from PMT flash cut
\newcommand{\nlossflash}{0.2\%\xspace}%{0.6~days\xspace}
% Days lost from S2 tail cut
\newcommand{\nlosstails}{4.4\%\xspace}%{12.3~days\xspace}
% Days of good Rn220 data
\newcommand{\ndaysrn}{17.1 days\xspace}
% Days of good AmBe data
\newcommand{\ndaysambe}{30.0 days\xspace}
% Days of good NG data
\newcommand{\ndaysng}{1.9 days\xspace}

%% **********************
% Thresholds and acceptance
%% **********************
% S2 threshold above 200pe
\newcommand{\nstwoaccoverthresh}{unity\xspace}
% Mean SPE acceptance, 3% is the 1-sigma. RMS would be 9.2%
\newcommand{\nmeanspeacceptance}{$(93\pm3)$\%\xspace}

%% **********************
% Fiducial and backgrounds
%% **********************
% Fiducial mass
\newcommand{\ncoremassname}{0.65~\ton\xspace}
\newcommand{\nonetonnemassname}{0.9~\ton\xspace}
\newcommand{\nnominalfiducialmassname}{1.3~\ton\xspace}
\newcommand{\nnominalfiducialmass}{$(1.30~\pm~0.01)$\;\ton\xspace}
%\newcommand{\nfiducialmass}{$1.6$}
% Combined exposure
\newcommand{\nexposure}{1.0\;\ton$\times$yr\xspace}
% Total NR background in fiducial mass
\newcommand{\ntotalnrbackground}{$XX$}
% Total ER background in fiducial mass
\newcommand{\nwallbackground}{$XX$}
% Kr85 level
\newcommand{\nkrlevel}{$^\mathrm{nat}\mathrm{Kr}/\mathrm{Xe} = (0.66\pm0.11)~\mathrm{ppt}$}
\newcommand{\krrate}{$(7.7\pm 1.3)$~events/$(\mathrm{\ton}\times\mathrm{yr}\times\kevee)$}

\newcommand{\rnlevel}{$(12.6 \pm 0.8)~\mu\mathrm{Bq}/\mathrm{kg}$\xspace}

\newcommand{\rnrate}{$(7.7\pm 1.8)$~events/$(\mathrm{\ton}\times\mathrm{yr}\times\kevee)$}

%\newcommand{\nkrlevel}{$^{85}\mathrm{Kr}/^{nat}\mathrm{Kr} = (1.645 \substack{+0.413 \\ -0.276})\times 10^{-11}$}
% Rn222 level
\newcommand{\nrnlevel}{YY}
%\newcommand{\nlowestbg}{${(63~\pm~2)}$~\dru\xspace}
\newcommand{\nlowestbg}{$(82\substack{+5 \\ -3}\textrm{~(sys)}\pm3\textrm{~(stat)})$~\dru\xspace}

\newcommand{\rntwo}{${}^{222}$Rn\xspace}
\newcommand{\rnzero}{${}^{220}$Rn\xspace}
\newcommand{\krbkg}{${}^{85}$Kr\xspace}
\newcommand{\krm}{${}^{83\mathrm{m}}$Kr\xspace}
\newcommand{\ambe}{${}^{241}$AmBe\xspace}

\newcommand{\cSone}{$\mathrm{cS1}$\xspace}
\newcommand{\cStwo}{$\mathrm{cS2}$\xspace}
\newcommand{\cStwob}{$\mathrm{cS2_b}$\xspace}
\newcommand{\ucSone}{$\mathrm{S1}$\xspace}
\newcommand{\ucStwo}{$\mathrm{S2}$\xspace}
\newcommand{\Sone}{$\mathrm{S1}$\xspace}
\newcommand{\Stwo}{$\mathrm{S2}$\xspace}
\newcommand{\z}{Z\xspace}
\newcommand{\radius}{R\xspace}
\newcommand{\radiussquared}{R$^{2}$\xspace}

\newcommand{\nmoststringentlimit}{$4.1\times10^{-47}$~cm$^2$\xspace}
\newcommand{\nmoststingentmass}{30~\gevcsq}
\newcommand{\nbestfitsigmasi}{$2.9\times10^{-48}$~cm$^2$\xspace}
\newcommand{\nbestfitsigmasitwoh}{$4.7\times10^{-47}$~cm$^2$\xspace}

\newcommand\figref[1]{Fig.~\ref{#1}}
\newcommand\Figref[1]{Figure~\ref{#1}}
\newcommand\tabref[1]{Table~\ref{#1}}
\newcommand\figsref[2]{Figs.~\ref{#1}~and~\ref{#2}}
\newcommand\Figsref[2]{Figures~\ref{#1}~and~\ref{#2}}

\newcommand{\kevee}{\mathrm{keV_{ee}}}
\newcommand{\kevnr}{\mathrm{keV_{nr}}}

% Old abbreviations
\newcommand{\AC}{AC\xspace}
\newcommand{\FM}{fiducial mass\xspace}

% old microscopic units
%\newcommand{\dru}{($\mathrm{kg}\times\mathrm{day}\times\mathrm{keV})^{-1}$\xspace}
% new macroscopic units
\newcommand{\dru}{events/$(\mathrm{\ton}\times\mathrm{yr}\times\kevee)$}
\newcommand{\gevcsq}{GeV/c${}^2$\xspace}
\newcommand{\tevcsq}{TeV/c${}^2$\xspace}
\newcommand{\searchregion}{cS$1\!\in\![3, 70]\;\mathrm{PE}$, cS$2_b\!\in\![50, 8000]\;\mathrm{PE}$~search region}
% https://xe1t-wiki.lngs.infn.it/doku.php?id=greene:bbf_acceptances
\newcommand{\searchregionkev}{[1.4,~10.6]~$\kevee$\xspace}
\newcommand{\searchregionkevnr}{[4.9,~40.9]~$\kevnr$\xspace}

\newcommand{\todo}[1]{\textcolor{red}{\textbf{$\lceil$#1$\rfloor$}}}
\newcommand{\num}[1]{#1}

\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\arxiv}[1]{\href{http://arxiv.org/abs/#1}{\texttt{arXiv:#1}}}

\makeatletter
\newcommand{\romenum}[1]{(\romannumeral #1)}
\makeatother

\newcommand{\Delete}[2][magenta]{\textcolor{#1}{\sout{#2}}}
\newcommand{\Modify}[2][magenta]{\textcolor{#1}{\textrm{#2}}}

\newcommand{\bern}{\affiliation{Albert Einstein Center for Fundamental Physics, University of Bern, 3012 Bern, Switzerland}}

\newcommand{\bologna}{\affiliation{Department of Physics and Astronomy, University of Bologna and INFN-Bologna, 40126 Bologna, Italy}}

\newcommand{\chicago}{\affiliation{Department of Physics \& Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA}}

\newcommand{\coimbra}{\affiliation{LIBPhys, Department of Physics, University of Coimbra, 3004-516 Coimbra, Portugal}}

\newcommand{\columbia}{\affiliation{Physics Department, Columbia University, New York, NY 10027, USA}}

\newcommand{\lngs}{\affiliation{INFN-Laboratori Nazionali del Gran Sasso and Gran Sasso Science Institute, 67100 L'Aquila, Italy}}

\newcommand{\mainz}{\affiliation{Institut f\"ur Physik \& Exzellenzcluster PRISMA, Johannes Gutenberg-Universit\"at Mainz, 55099 Mainz, Germany}}

\newcommand{\heidelberg}{\affiliation{Max-Planck-Institut f\"ur Kernphysik, 69117 Heidelberg, Germany}}

\newcommand{\munster}{\affiliation{Institut f\"ur Kernphysik, Westf\"alische Wilhelms-Universit\"at M\"unster, 48149 M\"unster, Germany}}

\newcommand{\nikhef}{\affiliation{Nikhef and the University of Amsterdam, Science Park, 1098XG Amsterdam, Netherlands}}

\newcommand{\nyuad}{\affiliation{New York University Abu Dhabi, Abu Dhabi, United Arab Emirates}}

\newcommand{\purdue}{\affiliation{Department of Physics and Astronomy, Purdue University, West Lafayette, IN 47907, USA}}

\newcommand{\rpi}{\affiliation{Department of Physics, Applied Physics and Astronomy, Rensselaer Polytechnic Institute, Troy, NY 12180, USA}}

\newcommand{\rice}{\affiliation{Department of Physics and Astronomy, Rice University, Houston, TX 77005, USA}}

\newcommand{\stockholm}{\affiliation{Oskar Klein Centre, Department of Physics, Stockholm University, AlbaNova, Stockholm SE-10691, Sweden}}

\newcommand{\subatech}{\affiliation{SUBATECH, IMT Atlantique, CNRS/IN2P3, Universit\'e de Nantes, Nantes 44307, France}}

\newcommand{\torino}{\affiliation{INFN-Torino and Osservatorio Astrofisico di Torino, 10125 Torino, Italy}}

\newcommand{\ucla}{\affiliation{Physics \& Astronomy Department, University of California, Los Angeles, CA 90095, USA}}

\newcommand{\ucsd}{\affiliation{Department of Physics, University of California, San Diego, CA 92093, USA}}

\newcommand{\wis}{\affiliation{Department of Particle Physics and Astrophysics, Weizmann Institute of Science, Rehovot 7610001, Israel}}

\newcommand{\zurich}{\affiliation{Physik-Institut, University of Zurich, 8057  Zurich, Switzerland}}

\newcommand{\paris}{\affiliation{LPNHE, Universit\'{e} Pierre et Marie Curie, Universit\'{e} Paris Diderot, CNRS/IN2P3, Paris 75252, France}}

\newcommand{\freiburg}{\affiliation{Physikalisches Institut, Universit\"at Freiburg, 79104 Freiburg, Germany}}

\begin{document}

% CHANGE TO TITLE

\title{Background Modeling and Statistical Inference for WIMP Searches in XENON1T }

\input{authors.tex}

\date{\today}

\begin{abstract}

\end{abstract}

\pacs{
    95.35.+d, %Dark matter
    14.80.Ly, %Supersymmetric partners of known particles
    29.40.-n,  %Radiation detectors
    95.55.Vj
}

\keywords{Dark Matter, Direct Detection, Xenon, Data Analysis}

\maketitle

\section{Introduction}
% @all

\section{Detector Signal Response Model}
% @Qing

\input{Sections/DetectorSignalResponse.tex}

\section{Background and Dark Matter Signal Model}

\input{Sections/ERBackground.tex}

\input{Sections/NRBackground.tex}

\input{Sections/SurfaceBackground.tex}

\input{Sections/ACBackground.tex}

\input{Sections/WIMPSignalModel.tex}

\input{Sections/Inference.tex}
\subsection{Inference of XENON1T Data}
\input{Sections/Likelihood.tex}

\input{bibliography.tex}
\end{document}
